### 2019-01-03 notebook.tex
updating report

% Default to the notebook output style

% Inherit from the specified cell style.

\documentclass[11pt]{article}

    \usepackage[T1]{fontenc}
    % Nicer default font (+ math font) than Computer Modern for most use cases
    \usepackage{mathpazo}

    % Basic figure setup, for now with no caption control since it's done
    % automatically by Pandoc (which extracts ![](path) syntax from Markdown).
    \usepackage{graphicx}
    % We will generate all images so they have a width \maxwidth. This means
    % that they will get their normal width if they fit onto the page, but
    % are scaled down if they would overflow the margins.
    \makeatletter
    \def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth
    \else\Gin@nat@width\fi}
    \makeatother
    \let\Oldincludegraphics\includegraphics
    % Set max figure width to be 80% of text width, for now hardcoded.
    \renewcommand{\includegraphics}[1]{\Oldincludegraphics[width=.8\maxwidth]{#1}}
    % Ensure that by default, figures have no caption (until we provide a
    % proper Figure object with a Caption API and a way to capture that
    % in the conversion process - todo).
    \usepackage{caption}
    \DeclareCaptionLabelFormat{nolabel}{}
    \captionsetup{labelformat=nolabel}

    \usepackage{adjustbox} % Used to constrain images to a maximum size 
    \usepackage{xcolor} % Allow colors to be defined
    \usepackage{enumerate} % Needed for markdown enumerations to work
    \usepackage{geometry} % Used to adjust the document margins
    \usepackage{amsmath} % Equations
    \usepackage{amssymb} % Equations
    \usepackage{textcomp} % defines textquotesingle
    % Hack from http://tex.stackexchange.com/a/47451/13684:
    \AtBeginDocument{%
        \def\PYZsq{\textquotesingle}% Upright quotes in Pygmentized code
    }
    \usepackage{upquote} % Upright quotes for verbatim code
    \usepackage{eurosym} % defines \euro
    \usepackage[mathletters]{ucs} % Extended unicode (utf-8) support
    \usepackage[utf8x]{inputenc} % Allow utf-8 characters in the tex document
    \usepackage{fancyvrb} % verbatim replacement that allows latex
    \usepackage{grffile} % extends the file name processing of package graphics 
                         % to support a larger range 
    % The hyperref package gives us a pdf with properly built
    % internal navigation ('pdf bookmarks' for the table of contents,
    % internal cross-reference links, web links for URLs, etc.)
    \usepackage{hyperref}
    \usepackage{longtable} % longtable support required by pandoc >1.10
    \usepackage{booktabs}  % table support for pandoc > 1.12.2
    \usepackage[inline]{enumitem} % IRkernel/repr support (it uses the enumerate* environment)
    \usepackage[normalem]{ulem} % ulem is needed to support strikethroughs (\sout)
                                % normalem makes italics be italics, not underlines

    % Colors for the hyperref package
    \definecolor{urlcolor}{rgb}{0,.145,.698}
    \definecolor{linkcolor}{rgb}{.71,0.21,0.01}
    \definecolor{citecolor}{rgb}{.12,.54,.11}

    % ANSI colors
    \definecolor{ansi-black}{HTML}{3E424D}
    \definecolor{ansi-black-intense}{HTML}{282C36}
    \definecolor{ansi-red}{HTML}{E75C58}
    \definecolor{ansi-red-intense}{HTML}{B22B31}
    \definecolor{ansi-green}{HTML}{00A250}
    \definecolor{ansi-green-intense}{HTML}{007427}
    \definecolor{ansi-yellow}{HTML}{DDB62B}
    \definecolor{ansi-yellow-intense}{HTML}{B27D12}
    \definecolor{ansi-blue}{HTML}{208FFB}
    \definecolor{ansi-blue-intense}{HTML}{0065CA}
    \definecolor{ansi-magenta}{HTML}{D160C4}
    \definecolor{ansi-magenta-intense}{HTML}{A03196}
    \definecolor{ansi-cyan}{HTML}{60C6C8}
    \definecolor{ansi-cyan-intense}{HTML}{258F8F}
    \definecolor{ansi-white}{HTML}{C5C1B4}
    \definecolor{ansi-white-intense}{HTML}{A1A6B2}

    % commands and environments needed by pandoc snippets
    % extracted from the output of `pandoc -s`
    \providecommand{\tightlist}{%
      \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
    \DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
    % Add ',fontsize=\small' for more characters per line
    \newenvironment{Shaded}{}{}
    \newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.00,0.44,0.13}{\textbf{{#1}}}}
    \newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.56,0.13,0.00}{{#1}}}
    \newcommand{\DecValTok}[1]{\textcolor[rgb]{0.25,0.63,0.44}{{#1}}}
    \newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.25,0.63,0.44}{{#1}}}
    \newcommand{\FloatTok}[1]{\textcolor[rgb]{0.25,0.63,0.44}{{#1}}}
    \newcommand{\CharTok}[1]{\textcolor[rgb]{0.25,0.44,0.63}{{#1}}}
    \newcommand{\StringTok}[1]{\textcolor[rgb]{0.25,0.44,0.63}{{#1}}}
    \newcommand{\CommentTok}[1]{\textcolor[rgb]{0.38,0.63,0.69}{\textit{{#1}}}}
    \newcommand{\OtherTok}[1]{\textcolor[rgb]{0.00,0.44,0.13}{{#1}}}
    \newcommand{\AlertTok}[1]{\textcolor[rgb]{1.00,0.00,0.00}{\textbf{{#1}}}}
    \newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.02,0.16,0.49}{{#1}}}
    \newcommand{\RegionMarkerTok}[1]{{#1}}
    \newcommand{\ErrorTok}[1]{\textcolor[rgb]{1.00,0.00,0.00}{\textbf{{#1}}}}
    \newcommand{\NormalTok}[1]{{#1}}

    % Additional commands for more recent versions of Pandoc
    \newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.53,0.00,0.00}{{#1}}}
    \newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.25,0.44,0.63}{{#1}}}
    \newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.25,0.44,0.63}{{#1}}}
    \newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.73,0.40,0.53}{{#1}}}
    \newcommand{\ImportTok}[1]{{#1}}
    \newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.73,0.13,0.13}{\textit{{#1}}}}
    \newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.38,0.63,0.69}{\textbf{\textit{{#1}}}}}
    \newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.38,0.63,0.69}{\textbf{\textit{{#1}}}}}
    \newcommand{\VariableTok}[1]{\textcolor[rgb]{0.10,0.09,0.49}{{#1}}}
    \newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.00,0.44,0.13}{\textbf{{#1}}}}
    \newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.40,0.40,0.40}{{#1}}}
    \newcommand{\BuiltInTok}[1]{{#1}}
    \newcommand{\ExtensionTok}[1]{{#1}}
    \newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.74,0.48,0.00}{{#1}}}
    \newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.49,0.56,0.16}{{#1}}}
    \newcommand{\InformationTok}[1]{\textcolor[rgb]{0.38,0.63,0.69}{\textbf{\textit{{#1}}}}}
    \newcommand{\WarningTok}[1]{\textcolor[rgb]{0.38,0.63,0.69}{\textbf{\textit{{#1}}}}}

    % Define a nice break command that doesn't care if a line doesn't already
    % exist.
    \def\br{\hspace*{\fill} \\* }
    % Math Jax compatability definitions
    \def\gt{>}
    \def\lt{<}
    % Document parameters
    \title{Report}

    % Pygments definitions

\makeatletter
\def\PY@reset{\let\PY@it=\relax \let\PY@bf=\relax%
    \let\PY@ul=\relax \let\PY@tc=\relax%
    \let\PY@bc=\relax \let\PY@ff=\relax}
\def\PY@tok#1{\csname PY@tok@#1\endcsname}
\def\PY@toks#1+{\ifx\relax#1\empty\else%
    \PY@tok{#1}\expandafter\PY@toks\fi}
\def\PY@do#1{\PY@bc{\PY@tc{\PY@ul{%
    \PY@it{\PY@bf{\PY@ff{#1}}}}}}}
\def\PY#1#2{\PY@reset\PY@toks#1+\relax+\PY@do{#2}}

\expandafter\def\csname PY@tok@w\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.73,0.73}{##1}}}
\expandafter\def\csname PY@tok@c\endcsname{\let\PY@it=\textit\def\PY@tc##1{\textcolor[rgb]{0.25,0.50,0.50}{##1}}}
\expandafter\def\csname PY@tok@cp\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.74,0.48,0.00}{##1}}}
\expandafter\def\csname PY@tok@k\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@kp\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@kt\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.69,0.00,0.25}{##1}}}
\expandafter\def\csname PY@tok@o\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
\expandafter\def\csname PY@tok@ow\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.67,0.13,1.00}{##1}}}
\expandafter\def\csname PY@tok@nb\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@nf\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.00,0.00,1.00}{##1}}}
\expandafter\def\csname PY@tok@nc\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.00,1.00}{##1}}}
\expandafter\def\csname PY@tok@nn\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.00,1.00}{##1}}}
\expandafter\def\csname PY@tok@ne\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.82,0.25,0.23}{##1}}}
\expandafter\def\csname PY@tok@nv\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.10,0.09,0.49}{##1}}}
\expandafter\def\csname PY@tok@no\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.53,0.00,0.00}{##1}}}
\expandafter\def\csname PY@tok@nl\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.63,0.63,0.00}{##1}}}
\expandafter\def\csname PY@tok@ni\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.60,0.60,0.60}{##1}}}
\expandafter\def\csname PY@tok@na\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.49,0.56,0.16}{##1}}}
\expandafter\def\csname PY@tok@nt\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@nd\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.67,0.13,1.00}{##1}}}
\expandafter\def\csname PY@tok@s\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
\expandafter\def\csname PY@tok@sd\endcsname{\let\PY@it=\textit\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
\expandafter\def\csname PY@tok@si\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.73,0.40,0.53}{##1}}}
\expandafter\def\csname PY@tok@se\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.73,0.40,0.13}{##1}}}
\expandafter\def\csname PY@tok@sr\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.40,0.53}{##1}}}
\expandafter\def\csname PY@tok@ss\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.10,0.09,0.49}{##1}}}
\expandafter\def\csname PY@tok@sx\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@m\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
\expandafter\def\csname PY@tok@gh\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.00,0.50}{##1}}}
\expandafter\def\csname PY@tok@gu\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.50,0.00,0.50}{##1}}}
\expandafter\def\csname PY@tok@gd\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.63,0.00,0.00}{##1}}}
\expandafter\def\csname PY@tok@gi\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.00,0.63,0.00}{##1}}}
\expandafter\def\csname PY@tok@gr\endcsname{\def\PY@tc##1{\textcolor[rgb]{1.00,0.00,0.00}{##1}}}
\expandafter\def\csname PY@tok@ge\endcsname{\let\PY@it=\textit}
\expandafter\def\csname PY@tok@gs\endcsname{\let\PY@bf=\textbf}
\expandafter\def\csname PY@tok@gp\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.00,0.50}{##1}}}
\expandafter\def\csname PY@tok@go\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.53,0.53,0.53}{##1}}}
\expandafter\def\csname PY@tok@gt\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.00,0.27,0.87}{##1}}}
\expandafter\def\csname PY@tok@err\endcsname{\def\PY@bc##1{\setlength{\fboxsep}{0pt}\fcolorbox[rgb]{1.00,0.00,0.00}{1,1,1}{\strut ##1}}}
\expandafter\def\csname PY@tok@kc\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@kd\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@kn\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@kr\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@bp\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\expandafter\def\csname PY@tok@fm\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.00,0.00,1.00}{##1}}}
\expandafter\def\csname PY@tok@vc\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.10,0.09,0.49}{##1}}}
\expandafter\def\csname PY@tok@vg\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.10,0.09,0.49}{##1}}}
\expandafter\def\csname PY@tok@vi\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.10,0.09,0.49}{##1}}}
\expandafter\def\csname PY@tok@vm\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.10,0.09,0.49}{##1}}}
\expandafter\def\csname PY@tok@sa\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
\expandafter\def\csname PY@tok@sb\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
\expandafter\def\csname PY@tok@sc\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
\expandafter\def\csname PY@tok@dl\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
\expandafter\def\csname PY@tok@s2\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
\expandafter\def\csname PY@tok@sh\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
\expandafter\def\csname PY@tok@s1\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
\expandafter\def\csname PY@tok@mb\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
\expandafter\def\csname PY@tok@mf\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
\expandafter\def\csname PY@tok@mh\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
\expandafter\def\csname PY@tok@mi\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
\expandafter\def\csname PY@tok@il\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
\expandafter\def\csname PY@tok@mo\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
\expandafter\def\csname PY@tok@ch\endcsname{\let\PY@it=\textit\def\PY@tc##1{\textcolor[rgb]{0.25,0.50,0.50}{##1}}}
\expandafter\def\csname PY@tok@cm\endcsname{\let\PY@it=\textit\def\PY@tc##1{\textcolor[rgb]{0.25,0.50,0.50}{##1}}}
\expandafter\def\csname PY@tok@cpf\endcsname{\let\PY@it=\textit\def\PY@tc##1{\textcolor[rgb]{0.25,0.50,0.50}{##1}}}
\expandafter\def\csname PY@tok@c1\endcsname{\let\PY@it=\textit\def\PY@tc##1{\textcolor[rgb]{0.25,0.50,0.50}{##1}}}
\expandafter\def\csname PY@tok@cs\endcsname{\let\PY@it=\textit\def\PY@tc##1{\textcolor[rgb]{0.25,0.50,0.50}{##1}}}

\def\PYZbs{\char`\\}
\def\PYZus{\char`\_}
\def\PYZob{\char`\{}
\def\PYZcb{\char`\}}
\def\PYZca{\char`\^}
\def\PYZam{\char`\&}
\def\PYZlt{\char`\<}
\def\PYZgt{\char`\>}
\def\PYZsh{\char`\#}
\def\PYZpc{\char`\%}
\def\PYZdl{\char`\$}
\def\PYZhy{\char`\-}
\def\PYZsq{\char`\'}
\def\PYZdq{\char`\"}
\def\PYZti{\char`\~}
% for compatibility with earlier versions
\def\PYZat{@}
\def\PYZlb{[}
\def\PYZrb{]}
\makeatother

    % Exact colors from NB
    \definecolor{incolor}{rgb}{0.0, 0.0, 0.5}
    \definecolor{outcolor}{rgb}{0.545, 0.0, 0.0}

    % Prevent overflowing lines due to hard-to-break entities
    \sloppy 
    % Setup hyperref package
    \hypersetup{
      breaklinks=true,  % so long urls are correctly broken across lines
      colorlinks=true,
      urlcolor=urlcolor,
      linkcolor=linkcolor,
      citecolor=citecolor,
      }
    % Slightly bigger margins than the latex defaults

    \geometry{verbose,tmargin=1in,bmargin=1in,lmargin=1in,rmargin=1in}

    \begin{document}

    \maketitle

    \(\title(Abstract)\)

    \begin{itemize}
\tightlist
\item
  \#TODO write some sentence about general motivation for bibliometric
  analysis
\end{itemize}

We explore ways to extract information from ICLS and CSCL papers to gain
an understanding about the community formed by conference participants
and what research is being conducted within the community. After
describing how to extract data from the original dataset in suitable
format for analysis we perform an exploratory data analysis after which
we derive insights into the community using social network analysis and
{[}Nour: NLP etc{]}.

\begin{itemize}
\tightlist
\item
  \#TODO write a few centences about the most central findings
\end{itemize}

    \hypertarget{introduction}{%
\subsection{1. Introduction}\label{introduction}}

    \hypertarget{bibliometric-study-to-analyse-the-papers-published-in-the-proceeding-of-the-conferences-organized-by-the-international-learning-science-society.}{%
\subsection{Bibliometric study to analyse the papers published in the
Proceeding of the Conferences organized by the International Learning
Science
Society.}\label{bibliometric-study-to-analyse-the-papers-published-in-the-proceeding-of-the-conferences-organized-by-the-international-learning-science-society.}}

    \hypertarget{data-processing}{%
\subsection{2. Data Processing}\label{data-processing}}

    To extract information from the dataset we first need to convert the
data into a suitable format. We store the extracted data in csv format,
as this makes it accessible to any scientist and can be read as is on
the GitHub. Only the data frame containing emails is stored in pickle
format, which is done for privacy reasons.

    \hypertarget{metadata}{%
\subsubsection{2.1 Metadata}\label{metadata}}

\hypertarget{extraction}{%
\paragraph{Extraction}\label{extraction}}

The provided raw dataset consists of papers in pdf format as well as
associated metadata in xml format. This associated metadata consists of
: full-length author names, abstract of the paper, associated keywords,
document type, publisher, title of the paper, time of issue and the
citation string for the paper. We extract the xml metadata using the
lxmltree python library into a csv file containing the above listed
columns. The provided xml does not exactly follow the xml standard,
hence we handle errors by iteratively parsing the file.

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}2}]:} \PY{k+kn}{import} \PY{n+nn}{os} 
        \PY{k+kn}{import} \PY{n+nn}{pandas} \PY{k+kn}{as} \PY{n+nn}{pd}
        \PY{n}{rootdir} \PY{o}{=} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{data/papers}\PY{l+s+s1}{\PYZsq{}}
        \PY{n}{contents} \PY{o}{=} \PY{p}{[}\PY{p}{]}
        \PY{n}{i} \PY{o}{=} \PY{l+m+mi}{0}
        \PY{n}{source} \PY{o}{=} \PY{p}{[}\PY{p}{]}
        \PY{n}{errors} \PY{o}{=} \PY{p}{[}\PY{p}{]}
        \PY{n}{doc} \PY{o}{=} \PY{p}{[}\PY{p}{]}
        \PY{n}{year} \PY{o}{=} \PY{p}{[}\PY{p}{]}
        \PY{k}{for} \PY{n}{subdir}\PY{p}{,} \PY{n}{dirs}\PY{p}{,} \PY{n}{files} \PY{o+ow}{in} \PY{n}{os}\PY{o}{.}\PY{n}{walk}\PY{p}{(}\PY{n}{rootdir}\PY{p}{)}\PY{p}{:}
            \PY{k}{for} \PY{n+nb}{file} \PY{o+ow}{in} \PY{n}{files}\PY{p}{:}
                \PY{k}{if} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{txt}\PY{l+s+s1}{\PYZsq{}} \PY{o+ow}{in} \PY{n+nb}{file}\PY{p}{:}
                    \PY{n}{i} \PY{o}{+}\PY{o}{=} \PY{l+m+mi}{1}
                    \PY{n}{path} \PY{o}{=} \PY{n}{os}\PY{o}{.}\PY{n}{path}\PY{o}{.}\PY{n}{join}\PY{p}{(}\PY{n}{subdir}\PY{p}{,} \PY{n+nb}{file}\PY{p}{)}
                    \PY{k}{with} \PY{n+nb}{open}\PY{p}{(}\PY{n}{path}\PY{p}{)} \PY{k}{as} \PY{n+nb}{file}\PY{p}{:}
                        \PY{n}{doc}\PY{o}{.}\PY{n}{append}\PY{p}{(}\PY{n}{path}\PY{o}{.}\PY{n}{split}\PY{p}{(}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{\PYZus{}}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}\PY{p}{[}\PY{l+m+mi}{1}\PY{p}{]}\PY{p}{[}\PY{p}{:}\PY{l+m+mi}{3}\PY{p}{]}\PY{p}{)}
                        \PY{n}{year}\PY{o}{.}\PY{n}{append}\PY{p}{(}\PY{n+nb}{int}\PY{p}{(}\PY{n}{path}\PY{o}{.}\PY{n}{split}\PY{p}{(}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{/}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}\PY{p}{[}\PY{o}{\PYZhy{}}\PY{l+m+mi}{1}\PY{p}{]}\PY{p}{[}\PY{l+m+mi}{6}\PY{p}{:}\PY{l+m+mi}{10}\PY{p}{]}\PY{p}{)}\PY{p}{)}
                        \PY{k}{try}\PY{p}{:}
                            \PY{n}{text} \PY{o}{=} \PY{n+nb}{file}\PY{o}{.}\PY{n}{read}\PY{p}{(}\PY{p}{)}
                            \PY{k}{if} \PY{n+nb}{len}\PY{p}{(}\PY{n}{text}\PY{p}{)}\PY{o}{\PYZgt{}} \PY{l+m+mi}{10} \PY{p}{:}
                                \PY{n}{contents}\PY{o}{.}\PY{n}{append}\PY{p}{(}\PY{n}{text}\PY{p}{)}
                            \PY{n}{source}\PY{o}{.}\PY{n}{append}\PY{p}{(}\PY{n}{subdir}\PY{p}{[}\PY{n+nb}{len}\PY{p}{(}\PY{n}{rootdir}\PY{p}{)}\PY{p}{:}\PY{p}{]}\PY{p}{)}
                        \PY{k}{except}\PY{p}{:}
                            \PY{n}{name}\PY{p}{,} \PY{n}{message}\PY{p}{,} \PY{n}{content} \PY{o}{=} \PY{n}{sys}\PY{o}{.}\PY{n}{exc\PYZus{}info}\PY{p}{(}\PY{p}{)}
                            \PY{n}{errors}\PY{o}{.}\PY{n}{append}\PY{p}{(}\PY{n}{message}\PY{p}{)}
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}5}]:} \PY{k}{print}\PY{p}{(}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{Number of papers is : \PYZob{}\PYZcb{}}\PY{l+s+s1}{\PYZsq{}}\PY{o}{.}\PY{n}{format}\PY{p}{(}\PY{n+nb}{len}\PY{p}{(}\PY{n}{contents}\PY{p}{)}\PY{p}{)}\PY{p}{)}
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
Number of papers is : 869

    \end{Verbatim}

    Some of the documents are not readable and have some strange format so
we need to take them out of the analysis. Wwe find ourselves with
roughly 834 documents

    \hypertarget{data-cleaning}{%
\subsection{Data Cleaning}\label{data-cleaning}}

    your part for the references universities parsing \ldots{}

    \hypertarget{text-preprocessing}{%
\subsubsection{Text preprocessing}\label{text-preprocessing}}

    From the pdf parser some of the documents were corrupted with some weird
caracters such as `\xe2\x80\x99s', white space strings \ldots{}

\begin{itemize}
\item
  We used \textbf{\emph{beautiful soup}} and \textbf{\emph{string}}
  libraries to only keep the text that we needed without any special
  character.
\item
  we applied \textbf{\emph{regular expression}} to remove numbers
  because we thought that numbers were not that important.
\item
  We put all the words to lower cases
\item
  We removed the words that were connecting parts of a sentence rather
  than showing subjects, objects or intent. For us these words were not
  that important and were only going to increase the bag of words length
\item
  In some methods we used \textbf{\emph{Lemmatization}} and
  \textbf{\emph{stemming}} and in other methods we didn't because we
  wanted to do a mapping with \textbf{\emph{GloVe}} vocabulary which we
  will explain later on.
\end{itemize}

\textbf{\emph{Lemmatization}} is a word variations to the root of the
word (e.g.~working, works, worked changed to work).
\textbf{\emph{Stemming}} is the process of reducing inflected and
derived words to their word stem, base or root form---generally a
written word form As the use of the stop words to reduce the BOW (bag of
words size we also used lemmatization and stemming to be able to reduce
the number of words without taking off any information)

    \textbf{\emph{Lemmatization}} and different form of
\textbf{\emph{Stemming}} were only used with \textbf{\emph{TF-IDF}}
while doing the Keywords extraction, otherwise we prefered keeping the
words as they are because we were doing a mapping with a pretrained
stanford word embedding and we did not wand to loose interpretability.

    \hypertarget{keywords-extraction}{%
\subsection{Keywords extraction}\label{keywords-extraction}}

    For the Keywords extraction we used three methods. The first one whe is
a trivial one is to search in the pdf itself for keywords and extract
them, this method is the most accurate but we found out that for 492
papers we had no keywords included. So we deciced to use two methods for
keywords extraction. The first one is \textbf{\emph{TF-IDF}} and the
second one is \textbf{\emph{Rake}}.

    \begin{itemize}
\tightlist
\item
  \textbf{\emph{TF-IDF}}: Tf--idf is one of the most popular
  term-weighting schemes today, in information retrieval, tf--idf or
  TFIDF, short for term frequency--inverse document frequency, is a
  numerical statistic that is intended to reflect how important a word
  is to a document in a collection or corpus. It is often used as a
  weighting factor in searches of information retrieval, text mining,
  and user modeling. The tf--idf value increases proportionally to the
  number of times a word appears in the document and is offset by the
  number of documents in the corpus that contain the word, which helps
  to adjust for the fact that some words appear more frequently in
  general.
\end{itemize}

    With TF-IDF we sorted for each document the words with the highest score
and then selected the the 7 first words for each document.

    \begin{itemize}
\tightlist
\item
  \textbf{\emph{Rake}}: Rake stands for Rapid Automatic Keyword
  Extraction. It is an existing python implementation that uses the NLTK
  toolkit for the score calculations.
\end{itemize}

\textbf{\emph{How it works}} : * It splits the text into sentences and
generates some words as candidates.\\
* Various punctuation signs will be treated as sentence boundaries. *
All words listed in the stopwords file will be treated as phrase
boundaries. This helps generate candidates that consist of one or more
non-stopwords. However ,it won't work in cases where the stopword is
part of the phrase. For example, `new' is listed in RAKE's stopword
list. This means that neither `New York' nor `New Zealand' can be ever a
keyword. * For each keyword candidate generated, the algorithm computes
the score of the pretended keyword, which is the sum of the scores for
each of its words (if it's a composed word). The words are scored
according to their frequency and the typical length of a candidate
phrase in which they appear. * The last step is ranking the scores ansd
selecting the ones with the highest score

    \textbf{\emph{Keywords in text}}: Select from the text the keywords
already given by the authors of the paper.

    Once we have all the keywords from the three methods, we tried to select
the most accurate keywords. So we created a method that selects the
intersection of TF-IDF keywords and the Rake keywords with the keywords
of the authors (if there are any keywords in the text), if the
intersection is empty and we have the keywords in the text we only take
the keywords of the text. If we don't have any keywords we take the
intersection of the TF-IDF and the Rake. If again, the intersection is
empty then we only take the TF-IDF keywords because they were closer to
the text keywords than the Rake Keywords.

    Once we have our final keywords, we created a method that goes into the
metadata and put assign to every document a publication year.

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}7}]:} \PY{n}{keywords\PYZus{}df} \PY{o}{=} \PY{n}{pd}\PY{o}{.}\PY{n}{read\PYZus{}csv}\PY{p}{(}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{keywords\PYZus{}final.csv}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}
\end{Verbatim}

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}30}]:} \PY{k+kn}{import} \PY{n+nn}{matplotlib.pyplot} \PY{k+kn}{as} \PY{n+nn}{plt}
         \PY{k+kn}{import} \PY{n+nn}{numpy} \PY{k+kn}{as} \PY{n+nn}{np}
         \PY{n}{x} \PY{o}{=} \PY{n}{plt}\PY{o}{.}\PY{n}{hist}\PY{p}{(}\PY{n+nb}{list}\PY{p}{(}\PY{n}{keywords\PYZus{}df}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{year}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]}\PY{p}{)}\PY{p}{,} \PY{n}{bins}\PY{o}{=}\PY{l+m+mi}{7}\PY{p}{,}\PY{p}{)}
         \PY{n}{x} \PY{o}{=} \PY{n}{plt}\PY{o}{.}\PY{n}{xticks}\PY{p}{(}\PY{n}{np}\PY{o}{.}\PY{n}{arange}\PY{p}{(}\PY{n+nb}{min}\PY{p}{(}\PY{n}{keywords\PYZus{}df}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{year}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]}\PY{p}{)}\PY{p}{,}\PY{n+nb}{max}\PY{p}{(}\PY{n}{keywords\PYZus{}df}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{year}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]}\PY{o}{+}\PY{l+m+mi}{1}\PY{p}{)} \PY{p}{,} \PY{l+m+mi}{1}\PY{p}{)}\PY{p}{)}
         \PY{n}{x} \PY{o}{=} \PY{n}{plt}\PY{o}{.}\PY{n}{title}\PY{p}{(}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{Distribution of the number of documents per year}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}
\end{Verbatim}

    \begin{center}
    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_24_0.png}
    \end{center}
    { \hspace*{\fill} \\}

    Since we don't have the same number of documents for each year we needed
to scale over the years and use the percentage of appearence of a word.
So after groupping the words by year and scaling them we found graph
below

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}33}]:} \PY{k+kn}{from} \PY{n+nn}{IPython.display} \PY{k+kn}{import} \PY{n}{Image}
         \PY{n}{Image}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{keywords\PYZus{}by\PYZus{}year.png}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
\end{Verbatim}

\texttt{\color{outcolor}Out[{\color{outcolor}33}]:}

    \begin{center}
    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_26_0.png}
    \end{center}
    { \hspace*{\fill} \\}

    We wanted then to know what are the trends of words for each specific
year, so we selected distinct words for each year, it means that we
selected for each year the words that were present for that year and
never for the others. We get the graph below. As we can see from the
graph, the most used word in the papers, more than 10\% of 2015 papers
uses the word `peer', more than 6\% of the papers uses the words
`building', `embodied' in 2016. In 2017 the most frequent keyword on is
`reponsive' and in 2018 `tools' is present with more than 6\%.

    \begin{Verbatim}[commandchars=\\\{\}]
{\color{incolor}In [{\color{incolor}37}]:} \PY{n}{Image}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{distinct\PYZus{}words.png}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
\end{Verbatim}

\texttt{\color{outcolor}Out[{\color{outcolor}37}]:}

    \begin{center}
    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_28_0.png}
    \end{center}
    { \hspace*{\fill} \\}

    \hypertarget{document-clustering}{%
\subsection{Document Clustering}\label{document-clustering}}

    % Add a bibliography block to the postdoc

    \end{document}

### 2019-01-03 Scripts/parse_metadata.py

@@ -193,8 +193,8 @@ d= {}
 for i, m in enumerate(names):
     for j, n in enumerate(names):
         if i < j and not 'de' in m:
-            y = set([i.lower() for i in regex.split(' |\,', unicodedata.normalize('NFC', m)) if len(regex.sub('\.', '', i)) > 1])
-            name = set([i.lower() for i in regex.split(' |\,', unicodedata.normalize('NFC', n)) if len(regex.sub('\.', '', i)) > 1])
+            y = set([i.lower() for i in regex.split(' |\,', unicodedata.normalize('NFC', m)) if len(regex.sub('\.', '', i)) > 2])
+            name = set([i.lower() for i in regex.split(' |\,', unicodedata.normalize('NFC', n)) if len(regex.sub('\.', '', i)) > 2])
             if len(name.intersection(y)) > 1 and n!= m and not ('Lee' in n or 'Lee' in m):
                 d[n]= m
 

### 2019-01-03 Report/paper.tex
comit report

--- 2019-01-03 notebook.tex
@@
 
-\documentclass[11pt]{article}
+    \documentclass[journal,twocolumn]{IEEEtran}
+\usepackage[noadjust]{cite}
 
@@
                                 % normalem makes italics be italics, not underlines
+    \usepackage{mathrsfs}
+
+\usepackage{mathptmx}
+\usepackage{algorithm}\usepackage{algorithmic}
 
@@
     \definecolor{ansi-white-intense}{HTML}{A1A6B2}
+    \definecolor{ansi-default-inverse-fg}{HTML}{FFFFFF}
+    \definecolor{ansi-default-inverse-bg}{HTML}{000000}
 
@@
     \def\br{\hspace*{\fill} \\* }
-    % Math Jax compatability definitions
+    % Math Jax compatibility definitions
     \def\gt{>}
     \def\lt{<}
+    \let\Oldtex\TeX
+    \let\Oldlatex\LaTeX
+    \renewcommand{\TeX}{\textrm{\Oldtex}}
+    \renewcommand{\LaTeX}{\textrm{\Oldlatex}}
     % Document parameters
-    \title{Report}
+    % Document title
+    \title{paper}
 
@@
 
+\renewcommand{\figurename}{Figure}
+\captionsetup{labelformat=simple}\title{Bibliometric Analysis of ICLS and CSCL research}
+\author{\IEEEauthorblockN{Léonore Valentine Guillain, Nour Ghalia Abassi}\par
+    \IEEEauthorblockA{EPFL}
+}
 \maketitle
 
-    \(\title(Abstract)\)
-
+\begin{abstract}
     \begin{itemize}
-\tightlist
-\item
-  \#TODO write some sentence about general motivation for bibliometric
-  analysis
+\item ~
+  \section{TODO write some sentence about general motivation for
+  bibliometric
+  analysis}\label{todo-write-some-sentence-about-general-motivation-for-bibliometric-analysis}
 \end{itemize}
@@
 \begin{itemize}
-\tightlist
-\item
-  \#TODO write a few centences about the most central findings
+\item ~
+  \section{TODO write a few centences about the most central
+  findings}\label{todo-write-a-few-centences-about-the-most-central-findings}
 \end{itemize}
+\end{abstract}
+    \section{Introduction}\label{introduction}
 
-    \hypertarget{introduction}{%
-\subsection{1. Introduction}\label{introduction}}
+Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod
+tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim
+veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea
+commodo consequat. Duis aute irure dolor in reprehenderit in voluptate
+velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint
+occaecat cupidatat non proident, sunt in culpa qui officia deserunt
+mollit anim id est laborum.
 
-    \hypertarget{bibliometric-study-to-analyse-the-papers-published-in-the-proceeding-of-the-conferences-organized-by-the-international-learning-science-society.}{%
-\subsection{Bibliometric study to analyse the papers published in the
-Proceeding of the Conferences organized by the International Learning
-Science
-Society.}\label{bibliometric-study-to-analyse-the-papers-published-in-the-proceeding-of-the-conferences-organized-by-the-international-learning-science-society.}}
+    Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod
+tempor incididunt ut labore et dolore magna aliqua \cite{article1}. Ut
+enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut
+aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit
+in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
+Excepteur sint occaecat cupidatat non proident, sunt in culpa qui
+officia deserunt mollit anim id est laborum.
 
-    \hypertarget{data-processing}{%
-\subsection{2. Data Processing}\label{data-processing}}
+Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod
+tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim
+veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea
+commodo consequat \cite{book1,booklet1,conference1}. Duis aute irure
+dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat
+nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in
+culpa qui officia deserunt mollit anim id est laborum.
+
+Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod
+tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim
+veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea
+commodo consequat. Duis aute irure dolor in reprehenderit in voluptate
+velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint
+occaecat cupidatat non proident, sunt in culpa qui officia deserunt
+mollit anim id est laborum.
+
+To illustrate how code, equations and figures are included in the
+notebook, I include a simple technical section (section
+\ref{illustrative-example}) below.
+
+    \subsection{Data Processing}\label{data-processing}
 
@@
 
-    \hypertarget{metadata}{%
-\subsubsection{2.1 Metadata}\label{metadata}}
+    \subsubsection{Metadata}\label{metadata}
 
-\hypertarget{extraction}{%
-\paragraph{Extraction}\label{extraction}}
+\paragraph{Extraction}\label{extraction}
 
@@
     \begin{Verbatim}[commandchars=\\\{\}]
-{\color{incolor}In [{\color{incolor}2}]:} \PY{k+kn}{import} \PY{n+nn}{os} 
-        \PY{k+kn}{import} \PY{n+nn}{pandas} \PY{k+kn}{as} \PY{n+nn}{pd}
-        \PY{n}{rootdir} \PY{o}{=} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{data/papers}\PY{l+s+s1}{\PYZsq{}}
-        \PY{n}{contents} \PY{o}{=} \PY{p}{[}\PY{p}{]}
-        \PY{n}{i} \PY{o}{=} \PY{l+m+mi}{0}
-        \PY{n}{source} \PY{o}{=} \PY{p}{[}\PY{p}{]}
-        \PY{n}{errors} \PY{o}{=} \PY{p}{[}\PY{p}{]}
-        \PY{n}{doc} \PY{o}{=} \PY{p}{[}\PY{p}{]}
-        \PY{n}{year} \PY{o}{=} \PY{p}{[}\PY{p}{]}
-        \PY{k}{for} \PY{n}{subdir}\PY{p}{,} \PY{n}{dirs}\PY{p}{,} \PY{n}{files} \PY{o+ow}{in} \PY{n}{os}\PY{o}{.}\PY{n}{walk}\PY{p}{(}\PY{n}{rootdir}\PY{p}{)}\PY{p}{:}
-            \PY{k}{for} \PY{n+nb}{file} \PY{o+ow}{in} \PY{n}{files}\PY{p}{:}
-                \PY{k}{if} \PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{txt}\PY{l+s+s1}{\PYZsq{}} \PY{o+ow}{in} \PY{n+nb}{file}\PY{p}{:}
-                    \PY{n}{i} \PY{o}{+}\PY{o}{=} \PY{l+m+mi}{1}
-                    \PY{n}{path} \PY{o}{=} \PY{n}{os}\PY{o}{.}\PY{n}{path}\PY{o}{.}\PY{n}{join}\PY{p}{(}\PY{n}{subdir}\PY{p}{,} \PY{n+nb}{file}\PY{p}{)}
-                    \PY{k}{with} \PY{n+nb}{open}\PY{p}{(}\PY{n}{path}\PY{p}{)} \PY{k}{as} \PY{n+nb}{file}\PY{p}{:}
-                        \PY{n}{doc}\PY{o}{.}\PY{n}{append}\PY{p}{(}\PY{n}{path}\PY{o}{.}\PY{n}{split}\PY{p}{(}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{\PYZus{}}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}\PY{p}{[}\PY{l+m+mi}{1}\PY{p}{]}\PY{p}{[}\PY{p}{:}\PY{l+m+mi}{3}\PY{p}{]}\PY{p}{)}
-                        \PY{n}{year}\PY{o}{.}\PY{n}{append}\PY{p}{(}\PY{n+nb}{int}\PY{p}{(}\PY{n}{path}\PY{o}{.}\PY{n}{split}\PY{p}{(}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{/}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}\PY{p}{[}\PY{o}{\PYZhy{}}\PY{l+m+mi}{1}\PY{p}{]}\PY{p}{[}\PY{l+m+mi}{6}\PY{p}{:}\PY{l+m+mi}{10}\PY{p}{]}\PY{p}{)}\PY{p}{)}
-                        \PY{k}{try}\PY{p}{:}
-                            \PY{n}{text} \PY{o}{=} \PY{n+nb}{file}\PY{o}{.}\PY{n}{read}\PY{p}{(}\PY{p}{)}
-                            \PY{k}{if} \PY{n+nb}{len}\PY{p}{(}\PY{n}{text}\PY{p}{)}\PY{o}{\PYZgt{}} \PY{l+m+mi}{10} \PY{p}{:}
-                                \PY{n}{contents}\PY{o}{.}\PY{n}{append}\PY{p}{(}\PY{n}{text}\PY{p}{)}
-                            \PY{n}{source}\PY{o}{.}\PY{n}{append}\PY{p}{(}\PY{n}{subdir}\PY{p}{[}\PY{n+nb}{len}\PY{p}{(}\PY{n}{rootdir}\PY{p}{)}\PY{p}{:}\PY{p}{]}\PY{p}{)}
-                        \PY{k}{except}\PY{p}{:}
-                            \PY{n}{name}\PY{p}{,} \PY{n}{message}\PY{p}{,} \PY{n}{content} \PY{o}{=} \PY{n}{sys}\PY{o}{.}\PY{n}{exc\PYZus{}info}\PY{p}{(}\PY{p}{)}
-                            \PY{n}{errors}\PY{o}{.}\PY{n}{append}\PY{p}{(}\PY{n}{message}\PY{p}{)}
-\end{Verbatim}
-
-    \begin{Verbatim}[commandchars=\\\{\}]
-{\color{incolor}In [{\color{incolor}5}]:} \PY{k}{print}\PY{p}{(}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{Number of papers is : \PYZob{}\PYZcb{}}\PY{l+s+s1}{\PYZsq{}}\PY{o}{.}\PY{n}{format}\PY{p}{(}\PY{n+nb}{len}\PY{p}{(}\PY{n}{contents}\PY{p}{)}\PY{p}{)}\PY{p}{)}
-\end{Verbatim}
-
-    \begin{Verbatim}[commandchars=\\\{\}]
 Number of papers is : 869
@@
 
-    \hypertarget{data-cleaning}{%
-\subsection{Data Cleaning}\label{data-cleaning}}
+    \subsection{Data Cleaning}\label{data-cleaning}
 
-    your part for the references universities parsing \ldots{}
+    your part for the references universities parsing ...
 
-    \hypertarget{text-preprocessing}{%
-\subsubsection{Text preprocessing}\label{text-preprocessing}}
+    \subsubsection{Text preprocessing}\label{text-preprocessing}
 
     From the pdf parser some of the documents were corrupted with some weird
-caracters such as `\xe2\x80\x99s', white space strings \ldots{}
+caracters such as , white space strings
 
@@
 \textbf{\emph{Lemmatization}} is a word variations to the root of the
-word (e.g.~working, works, worked changed to work).
+word (e.g. working, works, worked changed to work).
 \textbf{\emph{Stemming}} is the process of reducing inflected and
@@
 
-    \hypertarget{keywords-extraction}{%
-\subsection{Keywords extraction}\label{keywords-extraction}}
+    \subsection{Keywords extraction}\label{keywords-extraction}
 
@@
 
-    \begin{Verbatim}[commandchars=\\\{\}]
-{\color{incolor}In [{\color{incolor}7}]:} \PY{n}{keywords\PYZus{}df} \PY{o}{=} \PY{n}{pd}\PY{o}{.}\PY{n}{read\PYZus{}csv}\PY{p}{(}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{keywords\PYZus{}final.csv}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}
-\end{Verbatim}
-
-    \begin{Verbatim}[commandchars=\\\{\}]
-{\color{incolor}In [{\color{incolor}30}]:} \PY{k+kn}{import} \PY{n+nn}{matplotlib.pyplot} \PY{k+kn}{as} \PY{n+nn}{plt}
-         \PY{k+kn}{import} \PY{n+nn}{numpy} \PY{k+kn}{as} \PY{n+nn}{np}
-         \PY{n}{x} \PY{o}{=} \PY{n}{plt}\PY{o}{.}\PY{n}{hist}\PY{p}{(}\PY{n+nb}{list}\PY{p}{(}\PY{n}{keywords\PYZus{}df}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{year}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]}\PY{p}{)}\PY{p}{,} \PY{n}{bins}\PY{o}{=}\PY{l+m+mi}{7}\PY{p}{,}\PY{p}{)}
-         \PY{n}{x} \PY{o}{=} \PY{n}{plt}\PY{o}{.}\PY{n}{xticks}\PY{p}{(}\PY{n}{np}\PY{o}{.}\PY{n}{arange}\PY{p}{(}\PY{n+nb}{min}\PY{p}{(}\PY{n}{keywords\PYZus{}df}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{year}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]}\PY{p}{)}\PY{p}{,}\PY{n+nb}{max}\PY{p}{(}\PY{n}{keywords\PYZus{}df}\PY{p}{[}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{year}\PY{l+s+s1}{\PYZsq{}}\PY{p}{]}\PY{o}{+}\PY{l+m+mi}{1}\PY{p}{)} \PY{p}{,} \PY{l+m+mi}{1}\PY{p}{)}\PY{p}{)}
-         \PY{n}{x} \PY{o}{=} \PY{n}{plt}\PY{o}{.}\PY{n}{title}\PY{p}{(}\PY{l+s+s1}{\PYZsq{}}\PY{l+s+s1}{Distribution of the number of documents per year}\PY{l+s+s1}{\PYZsq{}}\PY{p}{)}
-\end{Verbatim}
-
-    \begin{center}
-    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_24_0.png}
-    \end{center}
-    { \hspace*{\fill} \\}
+    \begin{figure}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_27_0.png}\end{center}
+        \caption{}
+        \label{}
+    \end{figure}
 
@@
 
-    \begin{Verbatim}[commandchars=\\\{\}]
-{\color{incolor}In [{\color{incolor}33}]:} \PY{k+kn}{from} \PY{n+nn}{IPython.display} \PY{k+kn}{import} \PY{n}{Image}
-         \PY{n}{Image}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{keywords\PYZus{}by\PYZus{}year.png}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
-\end{Verbatim}
-
 \texttt{\color{outcolor}Out[{\color{outcolor}33}]:}
 
-    \begin{center}
-    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_26_0.png}
-    \end{center}
-    { \hspace*{\fill} \\}
+    \begin{figure}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_29_0.png}\end{center}
+        \caption{}
+        \label{}
+    \end{figure}
 
@@
 graph, the most used word in the papers, more than 10\% of 2015 papers
-uses the word `peer', more than 6\% of the papers uses the words
-`building', `embodied' in 2016. In 2017 the most frequent keyword on is
-`reponsive' and in 2018 `tools' is present with more than 6\%.
-
-    \begin{Verbatim}[commandchars=\\\{\}]
-{\color{incolor}In [{\color{incolor}37}]:} \PY{n}{Image}\PY{p}{(}\PY{l+s+s2}{\PYZdq{}}\PY{l+s+s2}{distinct\PYZus{}words.png}\PY{l+s+s2}{\PYZdq{}}\PY{p}{)}
-\end{Verbatim}
+uses the word 'peer', more than 6\% of the papers uses the words
+'building', 'embodied' in 2016. In 2017 the most frequent keyword on is
+'reponsive' and in 2018 'tools' is present with more than 6\%.
 
@@
 
-    \begin{center}
-    \adjustimage{max size={0.9\linewidth}{0.9\paperheight}}{output_28_0.png}
-    \end{center}
-    { \hspace*{\fill} \\}
+    \begin{figure}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_31_0.png}\end{center}
+        \caption{}
+        \label{}
+    \end{figure}
 
-    \hypertarget{document-clustering}{%
-\subsection{Document Clustering}\label{document-clustering}}
+    \subsection{Document Clustering}\label{document-clustering}
+
+    \section{Illustrative Example}\label{illustrative-example}
+
+For the purposes of illustration, consider a damped harmonic oscillator
+driven by a sinusoidal signal:
+
+\begin{equation}
+\frac{\mathrm{d}^2x}{\mathrm{d}t^2} + 2\zeta\omega_0\frac{\mathrm{d}x}{\mathrm{d}t} + \omega_0^2x = A\sin(\omega t), \label{eq:problem}
+\end{equation}
+
+\noindent where \(x(t)\) is the quantity of interest, \(\zeta\) is the
+damping constant, \(\omega_0\) is the undamped resonant frequency, and
+\(A\sin(\omega t)\) is the driving sinusoidal signal. The steady state
+solution to \eqref{eq:problem} is given by:
+
+\begin{eqnarray}
+x(t) &=& \frac{A}{Z_m\omega}\sin(\omega t + \phi), \label{eq:soln}\\
+Z_m &=& \sqrt{(2\omega_0\zeta)^2+\frac{(\omega^2-\omega_0^2)^2}{\omega^2}}, \nonumber\\
+\phi &=& \arctan\left(\frac{2\omega\omega_0\zeta}{\omega^2-\omega_0^2}\right). \nonumber
+\end{eqnarray}
+
+    \begin{figure}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_40_0.png}\end{center}
+        \caption{Variation of steady-state oscillation amplitude with driving frequency for an oscillator with undamped frequency of 100 Hz, a driving amplitude $A = 10^6$, and various damping constants.}
+        \label{fig1}
+    \end{figure}
+
+    In Figure \ref{fig1} we plot the steady state amplitude of a 100 Hz
+oscillator as a function of driving frequency. We see that the
+oscillator exhibits a strong resonance for small values of \(\zeta\),
+and that the resonance frequency is slightly lower than the driving
+frequency of 100 Hz.
+
+\begin{algorithm}
+\caption{Calculate $y = x^n + z^m$}
+\begin{algorithmic} 
+\REQUIRE $n \geq 0 \vee x \neq 0 \vee z \geq 0 \vee m \neq 0$
+\ENSURE $y = x^n + z^m$
+\STATE $y \leftarrow 1$
+\IF{$n < 0$}
+  \STATE $N \leftarrow -n$
+\ELSE
+  \STATE $N \leftarrow n$
+\ENDIF
+\end{algorithmic}
+\end{algorithm}
+    \section{Conclusions}\label{conclusions}
+
+Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod
+tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim
+veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea
+commodo consequat. Duis aute irure dolor in reprehenderit in voluptate
+velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint
+occaecat cupidatat non proident, sunt in culpa qui officia deserunt
+mollit anim id est laborum.
 
@@
 
+\bibliographystyle{unsrt}
+\bibliography{references}
+
     \end{document}

### 2019-01-04 Scripts/parse_metadata.py
push work

@@ -8,6 +8,9 @@ import re
 import regex
 import numpy as np
 import unicodedata
+import networkx as nx
+import difflib
+from pprint import pprint
 
 parser = argparse.ArgumentParser()
 parser.add_argument('--input', type=str, dest='path', default='papers-import/',  help='specifies the path to input dir')
@@ -199,6 +202,31 @@ for i, m in enumerate(names):
                 d[n]= m
 
 cleaning.loc[cleaning['long_name'].isin(d.keys()), 'long_name'] = cleaning.long_name.map(d)
+print('[Info] Unified the following names')
+pprint(d)
+
+build_graph = cleaning[['long_name', 'shortend_names', 'file']]
+build_graph = pd.merge(build_graph, build_graph, on='file')
+build_graph = build_graph[build_graph.long_name_x != build_graph.long_name_y]
+
+G = nx.from_pandas_edgelist(build_graph, source='long_name_x', target='long_name_y')
+
+threshold = 0.8
+d = dict()
+for name in build_graph.long_name_x.unique():
+    members = sorted(list(G.neighbors(name)))
+    for i, member in enumerate(members):
+            for j, member_2 in enumerate(members):
+                if i < j:
+                    difference = difflib.SequenceMatcher(None, member, member_2).ratio()
+                    if difference > threshold:
+                        d[member] = member_2
+
+print('[Info] Unified the following names')
+pprint(d)
+
+cleaning.loc[cleaning['long_name'].isin(d.keys()), 'long_name'] = cleaning.long_name.map(d)
+
 
 print('[INFO] Saved to individual authors list: {} as Parsed_metadata.csv'.format(output))
 cleaning.to_csv(os.path.join(output, 'Parsed_metadata.csv'))

### 2019-01-05 Scripts/reference_extraction.py
push differences

@@ -3,7 +3,6 @@ import pandas as pd
 import os
 import numpy as np
 import sys
-import matplotlib.pyplot as plt
 import json
 import argparse
 import regex as reg
@@ -28,23 +27,27 @@ def author_title(x):
         end = 0
     return ref[: (search+end)]
 
-
 def ref_extraction(text, extract=False):
-    """Extracts refrerence section: works well on well formated documents"""
+    """extracts refrerence section: on well formated documents"""
     mention = text.rfind("\nReferences")
     if mention == -1:
-        mention = text.lower().rfind(" references")
+        mention = text.rfind("\nReference")
+    if mention == -1 and reg.search('\n[\p{L}]*( |)[\p{L}]*( |)(R|r)eferences\n', text):
+        #to keep everything consistent substract
+            mention =  reg.search('\n[\p{L}]*( |)[\p{L}]*( |)(R|r)eferences\n', text).span()[1] - len("references")
     if mention == -1:
-        mention =  text.lower().rfind("reference")
+        return None
     #get reference section, account for different spelling
-    acknowledgements = max(text.lower().find("acknowledgements"), text.lower().find('acknowledgments'))
+    acknowledgements = max(text.find("Acknowledgement"), text.find('Acknowledgment'), text.find('Appendix'))
 
     #handle case that acknowlege ments are before references
     if acknowledgements < mention:
         acknowledgements = -1
     ref = text[mention+len("references"):acknowledgements]
+
     references = re.split(r'\n', ref)
 
+    #extract references while not extracting bottom text
     ref = [r for r in references if r and len(r) > 3 and not re.match(r'(CSCL|ICLS) \d{4} Proceedings|© ISLS', r)]
     if extract:
         print(text[mention+len("references"):acknowledgements])
@@ -52,32 +55,33 @@ def ref_extraction(text, extract=False):
     return ref
 
 def contains_citation_beginning(sentence):
-    """Checks if string begings with an citation (in APA format)"""
+
     ##Check for mention of publication date,
     #do it this way to not allow for ICLS 2015 string to be counted
     months = '(january|february|march|april|may|june|july|august|september|october|november|december)?'
[…]

### 2019-01-05 Report/paper.tex
push paper update

@@
                                 % normalem makes italics be italics, not underlines
-    \usepackage{mathrsfs}
 
@@
     \definecolor{ansi-white-intense}{HTML}{A1A6B2}
-    \definecolor{ansi-default-inverse-fg}{HTML}{FFFFFF}
-    \definecolor{ansi-default-inverse-bg}{HTML}{000000}
 
@@
     \def\br{\hspace*{\fill} \\* }
-    % Math Jax compatibility definitions
+    % Math Jax compatability definitions
     \def\gt{>}
     \def\lt{<}
-    \let\Oldtex\TeX
-    \let\Oldlatex\LaTeX
-    \renewcommand{\TeX}{\textrm{\Oldtex}}
-    \renewcommand{\LaTeX}{\textrm{\Oldlatex}}
     % Document parameters
-    % Document title
     \title{paper}
@@
 \begin{abstract}
-    \begin{itemize}
-\item ~
-  \section{TODO write some sentence about general motivation for
-  bibliometric
-  analysis}\label{todo-write-some-sentence-about-general-motivation-for-bibliometric-analysis}
-\end{itemize}
-
-We explore ways to extract information from ICLS and CSCL papers to gain
-an understanding about the community formed by conference participants
-and what research is being conducted within the community. After
-describing how to extract data from the original dataset in suitable
-format for analysis we perform an exploratory data analysis after which
-we derive insights into the community using social network analysis and
-{[}Nour: NLP etc{]}.
-
-\begin{itemize}
-\item ~
-  \section{TODO write a few centences about the most central
-  findings}\label{todo-write-a-few-centences-about-the-most-central-findings}
-\end{itemize}
+    \#TODO write some sentence about general motivation for bibliometric
+analysis We explore ways to extract information from ICLS and CSCL
+papers to gain an understanding about the community formed by conference
+participants and what research is being conducted within the community.
+After describing how to extract data from the original dataset in
+suitable format for analysis we perform an exploratory data analysis
+after which we derive insights into the community using social network
+analysis and {[}Nour: NLP etc{]}. \#TODO write a few centences about the
+most central findings
 \end{abstract}
-    \section{Introduction}\label{introduction}
+    \hypertarget{introduction}{%
+\section{Introduction}\label{introduction}}
 
@@
 
-    Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod
-tempor incididunt ut labore et dolore magna aliqua \cite{article1}. Ut
-enim ad minim veniam, quis nostrud exercitation ullamco laboris nisi ut
-aliquip ex ea commodo consequat. Duis aute irure dolor in reprehenderit
-in voluptate velit esse cillum dolore eu fugiat nulla pariatur.
-Excepteur sint occaecat cupidatat non proident, sunt in culpa qui
-officia deserunt mollit anim id est laborum.
+    \hypertarget{data-processing}{%
+\section{Data Processing}\label{data-processing}}
 
-Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod
-tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim
-veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea
-commodo consequat \cite{book1,booklet1,conference1}. Duis aute irure
-dolor in reprehenderit in voluptate velit esse cillum dolore eu fugiat
-nulla pariatur. Excepteur sint occaecat cupidatat non proident, sunt in
-culpa qui officia deserunt mollit anim id est laborum.
+    As a starting point we have papers of 4 years spanning 2015 to 2018 of
+the proceedings of ICLS, which is held in even years, respectively CSCL,
+held in odd years. The overall number of papers per year can be observed
+in figure \(\ref{fig1}\). The provided raw dataset consists of papers in
+pdf format as well as associated metadata in xml format. To extract
+information from the dataset we first need to convert the data a format
+that is more adapt to the task of data exploration and handling with a
+variety of external libraries. We store the data we extract from the
+provided dataset in csv format, as this makes it accessible to any
+scientist and is unlikely to become an obsolete any time soon.
 
-Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod
-tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim
-veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea
-commodo consequat. Duis aute irure dolor in reprehenderit in voluptate
-velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint
-occaecat cupidatat non proident, sunt in culpa qui officia deserunt
-mollit anim id est laborum.
+    \begin{figure}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_8_0.png}\end{center}
+        \caption{Distribution of papers published over the years}
+        \label{fig1}
+    \end{figure}
 
-To illustrate how code, equations and figures are included in the
-notebook, I include a simple technical section (section
-\ref{illustrative-example}) below.
+    \hypertarget{metadata}{%
+\subsection{Metadata}\label{metadata}}
 
-    \subsection{Data Processing}\label{data-processing}
+We extract the xml metadata --using the lxmltree python library-- into a
+csv file containing the information associated to different tags in its
+columns. The provided xml does not exactly follow the xml standard,
+hence we handle errors by iteratively parsing the xml tree. We then add
+columns that reference the name of the source file and the order in
+which an author name occurs in the xml file. From the associated
+citation string we add in a shortened version of author names, and the
+``author names (year) title'' string that we later use to identify a
+paper. Having extracted the metadata we then clean it by unifying names
+as slight spelling differences exist within the same author name. This
+is done by splitting up names based on whitespace and commas. If the
+intersection of the set of substrings of two distinct names contains at
+least 2 names of length at least 3 we consider these two names to be
+identical. Using this we reduce the number of authors in the dataset
+from 1951 down to 1879. To unify the names further, we need to make sure
+to not overmerge by labeling to different authors as having the same
+name. We do this by constructing the graph of co-authorship and then
+only considering names of authors that are in the same neighborhood of a
+node on the graph. Then we use the difflib library to check for
+similarity of two names and merge them if they reach a the threshold of
+0.8. This method again reduces the number of authors in the dataset from
+1879 to 1951.
 
-    To extract information from the dataset we first need to convert the
-data into a suitable format. We store the extracted data in csv format,
-as this makes it accessible to any scientist and can be read as is on
-the GitHub. Only the data frame containing emails is stored in pickle
-format, which is done for privacy reasons.
+    \hypertarget{handling-of-pdf-data}{%
+\subsection{Handling of pdf data}\label{handling-of-pdf-data}}
 
-    \subsubsection{Metadata}\label{metadata}
+To extract information from the papers themselves we need to first
+extract the text from the pdfs. Various parsers performing this task
+exist. However, many parsers {[}pdfminer, PyPDF2{]} that claim to be
+able to extract the text as well as metadata from papers have not been
+kept up to date, which leads to issues with dependencies. We found that
+the most reliable parser is poppler https://poppler.freedesktop.org/.
 
-\paragraph{Extraction}\label{extraction}
+We note that due to inconsistencies with numbering, some of the pdfs
+were not extracted correctly from the proceedings. We make sure to
+handle these cases.
 
-The provided raw dataset consists of papers in pdf format as well as
-associated metadata in xml format. This associated metadata consists of
-: full-length author names, abstract of the paper, associated keywords,
-document type, publisher, title of the paper, time of issue and the
-citation string for the paper. We extract the xml metadata using the
-lxmltree python library into a csv file containing the above listed
-columns. The provided xml does not exactly follow the xml standard,
-hence we handle errors by iteratively parsing the file.
+The advantage of papers is that they are structured fairly regularly.
+From ISLS\_Author\_Guidelines\_Oct2014.pdf we know papers the papers in
+our dataset should be structured. We use this to our advantage when
+extracting information from the paper text. As per
+{[}ISLS\_Author\_Guidelines\_Oct2014{]} the document should be
+structured in the following way: 1. Title 2. Abstract 3. Keywords 4.
+Body of submission (using heading levels 1, 2 and 3 as necessary) 5.
+Endnotes (if needed) 6. References 7. Acknowledgements (if needed)
 
-    \begin{Verbatim}[commandchars=\\\{\}]
-Number of papers is : 869
+\hypertarget{extracting-the-papers-cited-by-a-paper}{%
+\subsection{Extracting the papers cited by a
+paper}\label{extracting-the-papers-cited-by-a-paper}}
 
-    \end{Verbatim}
+We know that each valid paper should contain a reference section at the
+end listing all the references cited in the paper. While there are tools
+being developed to extract the reference section directly from pdfs,
+notably {[}scholarcy{]}, we found that none of them produced
+satisfactory results as of the time writing this report. Hence we resort
+the using regular expressions and our knowledge about how references
+should be presented within the paper.
 
-    Some of the documents are not readable and have some strange format so
-we need to take them out of the analysis. Wwe find ourselves with
-roughly 834 documents
+To get the reference section we use a regular expression to find the
+`Reference' header and cut of at the end if an Acknowledgement or
+Appendix section is present. Python has two modules that implement
+regular expressions re and regex. We used regex as it allows to better
+handle unicode strings by having unicode expressions, which frequently
+occur.
 
-    \subsection{Data Cleaning}\label{data-cleaning}
+To get the individual reference we tested many ways to split up the
+lines, but ultimately, the most robust way was to split up the section
+at each new line and the glue the references back together if the lines
+satisfy a set of conditions.
 
-    your part for the references universities parsing ...
+The underlying idea is that APA references, the standard referencing
+format, all have the same initial structure: Authors (year) title, other
+identifying information. We thus check that the beginning of each
+reference contains ``Authors (year)''. It is relatively easy to check
+for this using regular expressions as Author names and year have a given
+structure. If a string does not contain such a section, then it must be
+part of an other reference, which is lies before in the list of
+reference substrings.
 
-    \subsubsection{Text preprocessing}\label{text-preprocessing}
+Consider that the references strings are structured the following way
+{[}\ldots{}., reference\_part\_i, reference\_part\_i+1, \ldots{}.{]}
+Algorithm: 1. Merge names that were cut up. We detect them by checking
+against the regular expression: \_\_ 2. Check ending for invalid
+sentence endings: reference\_part\_i ends in comma, :, whitespace
+uppercase followed by point. If condition holds reference\_part\_i+1 3.
+Check beginning for invalid reference starts: not starting in a letter.
+Merge with reference\_part\_i if condition holds. 4. Check if a invalid
+reference\_part\_i+1 consists only of the authors names. If so Merge
+with reference\_part\_i 5. Move up all sentences that do not contain
+author names / start of a citation at the beginning 6. Move up all
+sentences that do not have a valid citation start
+
+After this we validate the returned split by looking at the overall
+length and the initials, as well as checking that a random sample
+returns satisfactory splitting accuracy. We find that the above method
+of extracting the references produces good results for proper APA
+citations and on APA citations outperforms Scolarcy.
+
+    \hypertarget{extracting-institution-country}{%
+\subsection{Extracting institution \&
+country}\label{extracting-institution-country}}
+
+Now we consider the information present in the section before the
+abstract, which contains the authors names, their email and the
+institution they are affiliated with. Affiliation with institution can
+give us a lot of insight where people are working and gives use a way
+estimate where they are from. To go from this section to an exact
+affiliation with an institution a multifaceted approach was used.
+
+\hypertarget{approach-1}{%
+\subsubsection{Approach 1}\label{approach-1}}
+
+The most robust way to get a persons institution affiliation is to use
+their email. Emails can easily be extracted from the header section
+using a regular expression and given a domain-university mapping {[}{]}
+give us an onto mapping from domain to institution. The additional
+advantage of this method is that using the additional metadata
+associated to each university in the mapping, we also access information
+about the country of the university.
+
+\hypertarget{approach-2}{%
+\subsubsection{Approach 2}\label{approach-2}}
+
+The header section itself contains information on the institution, but
+as different was to list authors are accepted, notably two ways {[}fig
+\_ a and b{]}. Hence, we first detect the structure of the header
+section before extracting the association. We tag the substring present
+in this section using a combination of named entity detection, using the
+implementation provided by spacy, simple matching of the names of
+authors and institutions we extracted from the metadata respectively
+from Approach 1 and tagging sections containing ``emails'' using regex ,
+to detect where in the header the email is. Then, taking the tagged
+section, we detect which subsections correspond to which
+author-affiliation listing type, and extract the author email -
+institution mapping accordingly.
+
+Approach 2 allows to match many more institutions to authors than
+Approach 1 as not every institution is present in the mapping and many
+participants use gmail and similar providers as their official
+correspondence email we are unable to acquire this information for many
+participants. But, Approach 2 may contain differences in spelling in the
+institution name, which need to be merged. Thus we combine both
+approaches, and use the corresponding institutions in Approach 1 to
+unify the institutions obtained in Approach 2.
+
+As institution affiliation does not allow us to automatically associate
+a country to the institution, we need to get this through additional
+means. A first step is to use the top level domains present in the
+emails to associate a country of origin to the participants \& their
+associated institutions.
+
+Alongside this, to plot the community we augment the dataset with
+geolocation information, having this information we can then easily
+associate a country to the institution.
+
+As there are a variety of way in which the name of an institution could
+be written --consider EPFL, EPF Lausanne-- it was found that crawling
+the english, french and german version of Wikipedia (not using the API,
+or the API wrapper, as this does not give access to the desired
+information) and using beautiful soup the get the coordinates present in
+the article was a quick and accurate way to get the location as the
+website directs to the relevant article on the institution even when
+misspellings are present. But not all institutions, even well known ones
+such as Tokyo University, have their coordinates listed on their
+Wikipedia. To get the remaining locations we use the geopy, which is a
+client for geocoding web services. These results however are more error
+prone and will always return a result. Then, to get the country we can
+then again use geopy. The resulting data containing paper identifier,
+the authors email, it's associated domain, order in which the author was
+cited, the institution, country, Longitude and Latitude are saved to
+csv. We use the paper identifier and author order to associate this data
+with the metadata to link information about authors with the papers they
+authored.
+
+    \hypertarget{keywords-extraction}{%
+\subsection{Keywords extraction}\label{keywords-extraction}}
+
+    \hypertarget{text-preprocessing}{%
+\subsubsection{Text preprocessing}\label{text-preprocessing}}
 
@@
 \textbf{\emph{Lemmatization}} is a word variations to the root of the
-word (e.g. working, works, worked changed to work).
+word (e.g.~working, works, worked changed to work).
 \textbf{\emph{Stemming}} is the process of reducing inflected and
@@
 stanford word embedding and we did not wand to loose interpretability.
-
-    \subsection{Keywords extraction}\label{keywords-extraction}
 
@@
 
-    \begin{figure}
-        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_27_0.png}\end{center}
-        \caption{}
-        \label{}
-    \end{figure}
-
     Since we don't have the same number of documents for each year we needed
@@
     \begin{figure}
-        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_29_0.png}\end{center}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_25_0.png}\end{center}
         \caption{}
@@
 graph, the most used word in the papers, more than 10\% of 2015 papers
-uses the word 'peer', more than 6\% of the papers uses the words
-'building', 'embodied' in 2016. In 2017 the most frequent keyword on is
-'reponsive' and in 2018 'tools' is present with more than 6\%.
+uses the word `peer', more than 6\% of the papers uses the words
+`building', `embodied' in 2016. In 2017 the most frequent keyword on is
+`reponsive' and in 2018 `tools' is present with more than 6\%.
 
-\texttt{\color{outcolor}Out[{\color{outcolor}37}]:}
+    \hypertarget{methodology}{%
+\section{Methodology}\label{methodology}}
 
-    \begin{figure}
-        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_31_0.png}\end{center}
-        \caption{}
-        \label{}
-    \end{figure}
+    \hypertarget{document-clustering}{%
+\subsection{Document Clustering}\label{document-clustering}}
 
-    \subsection{Document Clustering}\label{document-clustering}
-
-    \section{Illustrative Example}\label{illustrative-example}
+    \hypertarget{illustrative-example}{%
+\section{Illustrative Example}\label{illustrative-example}}
 
 For the purposes of illustration, consider a damped harmonic oscillator
-driven by a sinusoidal signal:
-
-\begin{equation}
+driven by a sinusoidal signal: \begin{equation}
 \frac{\mathrm{d}^2x}{\mathrm{d}t^2} + 2\zeta\omega_0\frac{\mathrm{d}x}{\mathrm{d}t} + \omega_0^2x = A\sin(\omega t), \label{eq:problem}
-\end{equation}
-
-\noindent where \(x(t)\) is the quantity of interest, \(\zeta\) is the
-damping constant, \(\omega_0\) is the undamped resonant frequency, and
-\(A\sin(\omega t)\) is the driving sinusoidal signal. The steady state
-solution to \eqref{eq:problem} is given by:
-
+\end{equation} \noindent where \(x(t)\) is the quantity of interest,
+\(\zeta\) is the damping constant, \(\omega_0\) is the undamped resonant
+frequency, and \(A\sin(\omega t)\) is the driving sinusoidal signal. The
+steady state solution to \eqref{eq:problem} is given by:
 \begin{eqnarray}
@@
     \begin{figure}
-        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_40_0.png}\end{center}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_34_0.png}\end{center}
         \caption{Variation of steady-state oscillation amplitude with driving frequency for an oscillator with undamped frequency of 100 Hz, a driving amplitude $A = 10^6$, and various damping constants.}
-        \label{fig1}
+        \label{figtest}
     \end{figure}
@@
 \end{algorithm}
-    \section{Conclusions}\label{conclusions}
+    \hypertarget{conclusions}{%
+\section{Conclusions}\label{conclusions}}
 

### 2019-01-05 Scripts/parse_metadata.py

@@ -77,6 +77,7 @@ def convert(arg):
 def extract_author(text):
     author_split = r'([\p{L}\-]*[\,] [\p{L}\.\ \-]*[\&\,\.]?)'
     author_split_2 = r'([\p{L}\-\.\ ]* [\p{L}\. \ \-]*[\,\.]?)'
+    text =  unicodedata.normalize('NFC', text)
     if regex.match('^([\p{L}\ \-]*\p{Lu}\.\,)', text):
         split = [a.replace(',', '').replace('&', '').rstrip() for a in regex.findall(
             author_split_2, text[:text.find('(')])]
@@ -105,7 +106,7 @@ def extract_author(text):
 
 
 def get_authors_month(sentence, debug = False):
-    general = r'[ééüş\xad\p{L}\,\ \.\:\;\/\&\-\'\`\(\)\’\–\¨\…\‐\*\´\＆\\]*\([\,\ \p{L}\d\-]*(18|19|20)\d{2}[\,\ \p{L}\d\-]*\)'
+    general = r'[\p{L}\,\ \.\:\;\/\&\-\'\`\(\)\’\–\¨\…\‐\*\´\＆\\]*\([\,\ \p{L}\d\-]*(18|19|20)\d{2}[\,\ \p{L}\d\-]*\)'
     match_bad_year = r'[\S\s]*\((18|19|20)\d{2}\/(18|19|20)\d{2}\)'
 
     match_press = r'[\S\s]*\((i|I)n (P|p)ress|manuscript under review\)'
@@ -114,7 +115,7 @@ def get_authors_month(sentence, debug = False):
     match_submitted = r'[\S\s]*\((s|S)ubmitted\)'
     match_underreview = r'[\S\s]*\((u|U)nder (R|r)eview\)'
 
-    #sentence = sentence.lower()
+    sentence =  unicodedata.normalize('NFC', sentence)
     if regex.match(general, sentence):
         s = regex.search(general, sentence).group(0)
         if len(s) > 9:

### 2019-01-05 Report/paper.tex
push report changes

@@
 
-    \hypertarget{metadata}{%
-\subsection{Metadata}\label{metadata}}
+    \hypertarget{processing-the-metadata}{%
+\subsection{Processing the Metadata}\label{processing-the-metadata}}
 
-We extract the xml metadata --using the lxmltree python library-- into a
-csv file containing the information associated to different tags in its
-columns. The provided xml does not exactly follow the xml standard,
-hence we handle errors by iteratively parsing the xml tree. We then add
-columns that reference the name of the source file and the order in
-which an author name occurs in the xml file. From the associated
-citation string we add in a shortened version of author names, and the
-``author names (year) title'' string that we later use to identify a
-paper. Having extracted the metadata we then clean it by unifying names
-as slight spelling differences exist within the same author name. This
-is done by splitting up names based on whitespace and commas. If the
-intersection of the set of substrings of two distinct names contains at
-least 2 names of length at least 3 we consider these two names to be
-identical. Using this we reduce the number of authors in the dataset
-from 1951 down to 1879. To unify the names further, we need to make sure
-to not overmerge by labeling to different authors as having the same
-name. We do this by constructing the graph of co-authorship and then
-only considering names of authors that are in the same neighborhood of a
-node on the graph. Then we use the difflib library to check for
+We extract the xml metadata into a csv file containing the information
+associated to different tags in its columns using the \emph{lxmltree}
+python library. The provided xml does not exactly follow the xml
+standard, hence we handle errors by iteratively parsing the xml tree. We
+then add columns that reference the name of the source file and the
+order in which an author name occurs in the xml file. From the
+associated citation string we add in a shortened version of author
+names, and the ``author names (year) title'' string that we later use to
+identify a paper. Having extracted the metadata we then clean it by
+unifying names as slight spelling differences exist within the same
+author name. This is done by splitting up names based on whitespace and
+commas. If the intersection of the set of substrings of two distinct
+names contains at least 2 names of length at least 3 we consider these
+two names to be identical. Using this we reduce the number of authors in
+the dataset from 1951 down to 1879. To unify the names further, we need
+to make sure to not overmerge by labeling to different authors as having
+the same name. We do this by constructing the graph of co-authorship and
+then only considering names of authors that are in the same neighborhood
+of a node on the graph. Then we use the difflib library to check for
 similarity of two names and merge them if they reach a the threshold of
@@
 extract the text from the pdfs. Various parsers performing this task
-exist. However, many parsers {[}pdfminer, PyPDF2{]} that claim to be
-able to extract the text as well as metadata from papers have not been
-kept up to date, which leads to issues with dependencies. We found that
-the most reliable parser is poppler https://poppler.freedesktop.org/.
-
-We note that due to inconsistencies with numbering, some of the pdfs
-were not extracted correctly from the proceedings. We make sure to
-handle these cases.
+exist. However, many parsers {[}pdfminer, PyPDF2{]} claiming to be able
+to extract the text as well as metadata from papers have not been kept
+up to date, which leads to issues with dependencies. We found that the
+most reliable parser is poppler https://poppler.freedesktop.org/. We
+note that due to inconsistencies with numbering, some of the pdfs were
+not extracted correctly from the proceedings which leads to text files
+that are either empty or do not contain the text of the paper referenced
+in the metadata.
 
 The advantage of papers is that they are structured fairly regularly.
-From ISLS\_Author\_Guidelines\_Oct2014.pdf we know papers the papers in
-our dataset should be structured. We use this to our advantage when
-extracting information from the paper text. As per
-{[}ISLS\_Author\_Guidelines\_Oct2014{]} the document should be
-structured in the following way: 1. Title 2. Abstract 3. Keywords 4.
-Body of submission (using heading levels 1, 2 and 3 as necessary) 5.
-Endnotes (if needed) 6. References 7. Acknowledgements (if needed)
+From ISLS Guildines \ref{ISLS_Author_Guidelines_Oct2014.pdf} we know
+papers the papers in our dataset should be structured. We use this to
+our advantage in the following sections when extracting information from
+the paper text.
 
@@
 Appendix section is present. Python has two modules that implement
-regular expressions re and regex. We used regex as it allows to better
-handle unicode strings by having unicode expressions, which frequently
-occur.
-
-To get the individual reference we tested many ways to split up the
-lines, but ultimately, the most robust way was to split up the section
-at each new line and the glue the references back together if the lines
-satisfy a set of conditions.
-
-The underlying idea is that APA references, the standard referencing
+regular expressions \emph{re} and \emph{regex}. We used regex as it
+allows to better handle unicode strings by having unicode expressions.
+This is important as many authors have names that do contain non-ascii
+characters. To get the individual reference we tested many ways to split
+up the lines, but ultimately, the most robust way was to split up the
+section at each new line and the glue the references back together if
+the lines satisfy a set of conditions.\\
+- The underlying idea is that APA references, the standard referencing
 format, all have the same initial structure: Authors (year) title, other
@@
 {[}\ldots{}., reference\_part\_i, reference\_part\_i+1, \ldots{}.{]}
-Algorithm: 1. Merge names that were cut up. We detect them by checking
-against the regular expression: \_\_ 2. Check ending for invalid
-sentence endings: reference\_part\_i ends in comma, :, whitespace
-uppercase followed by point. If condition holds reference\_part\_i+1 3.
-Check beginning for invalid reference starts: not starting in a letter.
-Merge with reference\_part\_i if condition holds. 4. Check if a invalid
-reference\_part\_i+1 consists only of the authors names. If so Merge
-with reference\_part\_i 5. Move up all sentences that do not contain
-author names / start of a citation at the beginning 6. Move up all
-sentences that do not have a valid citation start
+Algorithm:
 
-After this we validate the returned split by looking at the overall
+\[
+1. Merge names that were cut up. We detect them by checking against the regular expression: __ 
+2. Check ending for invalid sentence endings:  reference_part_i ends in comma, :, whitespace uppercase followed by point. If condition holds reference_part_i+1
+3. Check beginning for invalid reference starts: not starting in a letter. Merge with reference_part_i if condition holds.
+4. Check if a  invalid reference_part_i+1 consists only of the authors names. If so Merge with reference_part_i
+5. Move up all sentences that do not contain author names / start of a citation at the beginning 
+6. Move up all sentences that do not have a valid citation start
+\] After this we validate the returned split by looking at the overall
 length and the initials, as well as checking that a random sample
@@
 
-    \hypertarget{extracting-institution-country}{%
-\subsection{Extracting institution \&
-country}\label{extracting-institution-country}}
+    \hypertarget{extracting-institution-and-location}{%
+\subsection{Extracting Institution and
+Location}\label{extracting-institution-and-location}}
 
@@
 approaches, and use the corresponding institutions in Approach 1 to
-unify the institutions obtained in Approach 2.
-
-As institution affiliation does not allow us to automatically associate
-a country to the institution, we need to get this through additional
-means. A first step is to use the top level domains present in the
-emails to associate a country of origin to the participants \& their
-associated institutions.
-
-Alongside this, to plot the community we augment the dataset with
-geolocation information, having this information we can then easily
-associate a country to the institution.
+unify the institutions obtained in Approach 2. As institution
+affiliation does not allow us to automatically associate a country to
+the institution, we need to get this through additional means. A first
+step is to use the top level domains present in the emails to associate
+a country of origin to the participants \& their associated
+institutions. Alongside this, to plot the community we augment the
+dataset with geolocation information, having this information we can
+then easily associate a country to the institution.
 
@@
 or the API wrapper, as this does not give access to the desired
-information) and using beautiful soup the get the coordinates present in
-the article was a quick and accurate way to get the location as the
-website directs to the relevant article on the institution even when
-misspellings are present. But not all institutions, even well known ones
-such as Tokyo University, have their coordinates listed on their
+information) and using \emph{BeautifulSoup} the get the coordinates
+present in the article was a quick and accurate way to get the location
+as the website directs to the relevant article on the institution even
+when misspellings are present. But not all institutions, even well known
+ones such as Tokyo University, have their coordinates listed on their
 Wikipedia. To get the remaining locations we use the geopy, which is a
@@
 
-\texttt{\color{outcolor}Out[{\color{outcolor}33}]:}
+\texttt{\color{outcolor}Out[{\color{outcolor}20}]:}
 
@@
 
-    \hypertarget{methodology}{%
-\section{Methodology}\label{methodology}}
+    \hypertarget{methodology-find-better-section-head..}{%
+\section{Methodology {[}find better section
+head..{]}}\label{methodology-find-better-section-head..}}
 
@@
 \subsection{Document Clustering}\label{document-clustering}}
+
+    \hypertarget{results}{%
+\section{Results}\label{results}}
 
@@
     \begin{figure}
-        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_34_0.png}\end{center}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_35_0.png}\end{center}
         \caption{Variation of steady-state oscillation amplitude with driving frequency for an oscillator with undamped frequency of 100 Hz, a driving amplitude $A = 10^6$, and various damping constants.}

### 2019-01-05 Report/paper.tex

@@
 the proceedings of ICLS, which is held in even years, respectively CSCL,
-held in odd years. The overall number of papers per year can be observed
-in figure \(\ref{fig1}\). The provided raw dataset consists of papers in
+held in odd years. The overall number of papers per year is shown in
+figure \(\ref{fig1}\). The provided raw dataset consists of papers in
 pdf format as well as associated metadata in xml format. To extract
@@
 
+    \hypertarget{co-authorship-graphs}{%
+\subsection{Co-authorship graphs}\label{co-authorship-graphs}}
+
+\hypertarget{interactive-map-visualizations}{%
+\subsection{Interactive Map
+visualizations}\label{interactive-map-visualizations}}
+
     \hypertarget{results}{%
 \section{Results}\label{results}}
+
+    \hypertarget{community-composition-structure}{%
+\subsection{Community Composition \&
+Structure}\label{community-composition-structure}}
+
+We find that participants from 372 institutions participated over the
+last 4 years, with a median of 128 institutions per year. Numbers of
+institutions participating are increasing each year, with a noticeable
+peak in 2018, which participants from 261 institutions. This is a
+considerable up from the last conference ICLS in 2016 which had 135
+participating institutions. Most participants are from the US, with a
+average of 50\% of all participants being from the US. We can also
+observe a trend of increase in US participants with only 35\% of US
+participants in 2015 and 51\% in 2017, followed by 64\% in 2018.
+Overall, participants from 41 nations have participated over the 4
+years, which an average of 28 nations represented each conference. After
+the US, participants of Germany, Canada and Singapore make up the
+biggest proportion of participants \(\ref{figrep}\).
+
+\begin{verbatim}
+1. Collaboration
+2. Movement of participants
+3. Citation
+\end{verbatim}
+
+    \begin{figure}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_33_0.png}\end{center}
+        \caption{}
+        \label{}
+    \end{figure}
+
+    \hypertarget{collaboration}{%
+\subsubsection{Collaboration}\label{collaboration}}
+
+\texttt{\color{outcolor}Out[{\color{outcolor}135}]:}
+
+    \begin{figure}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_35_0.png}\end{center}
+        \caption{Collaborative papers between countries}
+        \label{figcollab}
+    \end{figure}
+
+    \hypertarget{research-topics-in-the-community}{%
+\subsection{Research topics in the
+Community}\label{research-topics-in-the-community}}
+
+\begin{verbatim}
+1. Keywords
+2. Outside influence: Conferences being sited
+\end{verbatim}
 
@@
     \begin{figure}
-        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_35_0.png}\end{center}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_42_0.png}\end{center}
         \caption{Variation of steady-state oscillation amplitude with driving frequency for an oscillator with undamped frequency of 100 Hz, a driving amplitude $A = 10^6$, and various damping constants.}

### 2019-01-06 Report/paper.tex
push new notebooks

@@
 
-\texttt{\color{outcolor}Out[{\color{outcolor}20}]:}
-
     \begin{figure}
@@
     \begin{figure}
-        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_33_0.png}\end{center}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_32_0.png}\end{center}
         \caption{}
@@
 
-\texttt{\color{outcolor}Out[{\color{outcolor}135}]:}
-
     \begin{figure}
-        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_35_0.png}\end{center}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_34_0.png}\end{center}
         \caption{Collaborative papers between countries}
@@
     \begin{figure}
-        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_42_0.png}\end{center}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_41_0.png}\end{center}
         \caption{Variation of steady-state oscillation amplitude with driving frequency for an oscillator with undamped frequency of 100 Hz, a driving amplitude $A = 10^6$, and various damping constants.}

### 2019-01-09 Report/paper.tex
pushing new graphs
push references

@@
 \begin{abstract}
-    \#TODO write some sentence about general motivation for bibliometric
-analysis We explore ways to extract information from ICLS and CSCL
-papers to gain an understanding about the community formed by conference
-participants and what research is being conducted within the community.
-After describing how to extract data from the original dataset in
-suitable format for analysis we perform an exploratory data analysis
-after which we derive insights into the community using social network
-analysis and {[}Nour: NLP etc{]}. \#TODO write a few centences about the
-most central findings
+    In this report we explore ways to automatically analyze ICLS and CSCL
+papers to gain an understanding of the community formed by conferences
+participants and of the research being conducted within the community.
+After describing how to extract data from the original dataset we we
+derive insights into the community using social network analysis and
+{[}Nour: NLP etc{]}. We discover patterns of collaboration between
+participants, their migration and the global spread of the community.
+{[}Something about the insights in keywords/NLP/Co-Citation{]}
 \end{abstract}
@@
 
-Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod
-tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim
-veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea
-commodo consequat. Duis aute irure dolor in reprehenderit in voluptate
-velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint
-occaecat cupidatat non proident, sunt in culpa qui officia deserunt
-mollit anim id est laborum.
+The starting point of the project are the proceedings of the
+International Conference of the Learning Sciences (ICLS), respectively
+the International Conference on Computer-Supported Collaborative
+Learning (CSCL). The two conferences are organized by the International
+Society of the Learning Sciences (ISLS) and held in biennial alternation
+with each other. At the time of writing the dataset contains 4 years of
+the proceedings, staring from 2015 to 2018. While ICLS covers the entire
+field of the learning sciences, CSCL focuses on learning through
+collaboration with the help of communication technologies \cite{ICLS}.
+To understand the community formed by the participants of the
+conferences as well as to understand the research being conducted within
+the community, we explore methods to bring insight into the following
+aspects:
+
+\begin{itemize}
+\tightlist
+\item
+  the institutions and countries dominant in the conferences
+\item
+  the differences between ICLS and CSCL with respect to citations,
+  contributors and publications
+\item
+  first insight into changes of the years with respect to citations,
+  contributors and publications
+\item
+  collaboration network patterns with respect to countries, institutions
+  and authors
+\item
+  the migration of participants across institutions
+\item
+  \ldots{} {[}Nour{]}
+\end{itemize}
+
+To this means we first present an extensive pipeline to process the
+textual data and extract features relevant to bibliographic analysis
+from the textual data. After this we perform a first bibliographic
+analysis based on the extracted data.
 
@@
 
-    As a starting point we have papers of 4 years spanning 2015 to 2018 of
-the proceedings of ICLS, which is held in even years, respectively CSCL,
-held in odd years. The overall number of papers per year is shown in
-figure \(\ref{fig1}\). The provided raw dataset consists of papers in
-pdf format as well as associated metadata in xml format. To extract
-information from the dataset we first need to convert the data a format
-that is more adapt to the task of data exploration and handling with a
-variety of external libraries. We store the data we extract from the
-provided dataset in csv format, as this makes it accessible to any
-scientist and is unlikely to become an obsolete any time soon.
+    The provided raw dataset consists of papers in \emph{pdf} format, as
+well as associated metadata in \emph{xml} format. To extract information
+from the dataset we first convert the data to a format that is more
+adapt to the task of data analysis and more compatible with a variety of
+external libraries. We store all the resulting data in \emph{csv}
+format, as csv is a human readable format and can easily be processed by
+all the data analysis tools we employ.
 
     \begin{figure}
-        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_8_0.png}\end{center}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_7_0.png}\end{center}
         \caption{Distribution of papers published over the years}
@@
 
-We extract the xml metadata into a csv file containing the information
-associated to different tags in its columns using the \emph{lxmltree}
-python library. The provided xml does not exactly follow the xml
-standard, hence we handle errors by iteratively parsing the xml tree. We
-then add columns that reference the name of the source file and the
-order in which an author name occurs in the xml file. From the
-associated citation string we add in a shortened version of author
-names, and the ``author names (year) title'' string that we later use to
-identify a paper. Having extracted the metadata we then clean it by
-unifying names as slight spelling differences exist within the same
-author name. This is done by splitting up names based on whitespace and
-commas. If the intersection of the set of substrings of two distinct
-names contains at least 2 names of length at least 3 we consider these
-two names to be identical. Using this we reduce the number of authors in
-the dataset from 1951 down to 1879. To unify the names further, we need
-to make sure to not overmerge by labeling to different authors as having
-the same name. We do this by constructing the graph of co-authorship and
-then only considering names of authors that are in the same neighborhood
-of a node on the graph. Then we use the difflib library to check for
-similarity of two names and merge them if they reach a the threshold of
-0.8. This method again reduces the number of authors in the dataset from
-1879 to 1951.
+We extract the metadata from the xml files using the \emph{lxmltree}
+python library. We associate the contents of each xml tag to a column in
+csv file. As the xml files do not exactly follow the xml standard, we
+handle errors by iteratively parsing the xml tree. For some files, the
+section containing the keywords is malformed which can not be handled by
+the parser. This is remedied by using regular expressions to match the
+section contains the keywords. To each file we associate the name of the
+source file and the order in which an author name occurs in the xml
+file. Each author is associated one line in the XML file. From the
+associated citation string we add to the first part of the citation
+containing the author names, year and title. which we use to identify
+references in other papers to that paper. Then we add a shortened
+version of author names (i.e.~West, R.) by considering the author order.
+Note that the short name extracted from the citation and the
+corresponding long name (Robert West) in the metadata do at times not
+match up. Thus the author order listed in the citation string does not
+always correspond to the author order listed in the metadata. After
+extraction, we clean the data by unifying names, as slight spelling
+differences exist within the same author name (i.e.~Robert West, Robert
+A. West). When unifying the names we need to make sure to not overmerge
+by labeling to different authors as having the same name. First, we use
+a strict condition to catch small differences in names, such as an extra
+middle name. This is done by splitting up names into substrings based on
+whitespace and commas. For two names in the dataset we check whether the
+intersection of their sets of substrings contains at least 2 names of
+length at least 3. If the condition is met we consider these two names
+to be identical, and add the mapping from one name to the other to a
+dictionary. Once all tuples of names (s.t. the first name appears before
+the second one in order) are checked and added to the dictionary we
+unify the names. Using this method we reduce the number of authors in
+the dataset from 1951 down to 1879. Further, to merge names with
+misspellings or people that use nicknames (Christian vs Chris) and avoid
+over-merging we consider only names of authors that have similar
+collaboration patterns. To do this we build the graph of co-authors and
+check names of authors that are in the same neighborhood of a node on
+the graph (see methodology for further details). Then we use the
+\emph{difflib} library to check for similarity of two strings and
+consider a name to belong to the same person if they reach the threshold
+of 0.8. Again names considered to belong to the same person are added to
+the mapping dictionary which is then applied to all names. This method
+again reduces the number of authors in the dataset from 1879 to 1951.
 
@@
 extract the text from the pdfs. Various parsers performing this task
-exist. However, many parsers {[}pdfminer, PyPDF2{]} claiming to be able
+exist. However, parsers such as pdfminer, PyPDF2 that claim to be able
 to extract the text as well as metadata from papers have not been kept
 up to date, which leads to issues with dependencies. We found that the
-most reliable parser is poppler https://poppler.freedesktop.org/. We
-note that due to inconsistencies with numbering, some of the pdfs were
-not extracted correctly from the proceedings which leads to text files
-that are either empty or do not contain the text of the paper referenced
-in the metadata.
+most reliable parser is \emph{poppler} \cite{poppler} which can be
+installed and then used via the command line to extract the text
+contained in the pdfs to \emph{txt} format. All methods describing how
+to extract data from the papers work on the extracted \emph{txt} files.
+The characters contained in the \emph{txt} files are not all encoded
+uniformly, which means that characters that look the same to humans may
+be encoded in different way . Hence, for many applications we need to
+unify the formating. This is done using the \emph{unicodedata} module
+and setting converting all characters to `Normal Form Composed' form .
 
-The advantage of papers is that they are structured fairly regularly.
-From ISLS Guildines \ref{ISLS_Author_Guidelines_Oct2014.pdf} we know
-papers the papers in our dataset should be structured. We use this to
-our advantage in the following sections when extracting information from
-the paper text.
+A convenient property of papers is that they are structured fairly
+regularly. The ISLS Author Guidelines \cite{guidelines} give us guidance
+on how the papers in our dataset should be structured. We use this to
+our advantage when extracting information from the paper text. While the
+vast majority of papers in the dataset follow these guidelines,
+exceptions do exist. We thus make sure to handle deviations from the
+structure.
 
@@
 
-We know that each valid paper should contain a reference section at the
-end listing all the references cited in the paper. While there are tools
-being developed to extract the reference section directly from pdfs,
-notably {[}scholarcy{]}, we found that none of them produced
-satisfactory results as of the time writing this report. Hence we resort
-the using regular expressions and our knowledge about how references
-should be presented within the paper.
+We know that each valid paper contains a reference section at the end
+listing all the references cited in the paper. While tools are being
+developed to extract the reference section directly from pdfs, notably
+Scholarcy \cite{scholarcy}, they did not produce satisfactory results.
+That is they had issues splitting the references correctly and
+categorizing parts of the reference accurately. This may occur because
+they are trained to extract any reference format, and thus can not make
+many assumptions on the structure. But in our dataset papers following
+the guidelines should list their references in APA format. Hence using
+regular expressions and background on how APA references gives us better
+results than out of the box methods.
 
-To get the reference section we use a regular expression to find the
-`Reference' header and cut of at the end if an Acknowledgement or
-Appendix section is present. Python has two modules that implement
-regular expressions \emph{re} and \emph{regex}. We used regex as it
-allows to better handle unicode strings by having unicode expressions.
-This is important as many authors have names that do contain non-ascii
-characters. To get the individual reference we tested many ways to split
-up the lines, but ultimately, the most robust way was to split up the
-section at each new line and the glue the references back together if
-the lines satisfy a set of conditions.\\
-- The underlying idea is that APA references, the standard referencing
-format, all have the same initial structure: Authors (year) title, other
-identifying information. We thus check that the beginning of each
-reference contains ``Authors (year)''. It is relatively easy to check
-for this using regular expressions as Author names and year have a given
-structure. If a string does not contain such a section, then it must be
-part of an other reference, which is lies before in the list of
-reference substrings.
+\textbf{Regular expressions in python:} Python has two modules that
+implement regular expressions \emph{re} and \emph{regex}. We used regex
+as --unlike the re module-- this module allows to handle strings with
+non-ascii characters by having unicode expressions. As many authors have
+names with non-ascii characters this is an important capability.
 
-Consider that the references strings are structured the following way
-{[}\ldots{}., reference\_part\_i, reference\_part\_i+1, \ldots{}.{]}
-Algorithm:
+\textbf{To get the reference section for of a paper} we use a regular
+expressions to find the reference header and determine the sections end
+by checking for acknowledgement or appendix sections in the text file
+previously extracted using poppler. Then, to extract individual
+references we split the section into a list of substrings at each new
+line character and glue substrings back together if they satisfy a set
+of conditions. We found this method to be robust as it makes sure that
+all properly formatted references are separated.
 
-\[
-1. Merge names that were cut up. We detect them by checking against the regular expression: __ 
-2. Check ending for invalid sentence endings:  reference_part_i ends in comma, :, whitespace uppercase followed by point. If condition holds reference_part_i+1
-3. Check beginning for invalid reference starts: not starting in a letter. Merge with reference_part_i if condition holds.
-4. Check if a  invalid reference_part_i+1 consists only of the authors names. If so Merge with reference_part_i
-5. Move up all sentences that do not contain author names / start of a citation at the beginning 
-6. Move up all sentences that do not have a valid citation start
-\] After this we validate the returned split by looking at the overall
-length and the initials, as well as checking that a random sample
-returns satisfactory splitting accuracy. We find that the above method
-of extracting the references produces good results for proper APA
-citations and on APA citations outperforms Scolarcy.
+\textbf{To glue back substrings} we exploit the fact that that APA
+references all have the same initial structure: \emph{Lastname F.M.
+(when published) Title which may contain colons and other non-alphabetic
+chars. Where published. Who published} \cite{apaformat}. We thus check
+that the beginning of each reference contains ``Lastname F.M. (when
+published)''. It is relatively easy to check for this using regular
+expressions as author names and year have a given structure. If a string
+does not contain such a section, then it must be part of an other
+reference, which is lies before in the list of reference substrings.
+Note that this beginning is also what is added to the metadata as
+identifying string. We found that in practical application it is
+important to first merge lines if they were clearly cut off, as papers
+with many authors may have the beginning on multiple lines. We can find
+split up lines by checking for lines starting with non-alphabetic
+characters or starting in a sentence. We merge these with the line
+above. We can identify lines by their ending as being split up, such as
+if they end in a comma, colon or only contain author names. We merge
+these lines with the lines below them. Only then can we check whether a
+line contains a valid citation start. If it does not we merge it with
+the line above it. After this merging process we validate the returned
+reference split by looking at the overall length and the initials, as
+well as checking that a random sample returns satisfactory splitting
+accuracy. We find that the above method of extracting the references
+produces good results for proper APA citations and on APA citations
+indeed outperforms Scolarcy when it comes to splitting up the lines.
+\emph{To then get the subcomponents of a reference} is rather trivial,
+as we can again use the structure of APA citations. The string before
+the first parenthesis contains the authors names, inside the parentheses
+we find the year or some other reference to publication time, after
+which the title follows until the first dot. Then a reference to the
+publishing venue follows.
+
+    \begin{figure}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_10_0.png}\end{center}
+        \caption{Different formats used to reference institution}
+        \label{figA}
+    \end{figure}
+
+    \begin{figure}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_10_1.png}\end{center}
+        \caption{Different formats used to reference institution}
+        \label{figA}
+    \end{figure}
 
@@
 
-Now we consider the information present in the section before the
-abstract, which contains the authors names, their email and the
-institution they are affiliated with. Affiliation with institution can
-give us a lot of insight where people are working and gives use a way
-estimate where they are from. To go from this section to an exact
-affiliation with an institution a multifaceted approach was used.
+Now we consider the section before the abstract, which contains the
+authors names, their email and the institution they are affiliated with.
+Affiliation with institution can give us a lot of insight where people
+are working and gives use a way estimate where they are from. To go from
+this section to an exact affiliation with an institution a multifaceted
+approach was used.
 
@@
 their email. Emails can easily be extracted from the header section
-using a regular expression and given a domain-university mapping {[}{]}
-give us an onto mapping from domain to institution. The additional
-advantage of this method is that using the additional metadata
-associated to each university in the mapping, we also access information
-about the country of the university.
+using a regular expression and given a domain-university mapping
+\cite{mapping} give us an onto mapping from domain to institution. The
+additional advantage of this method is that using the additional
+metadata associated to each university in the mapping, we also access
+information about the country of the university.
 
@@
 The header section itself contains information on the institution, but
-as different was to list authors are accepted, notably two ways {[}fig
-\_ a and b{]}. Hence, we first detect the structure of the header
-section before extracting the association. We tag the substring present
-in this section using a combination of named entity detection, using the
-implementation provided by spacy, simple matching of the names of
-authors and institutions we extracted from the metadata respectively
-from Approach 1 and tagging sections containing ``emails'' using regex ,
-to detect where in the header the email is. Then, taking the tagged
-section, we detect which subsections correspond to which
-author-affiliation listing type, and extract the author email -
-institution mapping accordingly.
+as different was to list authors are accepted, notably two ways as can
+be seen in \ref{figA} \ref{figB}. Hence, we first detect the structure
+of the header section before extracting the association. We tag the
+substring present in this section using a combination of \emph{named
+entity detection}, using the implementation provided by \emph{spacy},
+simple string comparison matching of the names of authors and
+institutions we extracted from the metadata respectively from Approach 1
+and tagging sections containing ``emails'' using regex , to detect where
+in the header the email is. Then, taking the tagged section, we detect
+which subsections correspond to which author-affiliation listing type,
+and extract the author email - institution mapping accordingly.
 
 Approach 2 allows to match many more institutions to authors than
-Approach 1 as not every institution is present in the mapping and many
-participants use gmail and similar providers as their official
-correspondence email we are unable to acquire this information for many
-participants. But, Approach 2 may contain differences in spelling in the
-institution name, which need to be merged. Thus we combine both
-approaches, and use the corresponding institutions in Approach 1 to
-unify the institutions obtained in Approach 2. As institution
-affiliation does not allow us to automatically associate a country to
-the institution, we need to get this through additional means. A first
-step is to use the top level domains present in the emails to associate
-a country of origin to the participants \& their associated
-institutions. Alongside this, to plot the community we augment the
-dataset with geolocation information, having this information we can
-then easily associate a country to the institution.
+Approach 1 as not every institution is present in the mapping --no
+companies will be in the mapping-- and many participants use gmail and
+similar providers as their official correspondence email. However,
+Approach 2 may contain differences in spelling in the institution name,
+which need to be merged. Thus we combine both approaches, and use the
+corresponding institutions in Approach 1 to unify the institutions
+obtained in Approach 2. Furthermore, we later merge names by considering
+the location of the institutions.
+
+But first as with Approach 2 institution affiliation does not allow us
+to automatically associate a country to the institution, we need to get
+this through other means. A first step is to use the top level domains
+present in the emails to associate a country of origin to the
+participants and their associated institutions. Then, to plot the
+community we augment the dataset with geolocation information. As a
+further benefit, having this information we can then easily associate a
+country to the institution for the emails that do not have a top level
+domain indicating location and merge the names of institutions where
+necessary based on location.
 
 As there are a variety of way in which the name of an institution could
-be written --consider EPFL, EPF Lausanne-- it was found that crawling
-the english, french and german version of Wikipedia (not using the API,
-or the API wrapper, as this does not give access to the desired
-information) and using \emph{BeautifulSoup} the get the coordinates
-present in the article was a quick and accurate way to get the location
-as the website directs to the relevant article on the institution even
-when misspellings are present. But not all institutions, even well known
-ones such as Tokyo University, have their coordinates listed on their
-Wikipedia. To get the remaining locations we use the geopy, which is a
-client for geocoding web services. These results however are more error
-prone and will always return a result. Then, to get the country we can
-then again use geopy. The resulting data containing paper identifier,
-the authors email, it's associated domain, order in which the author was
-cited, the institution, country, Longitude and Latitude are saved to
-csv. We use the paper identifier and author order to associate this data
-with the metadata to link information about authors with the papers they
-authored.
+be written --consider EPFL, EPF Lausanne-- crawling the english, french
+and german version of Wikipedia (not using the API, or the API wrapper,
+as this does not give access to the desired information) was a quick and
+accurate way to get the location. The advantage of sending requests over
+using the API is due to the website redirecting to the relevant article
+on the institution even when misspellings are present. Requests were
+sent using \emph{urllib3} and \emph{beautifulsoup} was used to parse
+them get the coordinates present in the article. Regretfully not all
+institutions, even well known ones such as Tokyo University, have their
+coordinates listed on their Wikipedia. To get the remaining locations we
+use the geopy, which is a client for geocoding web services. These
+results however are more error prone and will always return a result. It
+is thus recommended to verify the correctness of the results. To get the
+country we can then again use geopy. The resulting data containing paper
+identifier, the authors email, its associated domain, order in which the
+author was cited, the institution, country, Longitude and Latitude are
+saved to a csv file. We use the paper identifier and author order to
+associate this data with the metadata to link information about authors
+with the papers they authored.
 
@@
 \item
-  We used \textbf{\emph{beautiful soup}} and \textbf{\emph{string}}
+  We use \textbf{\emph{beautiful soup}} and \textbf{\emph{string}}
   libraries to only keep the text that we needed without any special
@@
 \item
-  we applied \textbf{\emph{regular expression}} to remove numbers
-  because we thought that numbers were not that important.
+  we apply \textbf{\emph{regular expression}} to remove numbers because
+  we thought that numbers were not that important.
 \item
@@
 \item
-  We removed the words that were connecting parts of a sentence rather
+  We remove the words that were connecting parts of a sentence rather
   than showing subjects, objects or intent. For us these words were not
@@
 \item
-  In some methods we used \textbf{\emph{Lemmatization}} and
-  \textbf{\emph{stemming}} and in other methods we didn't because we
+  In some methods we use \textbf{\emph{Lemmatization}} and
+  \textbf{\emph{stemming}} and in other methods we don't because we
   wanted to do a mapping with \textbf{\emph{GloVe}} vocabulary which we
@@
 \textbf{\emph{Stemming}} were only used with \textbf{\emph{TF-IDF}}
-while doing the Keywords extraction, otherwise we prefered keeping the
-words as they are because we were doing a mapping with a pretrained
-stanford word embedding and we did not wand to loose interpretability.
+while doing the Keywords extraction, otherwise we prefer keeping the
+words as they are because we are doing a mapping with a pretrained
+stanford word embedding and we do not want to loose interpretability.
 
-    For the Keywords extraction we used three methods. The first one whe is
-a trivial one is to search in the pdf itself for keywords and extract
-them, this method is the most accurate but we found out that for 492
-papers we had no keywords included. So we deciced to use two methods for
-keywords extraction. The first one is \textbf{\emph{TF-IDF}} and the
-second one is \textbf{\emph{Rake}}.
+    For the Keywords extraction we use three methods :
+
+The first one whe is a trivial one is to search in the pdf itself for
+keywords and extract them, this method is the most accurate but we found
+out that for 492 papers we had no keywords included. So we deciced to
+use two methods for keywords extraction. The first one is
+\textbf{\emph{TF-IDF}} and the second one is \textbf{\emph{Rake}}.
 
@@
 
-    Once we have all the keywords from the three methods, we tried to select
-the most accurate keywords. So we created a method that selects the
+    Once we have all the keywords from the three methods, we try to select
+the most accurate keywords. So we create a method that selects the
 intersection of TF-IDF keywords and the Rake keywords with the keywords
@@
 
-    Once we have our final keywords, we created a method that goes into the
-metadata and put assign to every document a publication year.
+    Once we have our final keywords, we create a method that goes into the
+metadata and assign to every document a publication year.
 
@@
     \begin{figure}
-        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_25_0.png}\end{center}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_26_0.png}\end{center}
         \caption{}
@@
     We wanted then to know what are the trends of words for each specific
-year, so we selected distinct words for each year, it means that we
-selected for each year the words that were present for that year and
-never for the others. We get the graph below. As we can see from the
-graph, the most used word in the papers, more than 10\% of 2015 papers
-uses the word `peer', more than 6\% of the papers uses the words
-`building', `embodied' in 2016. In 2017 the most frequent keyword on is
-`reponsive' and in 2018 `tools' is present with more than 6\%.
+year, so we select distinct words for each year, it means that we select
+for each year the words that were present for that year and never for
+the others. We get the graph below. As we can see from the graph, the
+most used word in the papers, more than 10\% of 2015 papers uses the
+word `peer', more than 6\% of the papers uses the words `building',
+`embodied' in 2016. In 2017 the most frequent keyword on is `reponsive'
+and in 2018 `tools' is present with more than 6\%.
 
@@
 
-    \hypertarget{co-authorship-graphs}{%
-\subsection{Co-authorship graphs}\label{co-authorship-graphs}}
+To cluster the documents we decided to use two different approaches. The
+first one is Natural Langage Processing (NLP) and the second one is a
+network analysis. The most accurate one is the network clustering using
+the references graph.
 
-\hypertarget{interactive-map-visualizations}{%
-\subsection{Interactive Map
-visualizations}\label{interactive-map-visualizations}}
+\hypertarget{approach-1-natural-langage-processing-nlp}{%
+\subsubsection{Approach 1 : Natural Langage Processing
+(NLP)}\label{approach-1-natural-langage-processing-nlp}}
+
+\hypertarget{baseline-tf-idf-combined-with-k-means}{%
+\paragraph{Baseline : TF-IDF combined with
+K-means}\label{baseline-tf-idf-combined-with-k-means}}
+
+With the natural langage processing, we start with a naive method which
+consists of clustering the documents using only TF-IDF. Each document
+has a vector representation with values for each word present in the
+document depending on the frequency of the word in this document
+regarding its frequency in all the other documents. So if a word is a
+keyword to the document and is not a common word than its value will be
+more important than the other words in the vector of the document. Once
+we have our vector representation, we select the max features parameter
+as 2500, it means that we will only consider the top max\_features
+ordered by term frequency across the corpus. On this word representation
+we will run K-means.
+
+\textbf{\emph{K-means}} clustering is a method used for clustering
+analysis, especially in data mining and statistics. It aims to partition
+a set of observations into a number of clusters (k), resulting in the
+partitioning of the data into Voronoi cells. It can be considered a
+method of finding out which group a certain object really belongs to.
+
+This method does not give good results as we can see it in the graph
+below all the vectors are together there is no clear separation between
+the documents. So we decide to use other methods using word embeddings
+and properties of TF-IDF.
+
+    \begin{figure}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_30_0.png}\end{center}
+        \caption{}
+        \label{}
+    \end{figure}
+
+    \hypertarget{second-method-average-of-glove-vectors-combined-with-k-means}{%
+\paragraph{Second method : Average of GloVe vectors combined with
+K-means}\label{second-method-average-of-glove-vectors-combined-with-k-means}}
+
+The second method was to use pre-trained words embeddings. We decided to
+use \textbf{\emph{GloVe}} library pre-trained on Wikipedia dataset.
+
+\textbf{\emph{GloVe}}, coined from Global Vectors, is a model for
+distributed word representation. The model is an unsupervised learning
+algorithm for obtaining vector representations for words. Training is
+performed on aggregated global word-word co-occurrence statistics from a
+corpus (Wikipedia), and the resulting representations showcase
+interesting linear substructures of the word vector space. It is
+developed as an open-source project at Stanford.{[}1{]}
+
+We construct a dictionnary from the words embeddings mapping each word
+of a document to its vector representation, than we average all the
+vectors of each document. Since each words has its representation in
+space, the average of all the words for each document will lead to a
+vector representing a document.
+
+Once we get a document vector representation, we apply to it K-means.
+The results are better, but we have only two clusters. If we increase
+the number of clusters than there is no clear separation anymore
+separation.
+
+    \begin{figure}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_32_0.png}\end{center}
+        \caption{}
+        \label{}
+    \end{figure}
+
+    \hypertarget{third-method-weighted-average-of-tf-idf-glove-combined-with-k-means}{%
+\paragraph{Third method : Weighted average of TF-IDF + GloVe combined
+with
+K-means}\label{third-method-weighted-average-of-tf-idf-glove-combined-with-k-means}}
+
+With this method, we did not use the parameter max features of the
+TF-IDF vector, we took all the vocabulary generated by all the documents
+and we created a method that sorts the document frequency vector, take
+the 500 first words and do a weighted average of the words embedding
+vectors with the TF-IDF score.
+
+Once we get the weighted average vector, and since we are using a words
+embedding of 50 dimentions. We decide to use feature reduction technique
+to reduce the number of dimensions and represent our vectors in an other
+vector space where all the features are orthogonal to each others.
+
+To apply the feature reduction to our vectors we used
+\textbf{\emph{Principal Component Analysis (PCA)}} algorithm.
+
+\textbf{PCA} is a statistical procedure that uses an orthogonal
+transformation to convert a set of observations of possibly correlated
+variables (entities each of which takes on various numerical values)
+into a set of values of linearly uncorrelated variables called principal
+components. If there are \textbf{\emph{n}} observations with ****p****
+variables, then the number of distinct principal components is
+\textbf{\emph{min(n-1,p)}}. This transformation is defined in such a way
+that the first principal component has the largest possible variance
+(that is, accounts for as much of the variability in the data as
+possible), and each succeeding component in turn has the highest
+variance possible under the constraint that it is orthogonal to the
+preceding components. The resulting vectors (each being a linear
+combination of the variables and containing n observations) are an
+uncorrelated orthogonal basis set. PCA is sensitive to the relative
+scaling of the original variables.
+
+Once we get our new vector representation, we apply K-means and we get
+the best separation, with a clear separation of 4 clusters as we can see
+it in the figure below.
+
+    \begin{figure}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_34_0.png}\end{center}
+        \caption{}
+        \label{}
+    \end{figure}
+
+    \hypertarget{approach-2-references-network-analysis}{%
+\subsubsection{Approach 2 : References Network
+Analysis}\label{approach-2-references-network-analysis}}
+
+For the references graph we choose to construct 4 different graphs to be
+able to extract the more information we can. Our first purpose is to be
+able to cluster the documents that are about the same subject.
+
+    \hypertarget{first-reference-graph-intersection-between-referenced-documents}{%
+\paragraph{First reference graph : Intersection between referenced
+documents}\label{first-reference-graph-intersection-between-referenced-documents}}
+
+Our first graph is constructed using the references of each document. It
+is constructed as follow, for each two documents, if there is an
+intersection between the references of both documents then there is a
+link. The weights of the edges are the length of the intersection set.
+The intuition behind is that the more the weight is high, the more the
+documents are likely to be about the same subjects since they are citing
+the same documents. From this graph, we create a subgraph of it, we
+filter the edges keeping only those who have a weight strictly higher
+than 3. It means that, each node of the subgraph, is related to at least
+one other node with 4 same documents referenced.
+
+\begin{Verbatim}[commandchars=\\\{\}]
+{\color{outcolor}Out[{\color{outcolor}9}]:} <IPython.core.display.HTML object>
+\end{Verbatim}
+
+    The resulted graph, is an undirected graph with 805 nodes and 6699
+edges. On this graph we extract two main information : * Strongly
+connected components to be able to detect clusters and related
+documents. * In\_degree in order to check if there are documents that
+are related to a lot of documents and those documents would be more
+general than others, and won't necessarly belong to one specific
+cluster.
+
+    \hypertarget{second-graph-relations-between-references}{%
+\paragraph{Second graph: Relations between
+references}\label{second-graph-relations-between-references}}
+
+The second graph is more about the referenced documents and not about
+the documents themselves. The aim of this graph is to see if there are
+documents that are more likely to cited together. If it is the case,
+then these documents are likely to be about the same subject. It is a
+weighted graph constructed as follow: for each document, we create a
+link between the references of the document. We create a dictionnary of
+links, if the link is already in the dictionnary then we increase the
+weight of the link. So for instance, if two references are present
+together in the 5 distinct documents, then the weight of the edge would
+be of 5. We obtain a graph of 10845 nodes and 148594 edges.
+
+    \begin{Verbatim}[commandchars=\\\{\}]
+Uploading 7403 kB. This may take a while{\ldots}
+
+    \end{Verbatim}
+
+\begin{Verbatim}[commandchars=\\\{\}]
+{\color{outcolor}Out[{\color{outcolor}11}]:} <IPython.core.display.HTML object>
+\end{Verbatim}
+
+    We can directly select from the interactive graph the nodes with degree
+higher than 100, these nodes represent the more cited documents, but we
+will construct a subgraph to specificly tackle these important
+referenced documents. On this graph, to be able to detect similar
+documents we also run Strongly connected components algorithm. On top of
+it, we inspected the documents with higher weights, we will explain more
+about what we extracted from this graph in the result section.
+
+    \hypertarget{third-graph-title-to-find}{%
+\paragraph{Third graph: ??? Title to
+find}\label{third-graph-title-to-find}}
+
+With this graph we aim to find what are the most cited documents, what
+are the documents that are the most influencial and how citations evolve
+over time.
+
+This is a directed graph constructed in this way. For each document, if
+the document cites another document than there is a link between the
+document and the cited one. We get a graph of 11650 nodes and 13243
+egdes. We also construct a subgraph of this graph, which is a
+co-citations in conferences, but because a lack of data, we find only
+three documents that cites other documents.
+
+On this graph, we run \textbf{\emph{PageRank}} algorithm to be able to
+extract the most influential documents.
+
+\textbf{PageRank (PR)}* is an algorithm used by Google Search to rank
+web pages in their search engine results. In our case, It measure
+PageRank is a way of measuring the importance of referenced papers.
+Compared to the in-degree analysis we get almost the same results since
+we have no out degree for almost every node.
+
+\begin{Verbatim}[commandchars=\\\{\}]
+{\color{outcolor}Out[{\color{outcolor}13}]:} <IPython.core.display.HTML object>
+\end{Verbatim}
+
+    \hypertarget{co-authorship}{%
+\subsection{Co-authorship}\label{co-authorship}}
+
+To get insight into collaborations within the community we build graphs
+based on co-authorship of papers. To build the graph structure and
+visualize it the python package \emph{networkx} was used. First, we
+built a co-authorship graph based on individual authors. Each node
+represents an author, and two nodes are connected if the authors
+collaborated on a paper. Other works \cite{cheong2009social},
+\cite{hesford2006management} have used a directed graph that only adds a
+link from the first author of the paper to all other authors. However,
+as we are more interested in collaboration patterns and less in finding
+the most influential first author, we build an undirected graph with
+edges between all co-authors. On the downside, yields a very dense graph
+that can not directly be interpreted. Hence, we prune the initial graph
+by removing nodes that do not satisfy additional conditions. Intuitively
+it is clear that a singular collaboration on a paper does not
+necessarily indicate that two people even know each other. A first
+condition was to only link two nodes together if the authors
+corresponding to each node have appear as co-authors in more than one
+conference. The graph produced by this approach is much more sparse and
+contains much fewer authors. Additionally all connected components
+contain fewer than 50 authors, making it possible to consider each
+author individually. Such a component is shown in figure \ref{fig_plot}.
+A second alternative approach was to consider the strength of bounds. In
+the graph authors are only linked if they have written at least 2 papers
+together. This method yields a much larger component --containing 441
+authors-- as this second condition is weaker. To get an understanding of
+author to author relations in this component we need to further prune
+away parts of the graph that are not insightful. When we look at
+individual author within the community, we are interested well
+collaborative individuals. Hence we remove nodes that have collaborated
+with fewer than 3 connections to other authors. The resulting graph can
+be seen in figure \ref{author_collab_large}. Details creating such a
+plot can be found in the section dedicated to this below.
+
+Focusing in on the authors is not the only way to interpret the
+co-authorship graph. One should also consider the overall structure of
+the graph. As graph is not connected, and contains one large main
+component with 1141 authors and 208 very small components with less than
+25 authors in them we focus on analyzing the structure of the main
+component of the graph. First we aim to detect sub-communities within
+the graph. Modularity is one measure used to find such communities. It
+measures the connection strength within a community relative to the
+strength of outgoing connections. Networks with high modularity have
+dense connections between the nodes within modules but sparse
+connections between nodes in different modules. A non-parametric
+algorithm for community detection is the Louvain Method
+\cite{blondel2008fast}. We used the implementation of Thomas Aynaud
+\cite{louvain}. This gives a good partitioning of the graph into 26
+communities of median size 42.84. This is quite a large number of
+communities, so we consider an alternative way to yield bigger
+partitions. An alternate way to find subcommunities is to look at
+normalized cuts, which partition the nodes into groups with many
+within-group connections and relatively few between-group connections.
+The advantage of this method is that we can choose how many cuts to
+make, and we are thus able to define the size of subcommunities. Finding
+normalized cuts in a graph can be done using \emph{sklearns} spectral
+clustering algorithm by passing it the adjacency matrix of the graph.
+With this method we are able to neatly separate the main component graph
+in three large communities. We note that the clusters found using method
+one are contained in the clusters found by method 2. See .
+
+To further analyze these subcommunities we look at the distribution of
+nationalities and institutions over the years. Additionally, to
+understand differences in the research being conducted, we analyze the
+frequency of keywords used for the papers that were writing within that.
+
+To get a better overview of how co-authorship happens across countries
+and institutions, we built graphs where every node represents a country
+respectively an institution. Two countries or institutions are linked if
+two authors from these two institutions collaborated on a paper
+together. The country graph is simple enough that it does not have to be
+pruned. The institution graph on the other hand is again not
+comprehensible without further processing. Thus, similar to the first
+approach on pruning presented, we only consider institutions who
+collaborated in at least two conferences. This the main component of
+this graph is shown in figure \ref{unigraph}.
+
+\textbf{Plotting of co-authorship graphs}: Graphs were visualised with
+the built in plot functions and graph layouts of networkx. The force
+directed layout was used as it clusters together nodes with strong
+connections. Then the size of each node was changed based on the
+position of the node in the graph. Central nodes with a lot of
+connections should be larger, while nodes with fewer connections should
+be smaller. To achieve this we used the measures of degree centrality
+for graphs with few nodes and edges and betweenness centrality for
+larger graphs . Degree centrality measures the fraction of degrees
+(number of connections) a node has with respect to the total number of
+connections in the graph. Betweenness centrality of a node is the sum of
+the fraction of all-pairs shortest paths that pass through it. Degree
+centrality is more adept for smaller graphs as their structure is still
+easy to interpret. As by construction betweenness takes into
+consideration the degrees of it neighboring nodes, it better structures
+the nodes large graphs into central and less central nodes.
+
+    \hypertarget{creating-interactive-visualizations}{%
+\subsection{Creating Interactive
+Visualizations}\label{creating-interactive-visualizations}}
+
+To better understand and interact with the data we create interactive
+graphs on top of the static graphs. Many libraries exist to allow for
+interaction. While working on the project, we worked with \emph{bookeh},
+\emph{holoviews}, \emph{mpld3} and \emph{plotly}. For some time
+implementing a custom visualization using \emph{D3} was also
+contemplated. However, functions provided by plotly is most general and
+allows to easily build interactive figures, while not being as heavy as
+booked and holoviews. Additionally, it is the most well maintained. D3
+requires a running server to be viewed and has a hard time dealing with
+large graphs. To plot figures we create them in networkx to grab the
+positioning of the nodes. Then we pass this positioning to plotly to
+plot.
 
@@
 
-\begin{verbatim}
-1. Collaboration
-2. Movement of participants
-3. Citation
-\end{verbatim}
-
-    \begin{figure}
-        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_32_0.png}\end{center}
-        \caption{}
-        \label{}
-    \end{figure}
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\tightlist
+\item
+  Collaboration
+\item
+  Movement of participants
+\item
+  Citation
+\end{enumerate}
 
@@
 
-    \begin{figure}
-        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_34_0.png}\end{center}
-        \caption{Collaborative papers between countries}
-        \label{figcollab}
-    \end{figure}
+    \hypertarget{movement-of-particpants}{%
+\subsubsection{Movement of particpants}\label{movement-of-particpants}}
+
+Using the data we have of participants over the years, and knowing their
+affiliation, we can now find members that change institutions over the
+years. Over the years of recording we find 14 participants that have
+changed moved countries and 47 that have moved institutions. We can see
+that most movement occured within the US respectively Europe,
+{[}fig\_move{]}.
 
@@
 
-\begin{verbatim}
-1. Keywords
-2. Outside influence: Conferences being sited
-\end{verbatim}
+\begin{enumerate}
+\def\labelenumi{\arabic{enumi}.}
+\tightlist
+\item
+  Keywords
+\item
+  Outside influence: Conferences being sited
+\end{enumerate}
 
-    \hypertarget{illustrative-example}{%
-\section{Illustrative Example}\label{illustrative-example}}
-
-For the purposes of illustration, consider a damped harmonic oscillator
-driven by a sinusoidal signal: \begin{equation}
-\frac{\mathrm{d}^2x}{\mathrm{d}t^2} + 2\zeta\omega_0\frac{\mathrm{d}x}{\mathrm{d}t} + \omega_0^2x = A\sin(\omega t), \label{eq:problem}
-\end{equation} \noindent where \(x(t)\) is the quantity of interest,
-\(\zeta\) is the damping constant, \(\omega_0\) is the undamped resonant
-frequency, and \(A\sin(\omega t)\) is the driving sinusoidal signal. The
-steady state solution to \eqref{eq:problem} is given by:
-\begin{eqnarray}
-x(t) &=& \frac{A}{Z_m\omega}\sin(\omega t + \phi), \label{eq:soln}\\
-Z_m &=& \sqrt{(2\omega_0\zeta)^2+\frac{(\omega^2-\omega_0^2)^2}{\omega^2}}, \nonumber\\
-\phi &=& \arctan\left(\frac{2\omega\omega_0\zeta}{\omega^2-\omega_0^2}\right). \nonumber
-\end{eqnarray}
-
-    \begin{figure}
-        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_41_0.png}\end{center}
-        \caption{Variation of steady-state oscillation amplitude with driving frequency for an oscillator with undamped frequency of 100 Hz, a driving amplitude $A = 10^6$, and various damping constants.}
-        \label{figtest}
-    \end{figure}
-
-    In Figure \ref{fig1} we plot the steady state amplitude of a 100 Hz
-oscillator as a function of driving frequency. We see that the
-oscillator exhibits a strong resonance for small values of \(\zeta\),
-and that the resonance frequency is slightly lower than the driving
-frequency of 100 Hz.
-
-\begin{algorithm}
-\caption{Calculate $y = x^n + z^m$}
-\begin{algorithmic} 
-\REQUIRE $n \geq 0 \vee x \neq 0 \vee z \geq 0 \vee m \neq 0$
-\ENSURE $y = x^n + z^m$
-\STATE $y \leftarrow 1$
-\IF{$n < 0$}
-  \STATE $N \leftarrow -n$
-\ELSE
-  \STATE $N \leftarrow n$
-\ENDIF
-\end{algorithmic}
-\end{algorithm}
     \hypertarget{conclusions}{%
@@
 mollit anim id est laborum.
+\newpage
 

### 2019-01-09 Report/paper.tex
push current status

@@
 
-    \begin{figure}
-        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_7_0.png}\end{center}
-        \caption{Distribution of papers published over the years}
-        \label{fig1}
-    \end{figure}
-
     \hypertarget{processing-the-metadata}{%
@@
 
-\textbf{To glue back substrings} we exploit the fact that that APA
+\textbf{To unify substrings} we exploit the fact that that APA
 references all have the same initial structure: \emph{Lastname F.M.
@@
     \begin{figure}
-        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_10_1.png}\end{center}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_11_0.png}\end{center}
         \caption{Different formats used to reference institution}
-        \label{figA}
+        \label{figB}
     \end{figure}
@@
 as different was to list authors are accepted, notably two ways as can
-be seen in \ref{figA} \ref{figB}. Hence, we first detect the structure
-of the header section before extracting the association. We tag the
-substring present in this section using a combination of \emph{named
-entity detection}, using the implementation provided by \emph{spacy},
-simple string comparison matching of the names of authors and
-institutions we extracted from the metadata respectively from Approach 1
-and tagging sections containing ``emails'' using regex , to detect where
-in the header the email is. Then, taking the tagged section, we detect
-which subsections correspond to which author-affiliation listing type,
-and extract the author email - institution mapping accordingly.
+be seen in Figure \ref{figA} and Figure \ref{figB}. Hence, we first
+detect the structure of the header section before extracting the
+association. We tag the substring present in this section using a
+combination of \emph{named entity detection}, using the implementation
+provided by \emph{spacy}, simple string comparison matching of the names
+of authors and institutions we extracted from the metadata respectively
+from Approach 1 and tagging sections containing ``emails'' using regex ,
+to detect where in the header the email is. Then, taking the tagged
+section, we detect which subsections correspond to which
+author-affiliation listing type, and extract the author email -
+institution mapping accordingly.
 
@@
 
-\begin{Verbatim}[commandchars=\\\{\}]
-{\color{outcolor}Out[{\color{outcolor}9}]:} <IPython.core.display.HTML object>
-\end{Verbatim}
-
     The resulted graph, is an undirected graph with 805 nodes and 6699
@@
 
-    \begin{Verbatim}[commandchars=\\\{\}]
-Uploading 7403 kB. This may take a while{\ldots}
-
-    \end{Verbatim}
-
-\begin{Verbatim}[commandchars=\\\{\}]
-{\color{outcolor}Out[{\color{outcolor}11}]:} <IPython.core.display.HTML object>
-\end{Verbatim}
-
     We can directly select from the interactive graph the nodes with degree
@@
 we have no out degree for almost every node.
-
-\begin{Verbatim}[commandchars=\\\{\}]
-{\color{outcolor}Out[{\color{outcolor}13}]:} <IPython.core.display.HTML object>
-\end{Verbatim}
 
@@
 
+    \begin{figure}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_48_0.png}\end{center}
+        \caption{One of the connected components of the co-authorship graph}
+        \label{fig_plot}
+    \end{figure}
+
+    \begin{figure}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_49_0.png}\end{center}
+        \caption{Largest Component}
+        \label{author_collab_large}
+    \end{figure}
+
     Focusing in on the authors is not the only way to interpret the
@@
 in three large communities. We note that the clusters found using method
-one are contained in the clusters found by method 2. See .
+one are contained in the clusters found by method 2. See Figure \ref{}
+and Figure \ref{}.
+
+    \begin{figure}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_51_0.png}\end{center}
+        \caption{}
+        \label{}
+    \end{figure}
+
+    \begin{figure}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_52_0.png}\end{center}
+        \caption{}
+        \label{}
+    \end{figure}
 
@@
 this graph is shown in figure \ref{unigraph}.
+
+    \begin{figure}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_54_0.png}\end{center}
+        \caption{Different formats used to reference institution}
+        \label{unigraph}
+    \end{figure}
 
@@
 
+    \begin{figure}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_58_0.png}\end{center}
+        \caption{Distribution of papers published over the years}
+        \label{fig1}
+    \end{figure}
+
     \hypertarget{community-composition-structure}{%
@@
 
+    \begin{figure}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_60_0.png}\end{center}
+        \caption{Different formats used to reference institution}
+        \label{figrep}
+    \end{figure}
+
     \hypertarget{collaboration}{%
 \subsubsection{Collaboration}\label{collaboration}}
+
+    \begin{figure}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_62_0.png}\end{center}
+        \caption{Collaborative papers between countries}
+        \label{figcollab}
+    \end{figure}
 

### 2019-01-10 Report/paper.tex
push paper
updates

@@
                                 % normalem makes italics be italics, not underlines
+    \usepackage{mathrsfs}
 
@@
     \def\br{\hspace*{\fill} \\* }
-    % Math Jax compatability definitions
+    % Math Jax compatibility definitions
     \def\gt{>}
     \def\lt{<}
+    \let\Oldtex\TeX
+    \let\Oldlatex\LaTeX
+    \renewcommand{\TeX}{\textrm{\Oldtex}}
+    \renewcommand{\LaTeX}{\textrm{\Oldlatex}}
     % Document parameters
+    % Document title
     \title{paper}
@@
 
-\expandafter\def\csname PY@tok@w\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.73,0.73}{##1}}}
-\expandafter\def\csname PY@tok@c\endcsname{\let\PY@it=\textit\def\PY@tc##1{\textcolor[rgb]{0.25,0.50,0.50}{##1}}}
-\expandafter\def\csname PY@tok@cp\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.74,0.48,0.00}{##1}}}
-\expandafter\def\csname PY@tok@k\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
-\expandafter\def\csname PY@tok@kp\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
-\expandafter\def\csname PY@tok@kt\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.69,0.00,0.25}{##1}}}
-\expandafter\def\csname PY@tok@o\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
-\expandafter\def\csname PY@tok@ow\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.67,0.13,1.00}{##1}}}
-\expandafter\def\csname PY@tok@nb\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
-\expandafter\def\csname PY@tok@nf\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.00,0.00,1.00}{##1}}}
-\expandafter\def\csname PY@tok@nc\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.00,1.00}{##1}}}
-\expandafter\def\csname PY@tok@nn\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.00,1.00}{##1}}}
-\expandafter\def\csname PY@tok@ne\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.82,0.25,0.23}{##1}}}
-\expandafter\def\csname PY@tok@nv\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.10,0.09,0.49}{##1}}}
-\expandafter\def\csname PY@tok@no\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.53,0.00,0.00}{##1}}}
-\expandafter\def\csname PY@tok@nl\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.63,0.63,0.00}{##1}}}
-\expandafter\def\csname PY@tok@ni\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.60,0.60,0.60}{##1}}}
-\expandafter\def\csname PY@tok@na\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.49,0.56,0.16}{##1}}}
-\expandafter\def\csname PY@tok@nt\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
-\expandafter\def\csname PY@tok@nd\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.67,0.13,1.00}{##1}}}
-\expandafter\def\csname PY@tok@s\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
-\expandafter\def\csname PY@tok@sd\endcsname{\let\PY@it=\textit\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
-\expandafter\def\csname PY@tok@si\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.73,0.40,0.53}{##1}}}
-\expandafter\def\csname PY@tok@se\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.73,0.40,0.13}{##1}}}
-\expandafter\def\csname PY@tok@sr\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.40,0.53}{##1}}}
-\expandafter\def\csname PY@tok@ss\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.10,0.09,0.49}{##1}}}
-\expandafter\def\csname PY@tok@sx\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
-\expandafter\def\csname PY@tok@m\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
-\expandafter\def\csname PY@tok@gh\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.00,0.50}{##1}}}
+\expandafter\def\csname PY@tok@gd\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.63,0.00,0.00}{##1}}}
 \expandafter\def\csname PY@tok@gu\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.50,0.00,0.50}{##1}}}
-\expandafter\def\csname PY@tok@gd\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.63,0.00,0.00}{##1}}}
-\expandafter\def\csname PY@tok@gi\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.00,0.63,0.00}{##1}}}
+\expandafter\def\csname PY@tok@gt\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.00,0.27,0.87}{##1}}}
+\expandafter\def\csname PY@tok@gs\endcsname{\let\PY@bf=\textbf}
 \expandafter\def\csname PY@tok@gr\endcsname{\def\PY@tc##1{\textcolor[rgb]{1.00,0.00,0.00}{##1}}}
-\expandafter\def\csname PY@tok@ge\endcsname{\let\PY@it=\textit}
-\expandafter\def\csname PY@tok@gs\endcsname{\let\PY@bf=\textbf}
-\expandafter\def\csname PY@tok@gp\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.00,0.50}{##1}}}
-\expandafter\def\csname PY@tok@go\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.53,0.53,0.53}{##1}}}
-\expandafter\def\csname PY@tok@gt\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.00,0.27,0.87}{##1}}}
-\expandafter\def\csname PY@tok@err\endcsname{\def\PY@bc##1{\setlength{\fboxsep}{0pt}\fcolorbox[rgb]{1.00,0.00,0.00}{1,1,1}{\strut ##1}}}
-\expandafter\def\csname PY@tok@kc\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
-\expandafter\def\csname PY@tok@kd\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
-\expandafter\def\csname PY@tok@kn\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
-\expandafter\def\csname PY@tok@kr\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
-\expandafter\def\csname PY@tok@bp\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
-\expandafter\def\csname PY@tok@fm\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.00,0.00,1.00}{##1}}}
-\expandafter\def\csname PY@tok@vc\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.10,0.09,0.49}{##1}}}
+\expandafter\def\csname PY@tok@cm\endcsname{\let\PY@it=\textit\def\PY@tc##1{\textcolor[rgb]{0.25,0.50,0.50}{##1}}}
 \expandafter\def\csname PY@tok@vg\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.10,0.09,0.49}{##1}}}
@@
 \expandafter\def\csname PY@tok@vm\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.10,0.09,0.49}{##1}}}
+\expandafter\def\csname PY@tok@mh\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
+\expandafter\def\csname PY@tok@cs\endcsname{\let\PY@it=\textit\def\PY@tc##1{\textcolor[rgb]{0.25,0.50,0.50}{##1}}}
+\expandafter\def\csname PY@tok@ge\endcsname{\let\PY@it=\textit}
+\expandafter\def\csname PY@tok@vc\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.10,0.09,0.49}{##1}}}
+\expandafter\def\csname PY@tok@il\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
+\expandafter\def\csname PY@tok@go\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.53,0.53,0.53}{##1}}}
+\expandafter\def\csname PY@tok@cp\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.74,0.48,0.00}{##1}}}
+\expandafter\def\csname PY@tok@gi\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.00,0.63,0.00}{##1}}}
+\expandafter\def\csname PY@tok@gh\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.00,0.50}{##1}}}
+\expandafter\def\csname PY@tok@ni\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.60,0.60,0.60}{##1}}}
+\expandafter\def\csname PY@tok@nl\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.63,0.63,0.00}{##1}}}
+\expandafter\def\csname PY@tok@nn\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.00,1.00}{##1}}}
+\expandafter\def\csname PY@tok@no\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.53,0.00,0.00}{##1}}}
+\expandafter\def\csname PY@tok@na\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.49,0.56,0.16}{##1}}}
+\expandafter\def\csname PY@tok@nb\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
+\expandafter\def\csname PY@tok@nc\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.00,1.00}{##1}}}
+\expandafter\def\csname PY@tok@nd\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.67,0.13,1.00}{##1}}}
+\expandafter\def\csname PY@tok@ne\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.82,0.25,0.23}{##1}}}
+\expandafter\def\csname PY@tok@nf\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.00,0.00,1.00}{##1}}}
+\expandafter\def\csname PY@tok@si\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.73,0.40,0.53}{##1}}}
+\expandafter\def\csname PY@tok@s2\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
+\expandafter\def\csname PY@tok@nt\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
+\expandafter\def\csname PY@tok@nv\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.10,0.09,0.49}{##1}}}
+\expandafter\def\csname PY@tok@s1\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
+\expandafter\def\csname PY@tok@dl\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
+\expandafter\def\csname PY@tok@ch\endcsname{\let\PY@it=\textit\def\PY@tc##1{\textcolor[rgb]{0.25,0.50,0.50}{##1}}}
+\expandafter\def\csname PY@tok@m\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
+\expandafter\def\csname PY@tok@gp\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.00,0.50}{##1}}}
+\expandafter\def\csname PY@tok@sh\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
+\expandafter\def\csname PY@tok@ow\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.67,0.13,1.00}{##1}}}
+\expandafter\def\csname PY@tok@sx\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
+\expandafter\def\csname PY@tok@bp\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
+\expandafter\def\csname PY@tok@c1\endcsname{\let\PY@it=\textit\def\PY@tc##1{\textcolor[rgb]{0.25,0.50,0.50}{##1}}}
+\expandafter\def\csname PY@tok@fm\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.00,0.00,1.00}{##1}}}
+\expandafter\def\csname PY@tok@o\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
+\expandafter\def\csname PY@tok@kc\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
+\expandafter\def\csname PY@tok@c\endcsname{\let\PY@it=\textit\def\PY@tc##1{\textcolor[rgb]{0.25,0.50,0.50}{##1}}}
+\expandafter\def\csname PY@tok@mf\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
+\expandafter\def\csname PY@tok@err\endcsname{\def\PY@bc##1{\setlength{\fboxsep}{0pt}\fcolorbox[rgb]{1.00,0.00,0.00}{1,1,1}{\strut ##1}}}
+\expandafter\def\csname PY@tok@mb\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
+\expandafter\def\csname PY@tok@ss\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.10,0.09,0.49}{##1}}}
+\expandafter\def\csname PY@tok@sr\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.40,0.53}{##1}}}
+\expandafter\def\csname PY@tok@mo\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
+\expandafter\def\csname PY@tok@kd\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
+\expandafter\def\csname PY@tok@mi\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
+\expandafter\def\csname PY@tok@kn\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
+\expandafter\def\csname PY@tok@cpf\endcsname{\let\PY@it=\textit\def\PY@tc##1{\textcolor[rgb]{0.25,0.50,0.50}{##1}}}
+\expandafter\def\csname PY@tok@kr\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
+\expandafter\def\csname PY@tok@s\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
+\expandafter\def\csname PY@tok@kp\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
+\expandafter\def\csname PY@tok@w\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.73,0.73}{##1}}}
+\expandafter\def\csname PY@tok@kt\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.69,0.00,0.25}{##1}}}
+\expandafter\def\csname PY@tok@sc\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
+\expandafter\def\csname PY@tok@sb\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
 \expandafter\def\csname PY@tok@sa\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
-\expandafter\def\csname PY@tok@sb\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
-\expandafter\def\csname PY@tok@sc\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
-\expandafter\def\csname PY@tok@dl\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
-\expandafter\def\csname PY@tok@s2\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
-\expandafter\def\csname PY@tok@sh\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
-\expandafter\def\csname PY@tok@s1\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
-\expandafter\def\csname PY@tok@mb\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
-\expandafter\def\csname PY@tok@mf\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
-\expandafter\def\csname PY@tok@mh\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
-\expandafter\def\csname PY@tok@mi\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
-\expandafter\def\csname PY@tok@il\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
-\expandafter\def\csname PY@tok@mo\endcsname{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
-\expandafter\def\csname PY@tok@ch\endcsname{\let\PY@it=\textit\def\PY@tc##1{\textcolor[rgb]{0.25,0.50,0.50}{##1}}}
-\expandafter\def\csname PY@tok@cm\endcsname{\let\PY@it=\textit\def\PY@tc##1{\textcolor[rgb]{0.25,0.50,0.50}{##1}}}
-\expandafter\def\csname PY@tok@cpf\endcsname{\let\PY@it=\textit\def\PY@tc##1{\textcolor[rgb]{0.25,0.50,0.50}{##1}}}
-\expandafter\def\csname PY@tok@c1\endcsname{\let\PY@it=\textit\def\PY@tc##1{\textcolor[rgb]{0.25,0.50,0.50}{##1}}}
-\expandafter\def\csname PY@tok@cs\endcsname{\let\PY@it=\textit\def\PY@tc##1{\textcolor[rgb]{0.25,0.50,0.50}{##1}}}
+\expandafter\def\csname PY@tok@k\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
+\expandafter\def\csname PY@tok@se\endcsname{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.73,0.40,0.13}{##1}}}
+\expandafter\def\csname PY@tok@sd\endcsname{\let\PY@it=\textit\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
 
@@
 participants and of the research being conducted within the community.
-After describing how to extract data from the original dataset we we
-derive insights into the community using social network analysis and
-{[}Nour: NLP etc{]}. We discover patterns of collaboration between
-participants, their migration and the global spread of the community.
-{[}Something about the insights in keywords/NLP/Co-Citation{]}
+After describing how to extract data from the original dataset we derive
+insights into the community using social network analysis, natural
+language processing and text mining. We discover patterns of
+collaboration between participants, their migration and the global
+spread of the community. We also extracted keywords and find clusters of
+referenced papers and documents within the conferences.
 \end{abstract}
-    \hypertarget{introduction}{%
-\section{Introduction}\label{introduction}}
+    \section{Introduction}\label{introduction}
 
@@
 \item
-  \ldots{} {[}Nour{]}
+  trends of keywords over the years
+\item
+  trends of citations and evolution of the number of documents from 1977
+  until 2018
+\item
+  clusters of the cited documents
+\item
+  clusters of the papers written within the conferences
 \end{itemize}
@@
 
-    \hypertarget{data-processing}{%
-\section{Data Processing}\label{data-processing}}
+    \section{Data Processing}\label{data-processing}
 
@@
 
-    \hypertarget{processing-the-metadata}{%
-\subsection{Processing the Metadata}\label{processing-the-metadata}}
+    \subsection{Processing the Metadata}\label{processing-the-metadata}
 
@@
 references in other papers to that paper. Then we add a shortened
-version of author names (i.e.~West, R.) by considering the author order.
+version of author names (i.e. West, R.) by considering the author order.
 Note that the short name extracted from the citation and the
@@
 extraction, we clean the data by unifying names, as slight spelling
-differences exist within the same author name (i.e.~Robert West, Robert
+differences exist within the same author name (i.e. Robert West, Robert
 A. West). When unifying the names we need to make sure to not overmerge
@@
 
-    \hypertarget{handling-of-pdf-data}{%
-\subsection{Handling of pdf data}\label{handling-of-pdf-data}}
+    \subsection{Handling of pdf data}\label{handling-of-pdf-data}
 
@@
 unify the formating. This is done using the \emph{unicodedata} module
-and setting converting all characters to `Normal Form Composed' form .
+and setting converting all characters to 'Normal Form Composed' form .
 
@@
 
-\hypertarget{extracting-the-papers-cited-by-a-paper}{%
 \subsection{Extracting the papers cited by a
-paper}\label{extracting-the-papers-cited-by-a-paper}}
+paper}\label{extracting-the-papers-cited-by-a-paper}
 
@@
 
-    \hypertarget{extracting-institution-and-location}{%
     \subsection{Extracting Institution and
-Location}\label{extracting-institution-and-location}}
+Location}\label{extracting-institution-and-location}
 
@@
 
-\hypertarget{approach-1}{%
-\subsubsection{Approach 1}\label{approach-1}}
+\subsubsection{Approach 1}\label{approach-1}
 
@@
 
-\hypertarget{approach-2}{%
-\subsubsection{Approach 2}\label{approach-2}}
+\subsubsection{Approach 2}\label{approach-2}
 
@@
 
-    \hypertarget{keywords-extraction}{%
-\subsection{Keywords extraction}\label{keywords-extraction}}
-
-    \hypertarget{text-preprocessing}{%
-\subsubsection{Text preprocessing}\label{text-preprocessing}}
+    \subsection{Keywords extraction}\label{keywords-extraction}
+
+    \subsubsection{Text preprocessing}\label{text-preprocessing}
 
@@
   to adjust for the fact that some words appear more frequently in
-  general.
+  general \cite{Tf-idf}
 \end{itemize}
@@
 most used word in the papers, more than 10\% of 2015 papers uses the
-word `peer', more than 6\% of the papers uses the words `building',
-`embodied' in 2016. In 2017 the most frequent keyword on is `reponsive'
-and in 2018 `tools' is present with more than 6\%.
-
-    \hypertarget{methodology-find-better-section-head..}{%
+word 'peer', more than 6\% of the papers uses the words 'building',
+'embodied' in 2016. In 2017 the most frequent keyword on is 'reponsive'
+and in 2018 'tools' is present with more than 6\%.
+
+    \begin{figure}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_28_0.png}\end{center}
+        \caption{}
+        \label{}
+    \end{figure}
+
     \section{Methodology {[}find better section
-head..{]}}\label{methodology-find-better-section-head..}}
-
-    \hypertarget{document-clustering}{%
-\subsection{Document Clustering}\label{document-clustering}}
+head..{]}}\label{methodology-find-better-section-head..}
+
+    \subsection{Document Clustering}\label{document-clustering}
 
@@
 
-\hypertarget{approach-1-natural-langage-processing-nlp}{%
 \subsubsection{Approach 1 : Natural Langage Processing
-(NLP)}\label{approach-1-natural-langage-processing-nlp}}
-
-\hypertarget{baseline-tf-idf-combined-with-k-means}{%
+(NLP)}\label{approach-1-natural-langage-processing-nlp}
+
 \paragraph{Baseline : TF-IDF combined with
-K-means}\label{baseline-tf-idf-combined-with-k-means}}
+K-means}\label{baseline-tf-idf-combined-with-k-means}
 
@@
     \begin{figure}
-        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_30_0.png}\end{center}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_31_0.png}\end{center}
         \caption{}
@@
 
-    \hypertarget{second-method-average-of-glove-vectors-combined-with-k-means}{%
     \paragraph{Second method : Average of GloVe vectors combined with
-K-means}\label{second-method-average-of-glove-vectors-combined-with-k-means}}
+K-means}\label{second-method-average-of-glove-vectors-combined-with-k-means}
 
@@
 interesting linear substructures of the word vector space. It is
-developed as an open-source project at Stanford.{[}1{]}
+developed as an open-source project at Stanford.\cite{GloVe}
 
@@
     \begin{figure}
-        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_32_0.png}\end{center}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_33_0.png}\end{center}
         \caption{}
@@
 
-    \hypertarget{third-method-weighted-average-of-tf-idf-glove-combined-with-k-means}{%
     \paragraph{Third method : Weighted average of TF-IDF + GloVe combined
 with
-K-means}\label{third-method-weighted-average-of-tf-idf-glove-combined-with-k-means}}
+K-means}\label{third-method-weighted-average-of-tf-idf-glove-combined-with-k-means}
 
@@
 uncorrelated orthogonal basis set. PCA is sensitive to the relative
-scaling of the original variables.
+scaling of the original variables \cite{PCA}.
 
@@
     \begin{figure}
-        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_34_0.png}\end{center}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_35_0.png}\end{center}
         \caption{}
@@
 
-    \hypertarget{approach-2-references-network-analysis}{%
     \subsubsection{Approach 2 : References Network
-Analysis}\label{approach-2-references-network-analysis}}
+Analysis}\label{approach-2-references-network-analysis}
 
@@
 
-    \hypertarget{first-reference-graph-intersection-between-referenced-documents}{%
     \paragraph{First reference graph : Intersection between referenced
-documents}\label{first-reference-graph-intersection-between-referenced-documents}}
+documents}\label{first-reference-graph-intersection-between-referenced-documents}
 
@@
 The intuition behind is that the more the weight is high, the more the
-documents are likely to be about the same subjects since they are citing
+documents are likely to be about the same subject since they are citing
 the same documents. From this graph, we create a subgraph of it, we
@@
 one other node with 4 same documents referenced.
+
+\begin{Verbatim}[commandchars=\\\{\}]
+{\color{outcolor}Out[{\color{outcolor}212}]:} <IPython.core.display.HTML object>
+\end{Verbatim}
 
@@
 
-    \hypertarget{second-graph-relations-between-references}{%
     \paragraph{Second graph: Relations between
-references}\label{second-graph-relations-between-references}}
+references}\label{second-graph-relations-between-references}
 
@@
 
+\begin{Verbatim}[commandchars=\\\{\}]
+{\color{outcolor}Out[{\color{outcolor}103}]:} <IPython.core.display.HTML object>
+\end{Verbatim}
+
+    \begin{figure}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_44_0.png}\end{center}
+        \caption{}
+        \label{}
+    \end{figure}
+
     We can directly select from the interactive graph the nodes with degree
@@
 
-    \hypertarget{third-graph-title-to-find}{%
-\paragraph{Third graph: ??? Title to
-find}\label{third-graph-title-to-find}}
+    \paragraph{Third graph: exploratory references
+graph}\label{third-graph-exploratory-references-graph}
 
@@
 
-    \hypertarget{co-authorship}{%
-\subsection{Co-authorship}\label{co-authorship}}
+\begin{Verbatim}[commandchars=\\\{\}]
+{\color{outcolor}Out[{\color{outcolor}105}]:} <IPython.core.display.HTML object>
+\end{Verbatim}
+
+    \subsection{Co-authorship}\label{co-authorship}
 
@@
     \begin{figure}
-        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_48_0.png}\end{center}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_50_0.png}\end{center}
         \caption{One of the connected components of the co-authorship graph}
@@
     \begin{figure}
-        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_49_0.png}\end{center}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_51_0.png}\end{center}
         \caption{Largest Component}
@@
 in three large communities. We note that the clusters found using method
-one are contained in the clusters found by method 2. See Figure \ref{}
-and Figure \ref{}.
-
-    \begin{figure}
-        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_51_0.png}\end{center}
-        \caption{}
-        \label{}
-    \end{figure}
-
-    \begin{figure}
-        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_52_0.png}\end{center}
-        \caption{}
-        \label{}
+one are contained in the clusters found by method 2. See Figure
+\ref{Louvain} and Figure \ref{normalized}.
+
+    \begin{figure}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_53_0.png}\end{center}
+        \caption{Subcommunities by Louvain}
+        \label{Louvain}
+    \end{figure}
+
+    \begin{figure}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_54_0.png}\end{center}
+        \caption{Subcommunities via normalized cuts}
+        \label{normalized}
     \end{figure}
@@
     \begin{figure}
-        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_54_0.png}\end{center}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_56_0.png}\end{center}
         \caption{Different formats used to reference institution}
@@
 
-    \hypertarget{creating-interactive-visualizations}{%
     \subsection{Creating Interactive
-Visualizations}\label{creating-interactive-visualizations}}
+Visualizations}\label{creating-interactive-visualizations}
 
@@
 
-    \hypertarget{results}{%
-\section{Results}\label{results}}
-
-    \begin{figure}
-        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_58_0.png}\end{center}
+    \section{Results}\label{results}
+
+    \begin{figure}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_60_0.png}\end{center}
         \caption{Distribution of papers published over the years}
@@
 
-    \hypertarget{community-composition-structure}{%
     \subsection{Community Composition \&
-Structure}\label{community-composition-structure}}
+Structure}\label{community-composition-structure}
 
@@
     \begin{figure}
-        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_60_0.png}\end{center}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_62_0.png}\end{center}
         \caption{Different formats used to reference institution}
@@
 
-    \hypertarget{collaboration}{%
-\subsubsection{Collaboration}\label{collaboration}}
-
-    \begin{figure}
-        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_62_0.png}\end{center}
+    \subsubsection{Collaboration}\label{collaboration}
+
+    \begin{figure}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_64_0.png}\end{center}
         \caption{Collaborative papers between countries}
@@
 
-    \hypertarget{movement-of-particpants}{%
-\subsubsection{Movement of particpants}\label{movement-of-particpants}}
+    \subsubsection{Movement of particpants}\label{movement-of-particpants}
 
@@
 
-    \hypertarget{research-topics-in-the-community}{%
     \subsection{Research topics in the
-Community}\label{research-topics-in-the-community}}
+Community}\label{research-topics-in-the-community}
 
@@
 
-    \hypertarget{conclusions}{%
-\section{Conclusions}\label{conclusions}}
+    \subsection{Clustering and referecences graphs
+results}\label{clustering-and-referecences-graphs-results}
+
+The distribution of referenced publications years are plotted in the
+graph below. We can see from the graph that there is a kind of a trend,
+each two, three years there is a pick of documents referenced followed
+by a two or three years of stagnancy. We can also notice that
+throughouts the year each pick is higher than the older one, which can
+be explained by the fact that The International Society of the Learning
+Sciences community is investigating more and more tools to facilitate
+learning over the years.
+
+    \begin{figure}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_68_0.png}\end{center}
+        \caption{}
+        \label{}
+    \end{figure}
+
+    Since the number of documents is increasing over the years, we also
+wanted to investigate more if the relevance of all the documents
+published is increasing too. Using Pagerank algorithm and the In-degree
+of each nodes to get the most influancial documents referenced of the
+citation graph that we constructed (graph3) before. We filtered the
+first 100 documents and then contructed a histogram of the counts. We
+obtain the figure below:
+
+    \begin{figure}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_70_0.png}\end{center}
+        \caption{}
+        \label{}
+    \end{figure}
+
+    We can see that in the top 100 cited documents more than 12\% are from
+2006, 8\% are from 2013, 6\% from 2014... We can not say that we have
+the same trend as before, and the relevance of the documents is
+increasing in the same way than with the number of publications but what
+we can say is that more than 50\% of the most cited documents are from
+2006 until 2016, we is 10 years. The other half is between 1977 until
+2005 which represents more than 25 years. On top of that, 2016 is the
+most important year in term of publications and maybe some documents did
+not have enough time to be cited yet.
+
+    The top 10 of the most influencial and most important referenced papers
+are the following:
+
+    \begin{figure}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_73_0.png}\end{center}
+        \caption{}
+        \label{}
+    \end{figure}
+
+    We also noticed from the first graph that some documents were more
+likely to cited together. We can say that the more two documents are
+likely to cited together the more it is probable that both documents are
+about the same subject From the table below we can also notice that some
+papers cites like to cite the same authors together, which is logic in a
+sense, because if some authors always treat about the same subjects then
+they are experts in that field and a lot of their publications are
+relevant and can be cited together.
+
+    \begin{figure}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_75_0.png}\end{center}
+        \caption{}
+        \label{}
+    \end{figure}
+
+    Using this graph, we also want to extract if there are some clusters of
+papers cited together. As we explained before, we run strongly connected
+algorithm to check if some cited documents are more likely to cited
+together, and this will give us clusters of cited documents that are
+more likely to be about the same subjects. We can visualise one cluster,
+the most important one.
+
+\begin{Verbatim}[commandchars=\\\{\}]
+{\color{outcolor}Out[{\color{outcolor}176}]:}                                                                                                                                                                                                                                                                                                                           Documents
+          cluster 4 0                                                                                                                                                                                                                                  schommer, m.
+(1990).
+effects of beliefs about the nature of knowledge on comprehension
+                    1                                                                                                                                                                          stathopoulou, c., \& vosniadou, s.
+(2007).
+exploring the relationship between physics-related epistemological beliefs and physics understanding
+                    2                                                                                                                                                                 hofer, b.
+k., \& pintrich, p.
+r.
+(1997).
+the development of epistemological theories: beliefs about knowledge and knowing and their relation to learning
+                    3                                                                                                                                                             chinn, c.
+a., buckland, l.
+a., \& samarapungavan, a.
+l.
+a.
+(2011).
+expanding the dimensions of epistemic cognition: arguments from philosophy and psychology
+          cluster 3 0  yoon, s., klopfer, e., wang, j., sheldon, j., wendel, d., schoenfeld, i., scheintaub, h., \& reider, d.
+(2013).
+designing to improve biology understanding through complex systems in high school classrooms: no simple matter!
+in the proceedings of the computer supported collaborative learning, madison, wisconsin
+                    1                                                                                                                                                             ertmer, p.a., ottenbreit-leftwich, a.t., sendurur, e., \& sendurur, p.
+(2012).
+teacher beliefs and technology integration practices: a critical relationship
+                    2                                                                                                                                                                                                                                                                                          epstein, j.
+(2008).
+'why model
+                    3                                                                                                                                                                                        national research council.
+(2012).
+education for life and work: developing transferable knowledge and skills in the 21st century
+                    4                                                                                                                                                                                                       thompson, j, windschitl, m., \& braaten, m.
+(2013).
+developing a theory of ambitious early-career teacher practice
+                    5                                                                                                                                                                                      desimone, l.
+(2009).
+improving impact studies of teachers’ professional development: toward better conceptualizations and measures
+                    6                                                                     yoon, s., koehler-yom, j., anderson, e., lin, j., \& klopfer, e.
+(accepted).
+using an adaptive expertise lens to understand the quality of teachers’ classroom implementation of computer-supported complex systems curricula in high school science
+                    7                                                                                                                         mueller, j., wood, e., willoughby, t., ross, c., \& specht, j.
+(2008).
+identifying discriminating variables between teachers who fully integrate computers and teachers with limited integration
+          cluster 2 0                                                                                                                                                                                                dougiamas, m., \& taylor, p.
+(2003).
+moodle: using learning communities to create an open source course management system
+                    1                                                                                                                                                                                                           coopey, e., schneider, l., \& danahy, e.
+(2013).
+interlace: interactive learning and collaboration environment
+                    2                                                                                                                                                                           scardamalia, m., \& bereiter, c.
+(2003).
+knowledge building environments: extending the limits of the possible in education and knowledge work
+                    3                                                                                                                                                                                                                            scardamalia, m., \& bereiter, c.
+(1996).
+student communities for the advancement of knowledge
+          cluster 1 0                                                                                                                                                                                                                          brown, j.
+s., collins, a., \& duguid, p.
+(1989).
+situated cognition and the culture of learning
+                    1                                                                                                                                                                                                                                                                             engeström, y.
+(1987).
+learning by expanding
+                    2                                                                                                                                                                                                                lave, j., \& wenger, e.
+(1991).
+situated learning: legitimate peripheral participation: cambridge univ pr
+                    3                                                                                                                                                                                                                                                                              vygotsky, l.
+s.
+(1978).
+mind in society (m
+                    4                                                                                                                                                                                                                            cole, m.
+(1996).
+cultural psychology: a once and future discipline: harvard university press
+                    5                                                                                                                              shaffer, d.
+w., hatfield, d., svarovsky, g.
+n., nash, p., nulty, a., bagley, e., .
+.
+.
+mislevy, r.
+(2009).
+epistemic network analysis: a prototype for 21st-century assessment of learning
+\end{Verbatim}
+
+\begin{Verbatim}[commandchars=\\\{\}]
+{\color{outcolor}Out[{\color{outcolor}185}]:} <IPython.core.display.HTML object>
+\end{Verbatim}
+
+    \begin{figure}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_80_0.png}\end{center}
+        \caption{}
+        \label{}
+    \end{figure}
+
+    The largest strongly connected component is the composed of 8 nodes and
+56 edges. This documents are all cited together more than 4 times. You
+can investingate the edges and the weights in the interactive graph
+constructed above. We wanted all the documents to be linked to each
+others to be more precise, but if we only look to giant connected
+component, we will get a network of 27 referenced paper with 142 egdes.
+
+\begin{Verbatim}[commandchars=\\\{\}]
+{\color{outcolor}Out[{\color{outcolor}166}]:} <IPython.core.display.HTML object>
+\end{Verbatim}
+
+    In the table below are the documents of the giant connected component
+represented in the interactive graph above.
+
+\begin{Verbatim}[commandchars=\\\{\}]
+{\color{outcolor}Out[{\color{outcolor}184}]:}                                                                                                                                                                                                                         Documents
+          0                                                                                        white, t., \& pea, r.
+(2011).
+distributed by design: on the promises and pitfalls of collaborative learning with multiple representations
+          1                                                                                 schneider b., wallace j., pea, r.
+\& blikstein p.
+(2013).
+preparing for future learning with a tangible user interface: the case of neuroscience
+          2                                                                                                                                                         dillenbourg, p., \& evans, m.
+(2011).
+interactive tabletops in education
+          3                                                                       speelpenning, t., antle, a.
+n., doering, t., \& van den hoven, e.
+(2011).
+exploring how tangible tools enable collaboration in a multi-touch tabletop game
+          4                                                                                                                                     price, s., rogers, y., stanton, d., \& smith, h.
+(2003).
+a new conceptual framework for cscl
+          5                                                                    fan, m., antle, a.
+n., neustaedter, c.
+\& wise, a.
+f.
+(2014).
+exploring how a co-dependent tangible tool design supports collaboration in a tabletop activity
+          6                                                                                                                                              jordan, b., \& henderson, a.
+(1995).
+interaction analysis: foundations and practice
+          7                                                                                                                                          rogoff, b.
+(1990).
+apprenticeship in thinking: cognitive development in social context
+          8   kirschner, p.
+a., sweller, j., \& clark, r.
+e.
+(2006).
+why minimal guidance during instruction does not work: an analysis of the failure of constructivist, discovery, problem-based, experiential, and inquiry-based teaching
+          9                                                 wise, a.
+f., saghafian, m.
+\& padmanabhan, p.
+(2012).
+towards more precise design guidance: specifying and testing the functions of assigned student roles in online discussions
+          10                                                                                                                                                  roschelle, j.
+(1992).
+learning by collaborating: convergent conceptual change
+          11                                                                                                                                                                      tomasello, m.
+(1995).
+joint attention as social cognition
+          12                                                                                            jermann, p., mullins, d., nüssli, m.-a., \& dillenbourg, p.
+(2011).
+collaborative gaze footprints: correlates of interaction quality
+          13                                                                 higgins, s.
+e., mercier, e., burd, e., \& hatch, a.
+(2011).
+multi-touch tables and the relationship with collaborative classroom pedagogies: a synthetic review
+          14                                                                                                    schneider, b., \& pea, r.
+(2013).
+real-time mutual gaze perception enhances collaborative learning and collaboration quality
+          15                                                                                             meier, a., spada, h., \& rummel, n.
+(2007).
+a rating scheme for assessing the quality of computer-supported collaboration processes
+          16                                                                                                                                                                                      barron, b.
+(2003).
+when smart groups fail
+          17                                                                                 antle, a.n., tanenbaum, j., macaranas, a.
+and robinson, j.
+(2014) games for change: looking at models of persuasion through the lens of design
+          18                                                                                                                                                ullmer, b.
+\& ishii, h.
+(2000).
+emerging frameworks for tangible user interfaces
+          19                                                                                             shaer, o., strait, m., valdes, c., feng, t., lintz, m., \& wang, h.
+(2011).
+enhancing genomic learning through tabletop interaction
+          20                                                                                                                                  fernaeus, y.
+\& tholander, j.
+(2006).
+finding design qualities in a tangible programming space
+          21                                                       richardson, d.
+c., \& dale, r.
+(2005).
+looking to understand: the coupling between speakers’ and listeners’ eye movements and its relationship to discourse comprehension
+          22                                                                                                                                           lave, j.
+\& wenger, e.
+(1991).
+situated learning: legitimate peripheral participation
+          23                                                                                schneider, b., jermann, p., zufferey, g., \& dillenbourg, p.
+(2011).
+benefits of a tangible interface for collaborative learning and interaction
+          24                       marshall, p., fleck, r., harris, a., rick, j., hornecker, e., rogers, y., \& dalton, n.
+s.
+(2009).
+fighting for control: children's embodied interactions when using physical and digital representations
+          25                                                                                 weinberger, a., \& fischer, f.
+(2006).
+a framework to analyze argumentative knowledge construction in computer-supported collaborative learning
+          26                                                                                                                                                             dillenbourg, p.
+(1999).
+what do you mean by collaborative learning
+\end{Verbatim}
+
+    Now we want to apply the same logic with the papers in-conferences. So
+we will focus on the analysis of the first graph that uses the
+intersection between the referenced documents of each two by two papers.
+The length of the intersection set had to be more than 4.
+
+So if more than 4 documents are referenced by two distinct documents
+than the latter are more likely to be about the same subect.
+
+\begin{Verbatim}[commandchars=\\\{\}]
+{\color{outcolor}Out[{\color{outcolor}231}]:}                                                                                                                                                                                                                                                                                                                                                                                                                                 Documents
+          cluster 9 0                                                                                                                                                                                                                                                                     Mazziotti, C., Rummel, N., \& Deiglmayr, A.
+(2016).
+Comparing Students’ Solutions When Learning Collaboratively or Individually Within Productive Failure
+                    1                                                                                                                                                                                                                                                                            Hartmann, C., Angersbach, J., \& Rummel, N.
+(2015).
+Social Interaction, Constructivism and their Application within (CS)CL Theories In  Lindwall, O
+                    2                                                                                                                                                                                                                                                             Mazziotti, C., Loibl, K., \& Rummel, N.
+(2015).
+Collaborative or Individual Learning within Productive Failure: Does the Social Form of Learning Make a Difference
+                    3                                                                                                                                                                                                                                                                             Hartmann, C., Rummel, N., \& Loibl, K.
+(2016).
+Communication Patterns and Their Role for Conceptual Knowledge Acquisition From Productive Failure
+          cluster 8 0                                                                                                                                                                                                                                                                                                                                                McBride, E., Vitale, J., \& Linn, M.
+(2018).
+Learning Design Through Science vs
+                    1                                                                                                                                                                                                                                                                             McBride, E., Vitale, J., Applebaum, L., \& Linn, M.
+(2017).
+Examining the Flow of Ideas During Critique Activities in a Design Project In Smith, B
+                    2                                                                                                                                                                                                                                      McBride, E.
+A., Vitale, J.
+M., Applebaum, L., \& C.Linn, M.
+(2016).
+Use of Interactive Computer Models to Promote Integration of Science Concepts Through the Engineering Design Process
+                    3                                                                                                                                                                                                                                                                                            McBride, E., Vitale, J., \& Linn, M.
+(2018).
+Middle School Student Ideas on the Relative Affordances of Physical and Virtual Models
+                    4                                                                                                                                                                                                                                                                                                                                          Mishra, S.
+\& Iyer, S.
+(2018).
+Promoting Cognitive Processes of Knowledge Integration
+          cluster 7 0                                                                                                                                                                        Greenhow, C., Hershkovitz, A., Baruch, A.
+F., Askari, E., Tsovaltzi, D., Asterhan, C., Puhl, T., Weinberger, A., Bouton, E., \& Polman, J.
+(2016).
+Teachers and Professional Development: New Contexts, Modes, and Concerns in the Age of Social Media
+                    1                                                                                                                                                                                                                                                              Erkens, M., Schlottbom, P., \& Bodemer, D.
+(2016).
+Qualitative and Quantitative Information in Cognitive Group Awareness Tools: Impact on Collaborative Learning
+                    2                                                                                                                                                                                                                                                                                                                      Schnaubert, L.
+\& Bodemer, D.
+(2016).
+How Socio-Cognitive Information Affects Individual Study Decisions
+                    3                                                                                                                                                                                                                                                                                             Asterhan, C.
+\& Bouton, E.
+(2017).
+Secondary school peer-to-peer knowledge sharing through social network technologies In Smith, B
+                    4                                                                                                                                                                                                                                                                                                                                                     Erkens, M.
+\& Bodemer, D.
+(2017).
+Which Visualization Guides Learners Best
+                    5                                                                                                                                                                                     Tsovaltzi, D., Dutta, N., Puhl, T., \& Weinberger, A.
+(2017).
+Group and Individual Level Effects of Supporting Socio-Cognitive Conflict Awareness and Its Resolution in Large SNS Discussion Groups: A Social Network Analysis In Smith, B
+                    6                                                                                                                                                                                                                                                                                                 Heimbuch, S.
+\& Bodemer, D.
+(2016).
+Effects of Implicit Guidance on Contribution Quality in a Wiki-Based Learning Environment
+                    7                                                                                                                                                                                                                                           Puhl, T., Tsovaltzi, D., \& Weinberger, A.
+(2015).
+A Long-Term View on Learning to Argue in Facebook: The Effects of Group Awareness Tools and Argumentation Scripts In  Lindwall, O
+          cluster 6 0                                                                                                                                                                                                                                                                                                           Dornfeld, C.
+L.
+\& Puntambekar, S.
+(2016).
+Negotiation Towards Intersubjectivity and Impacts on Conceptual Outcomes
+                    1                                                                                                                                                                                                                                                           Evenstone, A.
+L.
+\& Puntambekar, S.
+(2015).
+Internalization of Physics Concepts and Relationships Based on Teacher Modeling of Collaborative Prompts In  Lindwall, O
+                    2                                                                                                                                                                                                                                                           Dornfeld, C., Zhao, N., \& Puntambekar, S.
+(2017).
+A Mixed-Methods Approach for Studying Collaborative Learning Processes at Individual and Group Levels In Smith, B
+                    3                                                                                                                                                                                                                                                                       Martin, N.
+D., Gnesdilow, D., \& Puntambekar, S.
+(2015).
+Peer Scaffolding to Learn Science in Symmetrical Groups Collaborating Over Time In  Lindwall, O
+          cluster 5 0                                                                                                                                                                                                                                                                           Khanlari, A., Zhu, G., Costa, S., \& Scardamalia, M.
+(2018).
+Criss Crossing Science Domains in Knowledge Building Communities: An Exploratory Study
+                    1                                                                                                                                                                                                                                                                                                       Hong, H., Chai, C.
+S., \& Hung, G.
+(2015).
+Principle-Based Guidance to Foster Adaptive Teaching Practice In  Lindwall, O
+                    2                                                                                                                                                                                                                                                                                   Oshima, J.
+\& Tsunakawa, T.
+(2018).
+An Analysis of Collective Knowledge Advancement and  Emergent Nature of Ideas in Subject-Matter Learning
+                    3                                                                                                                                                                                                                                                                                                             Hod, Y., Sagy, O., \&  (2016).
+Learning the Learning Sciences: An Investigation of Newcomers’ Sociocultural Ideas
+                    4   Scardamalia, M., Bereiter, C., Laferrière, T., Bielaczyc, K., Chai, S., Chan, C.
+K., Chen, B., Chen, M., de Jong, F., del Castillo, F.
+D., Hakkarainen, K., Matsuzawa, Y., McAuley, A., Montané, M., Nunes, C., Reeve, R., Seitamaa-Hakkarainen, P., Oshima, J., Shirouzu, H., Tan, S.
+C., Teo, C.
+L., van Aalst, J., Vinha, T., \& Zhang, J.
+(2017).
+Toward a Multi-Level Knowledge Building Innovation Network In Smith, B
+                    5                                                                                        de Jong, F., van den Ende, J., van Heijst, H., Matsuzawa, Y., Kirschner, P., Zhang, J., Chen, M., Chen, F., Rosé, C., Godinez, E.
+V., Ratté, S., Chen, B., Chan, C., van Aalst, J., Yang, C., Oshima, J., Hmelo-Silver, C., \& Wise, A.
+(2017).
+Making a Difference: Analytics for Quality Knowledge-Building Conversations In Smith, B
+                    6                                                                                                                                                                                                                                                               Tao, D., Zhang, J., \& Gao, D.
+(2017).
+Reflective Structuration of Knowledge Building Practices in Grade 5 Science: A Two-Year Design-Based Research In Smith, B
+                    7                                                                                                                                                                                                                                                                                                                 Tao, D.
+\& Zhang, J.
+(2017).
+How Did a Grade 5 Science Community Co-Construct Collective Structures of Inquiry
+                    8                                                                                                                                                                                                                                                           Lee, V.
+Y., Tan, S.
+C., \& Chee, J.
+K.
+(2016).
+Idea Identification and Analysis (I2A): A Search for Sustainable Promising Ideas Within Knowledge-Building Discourse
+          {\ldots}                                                                                                                                                                                                                                                                                                                                                                                                                                   {\ldots}
+          cluster 4 3                                                                                                                                                                                                                                                                                                                                                     Olsen, J.
+K., Rummel, N., \& Aleven, V.
+(2017).
+Learning Alone or Together
+          cluster 3 0                                                                                                                                                                                                                                                                                                                    Keifert, D., Krist, C., Scipio, D.
+A., \& Phillips, A.
+M.
+(2018).
+Epistemic Agency as a Members’ Experience
+                    1                                                                                                                                                                                                                                                                                                          Munter, C., Haines, C., \& Bruton, R.
+(2018).
+Cultivating Formative Intervention Research Partnerships in Mathematics
+                    2                                                                                                                                                                                                                                                                                                       Roque, R., Lin, K., \& Liuzzi, R.
+(2016).
+“I’m Not Just a Mom”: Parents Developing Multiple Roles in Creative Computing
+                    3                                                                                                                                                                     Suárez, E., Tzou, C., Bang, M., *, M., Roque, R., Pinkard, N., McDermott, R., Barron, B., Goldman, S., Luce, M., Vea, T., Conlin, L., Bell, P., \& Martin, C.
+K.
+(2018).
+Designing for Axiological Innovation within Family-Centered Learning Environments
+                    4                                                                                                    Melendez, J.
+W., Radinsky, J., Vossoughi, S., Marin, A.
+M., Bang, M., Nolan, C.
+M., Phillips, N.
+C., Lund, V.
+K., Gonzales, W., Allen, S., Bild, D., Bruton, I., Carmichae, J., Martell, E., Schmidt, A., Jurow, A.
+S., \& Hall, R.
+(2018).
+Community-Based Design Partnerships: Examples from a New Generation of CHAT/DBR
+                    5                                                        Tissenbaum, M., Sheldon, J., Sherman, M.
+A., Abelson, H., Weintrop, D., Jona, K., Horn, M., Wilensky, U., Basu, S., Rutstein, D., Snow, E., Shear, L., Grover, S., Lee, I., Klopfer, E., Jayathirtha, G., Shaw, M., kafai, y., Mustafaraj, E., Temple, W., Shapiro, R.
+B., Lui, D., \& Sorensen, C.
+(2018).
+The State of the Field in Computational Thinking Assessment
+                    6                                                                                                                                                                                                                                                                                               Ko, M.
+\& Krist, C.
+(2018).
+Redistributing Epistemic Agency: How Teachers Open Up Space for Meaningful Participation in Science
+                    7                                                                                                                                              Bell, P., Severance, S., Penuel, W.
+R., Sumner, T., Mommandi, W., Quigley, D., Van Horne, K., Johnson, R., Stromholt, S., Lakhani, H., Davis, K., Bell, A., \& Bang, M.
+(2016).
+Researchers and Practitioners Co-Designing for Expansive Science Learning and Educational Equity
+                    8                                                                                                                                                                                                                                                                                     Meléndez, J.
+W.
+(2018).
+Identifying Expansive Learning in Democratic Activity: A CHAT/DBR Approach to Community-Based Design Partnerships
+                    9                                                                                                                                                                                                                                                                                                                            Roque, R.
+\& Jain, R.
+(2018).
+Becoming Facilitators of Creative Computing in Out-of-School Settings
+                    10                                                                                     Lee, V.
+R., Tzou, C., Bang, M., Bell, P., Stromholt, S., Price, N., Ng, M., Kafai, Y., Telhan, O., Davis, R., Steele, K., Adleberg, B., Kahn, J., Hall, R., Phillips, A., Hansen, J., Recker, M., \& Barron, B.
+(2017).
+Libraries as Emerging Spaces for Computer-Supported Collaborative Learning in Schools and Communities In Smith, B
+                    11                                                                                                                                                                                                                                                                                           Krist, C.
+\& Suárez, E.
+(2018).
+Doing Science with Fidelity to Persons: Instantiations of Caring Participation in Science Practices
+                    12                                                                                                                                                                                                                                                                                                                                                      Proctor, C.
+\& Blikstein, P.
+(2018).
+How Broad is Computational Thinking
+                    13                                                                                                                                                                                                                                                 Penuel, W., Van Horne, K., Severance, S., Quigley, D., \& Sumner, T.
+(2016).
+Students’ Responses to Curricular Activities as Indicator of Coherence in Project-Based Science
+                    14                                                                                                                                                                                                                                                                                   Chen, G.
+\& Shen, J.
+(2018).
+Student Learning of Computational Thinking in A Robotics Curriculum: Transferrable Skills and Relevant Factors
+                    15                                                                                                                                                                                                                                                          Swanson, H., Irgens, G.
+A., Bain, C., Hall, K., Woods, P., Rogge, C., Horn, M., \& Wilensky, U.
+(2018).
+Characterizing Computational Thinking in High School Science
+                    16                                                                                                                                                                                                                                                                                        Ramey, K.
+E., Stevens, R., \& Uttal, D.
+(2018).
+STEAM Learning in an In-school Makerspace: The Role of Distributed Spatial Sensemaking
+          cluster 2 0                                                                                                                                                                                                                                                                                                       Hickey, D.
+T.
+(2016).
+Competency-Based Digital Badges and Credentials: Cautions and Potential Solutions From the Field
+                    1                                                                                                                                                                                                                                                                                                                                                             Hickey, D.
+T.
+\& Chartrand, G.
+(2018).
+Recognizing Competencies vs
+                    2                                                                                                                                                                                                                          Slotta, J.
+D., Hickey, D., Rosé, C.
+P., Dillenbourg, P., Najafi, H., Håklev, S., Uttamchandani, S., \& Quick, J.
+(2016).
+The Learning Sciences @ Scale: Current Developments in Open Online Learning
+                    3                                                                                                                                                                                                                                                                            Hickey, D.
+T., Uttamchandani, S., \& Quick, J.
+D.
+(2016).
+Scaling Up Productive Disciplinary Engagement With Participatory Learning and Assessment
+          cluster 1 0                                                                                                                                                                                                                                                                            Furtak, E.
+M., Binder, T., \& Henson, K.
+(2018).
+Designing From Outer Space: Tensions in the Development of a Task to Assess a Crosscutting Concept
+                    1                                                                                                                                                                                                                                                  Basu, S., McElhaney, K.
+W., Grover, S., Harris, C.
+J., \& Biswas, G.
+(2018).
+A Principled Approach to Designing Assessments That Integrate Science and Computational Thinking
+                    2                                                                                                                                                                                                                                 Zivic, A., Smith, J.
+F., Reiser, B., Edwards, K., Novak, M., \& McGill, T.
+(2018).
+Negotiating Epistemic Agency and Target Learning Goals: Supporting Coherence from the Students’ Perspective
+                    3                                     Pellegrino, J.
+W., Gane, B.
+D., Zaidi, S.
+Z., Harris, C.
+J., McElhaney, K.
+W., Alozie, N., Pennock, P.
+H., Severance, S., Neumann, K., Fortus, D., Krajcik, J., Nordine, J., Furtak, E.
+M., Briggs, D., Chattergoon, R., Penuel, B., Wingert, K., \& Van Horne, K.
+(2018).
+The Challenge of Assessing “Knowledge in Use”: Examples from Three-Dimensional Science Learning and Instruction
+          cluster 0 0                                                                                                                                                                                                                                                                          Peppler, K.
+A., Thompson, N., Danish, J., \& Moczek, A.
+(2018).
+In the Hive: Designing for Emergence When Teaching Complex Systems In Early Childhood
+                    1                                                                                                                                                                                                                                                  Peppler, K.
+A., Thompson, N., Danish, J., Moczek, A., \& Corrigan, S.
+(2018).
+Comparing First- and Third-Person Perspectives in Early Elementary Learning of Honeybee Systems
+                    2                                                                                                                                                                                                                                         Peppler, K.
+A., Thompson, N., Danish, J., Moczek, A., \& Han, S.
+(2018).
+Indoor Positioning Technology \& Enhanced Engagement in Early Elementary Systems Thinking and Science Learning
+                    3                                                                                                                                                                                                                                                      Riedy, R., Van Horne, K., Bell, P., Penuel, B., Neill, T., \& Shaw, S.
+(2018).
+Mapping Networks to Help Education Leaders Gain Insights into Complex Educational Systems
+
+          [85 rows x 1 columns]
+\end{Verbatim}
+
+    When applying this kind of clustering we find that most of the clusters
+contains almost the same authors with different papers, which is logic
+because if they are specialists in one topic and write several papers on
+it, they might reuse some references in several documents.
+
+    \section{Conclusions}\label{conclusions}
 

### 2019-01-10 Report/paper.tex
df_replaced
add changes

--- 2019-01-09 Report/paper.tex
@@
 
-    \documentclass[journal,twocolumn]{IEEEtran}
+    \documentclass[journal,onecolumn]{IEEEtran}
 \usepackage[noadjust]{cite}
@@
     In this report we explore ways to automatically analyze ICLS and CSCL
-papers to gain an understanding of the community formed by conferences
+papers to gain an understanding of the community formed by conference
 participants and of the research being conducted within the community.
-After describing how to extract data from the original dataset we we
-derive insights into the community using social network analysis and
-{[}Nour: NLP etc{]}. We discover patterns of collaboration between
-participants, their migration and the global spread of the community.
-{[}Something about the insights in keywords/NLP/Co-Citation{]}
+After describing how to extract data from the original dataset we derive
+insights into the community using network analysis, natural language
+processing and text mining. We discover patterns of collaboration
+between participants, their migration and the global spread of the
+community. We extract keywords and find clusters of referenced papers
+and documents within the conferences.
 \end{abstract}
@@
 
+    \begin{figure}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_28_0.png}\end{center}
+        \caption{}
+        \label{}
+    \end{figure}
+
     \hypertarget{methodology-find-better-section-head..}{%
@@
 
-    \hypertarget{third-graph-title-to-find}{%
-\paragraph{Third graph: ??? Title to
-find}\label{third-graph-title-to-find}}
+    \hypertarget{third-graph-exploratory-references-graph}{%
+\paragraph{Third graph: exploratory references
+graph}\label{third-graph-exploratory-references-graph}}
 
@@
 
+\begin{Verbatim}[commandchars=\\\{\}]
+{\color{outcolor}Out[{\color{outcolor}105}]:} <IPython.core.display.HTML object>
+\end{Verbatim}
+
     \hypertarget{co-authorship}{%
@@
 based on co-authorship of papers. To build the graph structure and
-visualize it the python package \emph{networkx} was used. First, we
-built a co-authorship graph based on individual authors. Each node
-represents an author, and two nodes are connected if the authors
+visualize it the python package \emph{networkx} was used. When
+constructing the graph, we associate qualitative features --such as the
+name and institution of the author that is represented by a node-- to
+the nodes and edges of the graph.
+
+\hypertarget{graph-construction}{%
+\subsubsection{Graph Construction:}\label{graph-construction}}
+
+First, we built a co-authorship graph based on individual authors. Each
+node represents an author, and two nodes are connected if the authors
 collaborated on a paper. Other works \cite{cheong2009social},
@@
 the most influential first author, we build an undirected graph with
-edges between all co-authors. On the downside, yields a very dense graph
-that can not directly be interpreted. Hence, we prune the initial graph
-by removing nodes that do not satisfy additional conditions. Intuitively
-it is clear that a singular collaboration on a paper does not
-necessarily indicate that two people even know each other. A first
-condition was to only link two nodes together if the authors
-corresponding to each node have appear as co-authors in more than one
-conference. The graph produced by this approach is much more sparse and
-contains much fewer authors. Additionally all connected components
-contain fewer than 50 authors, making it possible to consider each
-author individually. Such a component is shown in figure \ref{fig_plot}.
+edges between all co-authors. On the downside, this yields a very dense
+graph. Hence, we prune the initial graph by removing nodes that do not
+satisfy additional conditions. Intuitively it is clear that a singular
+collaboration on a paper does not necessarily indicate that two people
+even know each other. A first condition was to only link two nodes
+together if the authors corresponding to each node have appear as
+co-authors in more than one conference. The graph produced by this
+approach is much more sparse and contains much fewer authors.
+Additionally all connected components contain fewer than 50 authors,
+making it possible to consider each author individually. Such a
+component is shown in figure \ref{fig_plot}.
+
+    \begin{figure}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_50_0.png}\end{center}
+        \caption{One of the connected components of the co-authorship graph}
+        \label{fig_plot}
+    \end{figure}
+
     A second alternative approach was to consider the strength of bounds. In
@@
     \begin{figure}
-        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_48_0.png}\end{center}
-        \caption{One of the connected components of the co-authorship graph}
-        \label{fig_plot}
-    \end{figure}
-
-    \begin{figure}
-        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_49_0.png}\end{center}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_52_0.png}\end{center}
         \caption{Largest Component}
@@
 in three large communities. We note that the clusters found using method
-one are contained in the clusters found by method 2. See Figure \ref{}
-and Figure \ref{}.
-
-    \begin{figure}
-        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_51_0.png}\end{center}
-        \caption{}
-        \label{}
-    \end{figure}
-
-    \begin{figure}
-        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_52_0.png}\end{center}
-        \caption{}
-        \label{}
+one are contained in the clusters found by method 2. See Figure
+\ref{Louvain} and Figure \ref{normalized}.
+
+    \begin{figure}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_54_0.png}\end{center}
+        \caption{Subcommunities by Louvain}
+        \label{Louvain}
+    \end{figure}
+
+    \begin{figure}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_55_0.png}\end{center}
+        \caption{Subcommunities via normalized cuts}
+        \label{normalized}
     \end{figure}
@@
     \begin{figure}
-        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_54_0.png}\end{center}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_57_0.png}\end{center}
         \caption{Different formats used to reference institution}
@@
 
-    \textbf{Plotting of co-authorship graphs}: Graphs were visualised with
-the built in plot functions and graph layouts of networkx. The force
-directed layout was used as it clusters together nodes with strong
-connections. Then the size of each node was changed based on the
-position of the node in the graph. Central nodes with a lot of
-connections should be larger, while nodes with fewer connections should
-be smaller. To achieve this we used the measures of degree centrality
-for graphs with few nodes and edges and betweenness centrality for
-larger graphs . Degree centrality measures the fraction of degrees
-(number of connections) a node has with respect to the total number of
-connections in the graph. Betweenness centrality of a node is the sum of
-the fraction of all-pairs shortest paths that pass through it. Degree
-centrality is more adept for smaller graphs as their structure is still
-easy to interpret. As by construction betweenness takes into
-consideration the degrees of it neighboring nodes, it better structures
-the nodes large graphs into central and less central nodes.
+    \hypertarget{numerical-analysis-of-graphs}{%
+\subsubsection{Numerical analysis of
+graphs:}\label{numerical-analysis-of-graphs}}
+
+To analyze the structure of the graphs themselves we calculated the
+following measures:
+
+\begin{itemize}
+\tightlist
+\item
+  Diameter: longest shortest path in the graph.
+\item
+  Average clustering coefficient: Measure of how much the nodes in a
+  graph tend to cluster together. Average over all clustering
+  coefficients. The clustering coefficient of a node is the fraction of
+  triangles prassing through the node over all possible triangles
+  through that node \cite{watts1998collective}.
+\item
+  Density: the number of edges in the graph divided by the maximum
+  number of possible edges for a graph with the same number of nodes
+\end{itemize}
+
+    \hypertarget{plotting-of-co-authorship-graphs}{%
+\subsubsection{Plotting of co-authorship
+graphs:}\label{plotting-of-co-authorship-graphs}}
+
+Graphs were visualised with the built in plot functions and graph
+layouts of networkx. The force directed layout was used as it clusters
+together nodes with strong connections. Then the size of each node was
+changed based on the position of the node in the graph. Central nodes
+with a lot of connections should be larger, while nodes with fewer
+connections should be smaller. To achieve this we used the measures of
+degree centrality for graphs with few nodes and edges and betweenness
+centrality for larger graphs . Degree centrality measures the fraction
+of degrees (number of connections) a node has with respect to the total
+number of connections in the graph. Betweenness centrality of a node is
+the sum of the fraction of all-pairs shortest paths that pass through
+it. Degree centrality is more adept for smaller graphs as their
+structure is still easy to interpret. As by construction betweenness
+takes into consideration the degrees of it neighboring nodes, it better
+structures the nodes large graphs into central and less central nodes.
 
@@
 
-    \begin{figure}
-        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_58_0.png}\end{center}
-        \caption{Distribution of papers published over the years}
-        \label{fig1}
-    \end{figure}
+In this section we present first insights gathered during the
+Bibliographic analysis.
 
@@
 
-We find that participants from 372 institutions participated over the
-last 4 years, with a median of 128 institutions per year. Numbers of
-institutions participating are increasing each year, with a noticeable
-peak in 2018, which participants from 261 institutions. This is a
-considerable up from the last conference ICLS in 2016 which had 135
+We found that participants from 372 institutions participated over the
+last 4 years, with a median of 128 institutions per year. The number of
+institutions participating increased each year, with a noticeable peak
+in 2018, with participants from 261 institutions. This is a considerable
+increase from the last conference ICLS in 2016 which had 135
 participating institutions. Most participants are from the US, with a
-average of 50\% of all participants being from the US. We can also
+average of 50\% of all participants being from the US. We could also
 observe a trend of increase in US participants with only 35\% of US
@@
 Overall, participants from 41 nations have participated over the 4
-years, which an average of 28 nations represented each conference. After
-the US, participants of Germany, Canada and Singapore make up the
-biggest proportion of participants \(\ref{figrep}\).
-
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-\tightlist
-\item
-  Collaboration
-\item
-  Movement of participants
-\item
-  Citation
-\end{enumerate}
-
-    \begin{figure}
-        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_60_0.png}\end{center}
+years, with an average of 28 nations represented at each conference.
+After the US, participants of Germany, Canada and Singapore make up the
+biggest proportion of participants \ref{fig_rep}.
+
+    \begin{figure}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_64_0.png}\end{center}
         \caption{Different formats used to reference institution}
@@
 
-    \begin{figure}
-        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_62_0.png}\end{center}
+*\textbf{International Collaboration:} The U.S. again stands out as a
+major player, with most collaborations happening between the U.S. and
+other countries. Out of 851 papers, 153 were international
+collaborations. Out of these 153, 108 involved at least one U.S.
+participant. Excluding U.S. participation we find figure \ref{}. We
+noted that Finland is very collaborative, and that there exists a strong
+bond between Sweden and Israel. Additionally we observed that Asian
+nations seem to collaborate almost exclusively with each other or
+Canada.
+
+    \begin{figure}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_66_0.png}\end{center}
         \caption{Collaborative papers between countries}
@@
 that most movement occured within the US respectively Europe,
-{[}fig\_move{]}.
-
-    \hypertarget{research-topics-in-the-community}{%
-\subsection{Research topics in the
-Community}\label{research-topics-in-the-community}}
-
-\begin{enumerate}
-\def\labelenumi{\arabic{enumi}.}
-\tightlist
-\item
-  Keywords
-\item
-  Outside influence: Conferences being sited
-\end{enumerate}
+\ref{fig_move}.
+
+    \begin{figure}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_68_0.png}\end{center}
+        \caption{Movement of participants across institutions}
+        \label{fig_move}
+    \end{figure}
+
+    \hypertarget{clustering-and-referecences-graphs-results}{%
+\subsection{Clustering and referecences graphs
+results}\label{clustering-and-referecences-graphs-results}}
+
+The distribution of referenced publications years are plotted in the
+graph below. We can see from the graph that there is a kind of a trend,
+each two, three years there is a pick of documents referenced followed
+by a two or three years of stagnancy. We can also notice that
+throughouts the year each pick is higher than the older one, which can
+be explained by the fact that The International Society of the Learning
+Sciences community is investigating more and more tools to facilitate
+learning over the years.
+
+    \begin{figure}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_70_0.png}\end{center}
+        \caption{}
+        \label{}
+    \end{figure}
+
+    Since the number of documents is increasing over the years, we also
+wanted to investigate more if the relevance of all the documents
+published is increasing too. Using Pagerank algorithm and the In-degree
+of each nodes to get the most influancial documents referenced of the
+citation graph that we constructed (graph3) before. We filtered the
+first 100 documents and then contructed a histogram of the counts. We
+obtain the figure below:
+
+    \begin{figure}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_72_0.png}\end{center}
+        \caption{}
+        \label{}
+    \end{figure}
+
+    We can see that in the top 100 cited documents more than 12\% are from
+2006, 8\% are from 2013, 6\% from 2014\ldots{} We can not say that we
+have the same trend as before, and the relevance of the documents is
+increasing in the same way than with the number of publications but what
+we can say is that more than 50\% of the most cited documents are from
+2006 until 2016, we is 10 years. The other half is between 1977 until
+2005 which represents more than 25 years. On top of that, 2016 is the
+most important year in term of publications and maybe some documents did
+not have enough time to be cited yet.
+
+    The top 10 of the most influencial and most important referenced papers
+are the following:
+
+    \begin{figure}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_75_0.png}\end{center}
+        \caption{}
+        \label{}
+    \end{figure}
+
+    We also noticed from the first graph that some documents were more
+likely to cited together. We can say that the more two documents are
+likely to cited together the more it is probable that both documents are
+about the same subject From the table below we can also notice that some
+papers cites like to cite the same authors together, which is logic in a
+sense, because if some authors always treat about the same subjects then
+they are experts in that field and a lot of their publications are
+relevant and can be cited together.
+
+    \begin{figure}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_77_0.png}\end{center}
+        \caption{}
+        \label{}
+    \end{figure}
+
+    Using this graph, we also want to extract if there are some clusters of
+papers cited together. As we explained before, we run strongly connected
+algorithm to check if some cited documents are more likely to cited
+together, and this will give us clusters of cited documents that are
+more likely to be about the same subjects. We can visualise one cluster,
+the most important one.
+
+    \begin{figure}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_80_0.png}\end{center}
+        \caption{}
+        \label{}
+    \end{figure}
+
+\begin{Verbatim}[commandchars=\\\{\}]
+{\color{outcolor}Out[{\color{outcolor}185}]:} <IPython.core.display.HTML object>
+\end{Verbatim}
+
+    \begin{figure}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_82_0.png}\end{center}
+        \caption{}
+        \label{}
+    \end{figure}
+
+    The largest strongly connected component is the composed of 8 nodes and
+56 edges. This documents are all cited together more than 4 times. You
+can investingate the edges and the weights in the interactive graph
+constructed above. We wanted all the documents to be linked to each
+others to be more precise, but if we only look to giant connected
+component, we will get a network of 27 referenced paper with 142 egdes.
+
+\begin{Verbatim}[commandchars=\\\{\}]
+{\color{outcolor}Out[{\color{outcolor}236}]:} <IPython.core.display.HTML object>
+\end{Verbatim}
+
+    In the table below are the documents of the giant connected component
+represented in the interactive graph above.
+
+    \begin{figure}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_86_0.png}\end{center}
+        \caption{}
+        \label{}
+    \end{figure}
+
+    Now we want to apply the same logic with the papers in-conferences. So
+we will focus on the analysis of the first graph that uses the
+intersection between the referenced documents of each two by two papers.
+The length of the intersection set had to be more than 4.
+
+So if more than 4 documents are referenced by two distinct documents
+than the latter are more likely to be about the same subect.
+
+    \begin{figure}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_88_0.png}\end{center}
+        \caption{}
+        \label{}
+    \end{figure}
+
+    When applying this kind of clustering we find that most of the clusters
+contains almost the same authors with different papers, which is logic
+because if they are specialists in one topic and write several papers on
+it, they might reuse some references in several documents.
 

### 2019-01-10 Report/paper.tex
push changes

@@
 
-    \documentclass[journal,onecolumn]{IEEEtran}
+    \documentclass[journal,twocolumn]{IEEEtran}
 \usepackage[noadjust]{cite}
@@
 So after groupping the words by year and scaling them we found graph
-below
+below \ref{fig1}
 
@@
         \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_26_0.png}\end{center}
-        \caption{}
-        \label{}
+        \caption{Trends of keywords over the years}
+        \label{fig1}
     \end{figure}
@@
 for each year the words that were present for that year and never for
-the others. We get the graph below. As we can see from the graph, the
-most used word in the papers, more than 10\% of 2015 papers uses the
-word `peer', more than 6\% of the papers uses the words `building',
-`embodied' in 2016. In 2017 the most frequent keyword on is `reponsive'
-and in 2018 `tools' is present with more than 6\%.
+the others. We get the figure below. As we can see from the graph
+\ref{fig2}, the most used word in the papers, more than 10\% of 2015
+papers uses the word `peer', more than 6\% of the papers uses the words
+`building', `embodied' in 2016. In 2017 the most frequent keyword on is
+`reponsive' and in 2018 `tools' is present with more than 6\%.
 
@@
         \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_28_0.png}\end{center}
-        \caption{}
-        \label{}
+        \caption{Distinct keywords over the years}
+        \label{fig2}
     \end{figure}
@@
 This method does not give good results as we can see it in the graph
-below all the vectors are together there is no clear separation between
-the documents. So we decide to use other methods using word embeddings
-and properties of TF-IDF.
+below \ref{fig3} all the vectors are together there is no clear
+separation between the documents. So we decide to use other methods
+using word embeddings and properties of TF-IDF.
 
@@
         \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_31_0.png}\end{center}
-        \caption{}
-        \label{}
+        \caption{Baseline model document clusters}
+        \label{fig3}
     \end{figure}
@@
 the number of clusters than there is no clear separation anymore
-separation.
+separation. The plot below \ref{fig4} reprensents the documents
+belonging to each cluster.
 
@@
         \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_33_0.png}\end{center}
-        \caption{}
-        \label{}
+        \caption{Cluster using Average of GloVe vectors combined with K-means }
+        \label{fig4}
     \end{figure}
@@
 the best separation, with a clear separation of 4 clusters as we can see
-it in the figure below.
+it in the figure below \ref{fig5}.
 
@@
         \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_35_0.png}\end{center}
-        \caption{}
-        \label{}
+        \caption{Cluster using Weighted average of TF-IDF + GloVe  combined with K-means }
+        \label{fig}
     \end{figure}
@@
 
-\begin{Verbatim}[commandchars=\\\{\}]
-{\color{outcolor}Out[{\color{outcolor}212}]:} <IPython.core.display.HTML object>
-\end{Verbatim}
-
-    The resulted graph, is an undirected graph with 805 nodes and 6699
-edges. On this graph we extract two main information : * Strongly
-connected components to be able to detect clusters and related
-documents. * In\_degree in order to check if there are documents that
-are related to a lot of documents and those documents would be more
-general than others, and won't necessarly belong to one specific
-cluster.
+    The resulted graph is plotted in this figure \ref{intersection}, is an
+undirected graph with 805 nodes and 6699 edges. On this graph we extract
+two main information : * Strongly connected components to be able to
+detect clusters and related documents. * In\_degree in order to check if
+there are documents that are related to a lot of documents and those
+documents would be more general than others, and won't necessarly belong
+to one specific cluster.
+
+    \begin{figure}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_41_0.png}\end{center}
+        \caption{Intersection between references graph}
+        \label{intersection}
+    \end{figure}
 
@@
 together in the 5 distinct documents, then the weight of the edge would
-be of 5. We obtain a graph of 10845 nodes and 148594 edges.
-
-\begin{Verbatim}[commandchars=\\\{\}]
-{\color{outcolor}Out[{\color{outcolor}103}]:} <IPython.core.display.HTML object>
-\end{Verbatim}
-
-    \begin{figure}
-        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_44_0.png}\end{center}
+be of 5. We obtain a graph of 10845 nodes and 148594 edges represented
+in this figure \ref{fig6}
+
+    \begin{figure}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_45_0.png}\end{center}
         \caption{}
@@
 we have no out degree for almost every node.
-
-\begin{Verbatim}[commandchars=\\\{\}]
-{\color{outcolor}Out[{\color{outcolor}105}]:} <IPython.core.display.HTML object>
-\end{Verbatim}
 
@@
     \begin{figure}
-        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_50_0.png}\end{center}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_51_0.png}\end{center}
         \caption{One of the connected components of the co-authorship graph}
@@
     \begin{figure}
-        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_52_0.png}\end{center}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_53_0.png}\end{center}
         \caption{Largest Component}
@@
     \begin{figure}
-        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_54_0.png}\end{center}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_55_0.png}\end{center}
         \caption{Subcommunities by Louvain}
@@
     \begin{figure}
-        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_55_0.png}\end{center}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_56_0.png}\end{center}
         \caption{Subcommunities via normalized cuts}
@@
     \begin{figure}
-        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_57_0.png}\end{center}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_58_0.png}\end{center}
         \caption{Different formats used to reference institution}
@@
     \begin{figure}
-        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_64_0.png}\end{center}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_65_0.png}\end{center}
         \caption{Different formats used to reference institution}
@@
     \begin{figure}
-        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_66_0.png}\end{center}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_67_0.png}\end{center}
         \caption{Collaborative papers between countries}
@@
     \begin{figure}
-        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_68_0.png}\end{center}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_69_0.png}\end{center}
         \caption{Movement of participants across institutions}
@@
 The distribution of referenced publications years are plotted in the
-graph below. We can see from the graph that there is a kind of a trend,
-each two, three years there is a pick of documents referenced followed
-by a two or three years of stagnancy. We can also notice that
-throughouts the year each pick is higher than the older one, which can
-be explained by the fact that The International Society of the Learning
-Sciences community is investigating more and more tools to facilitate
-learning over the years.
-
-    \begin{figure}
-        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_70_0.png}\end{center}
-        \caption{}
-        \label{}
+graph \ref{count_ref_docs}. We can see from the graph that there is a
+kind of a trend, each two, three years there is a pick of documents
+referenced followed by a two or three years of stagnancy. We can also
+notice that throughouts the year each pick is higher than the older one,
+which can be explained by the fact that The International Society of the
+Learning Sciences community is investigating more and more tools to
+facilitate learning over the years.
+
+    \begin{figure}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_71_0.png}\end{center}
+        \caption{Distribution of the number of referenced documents belonging to each year}
+        \label{count_ref_docs}
     \end{figure}
@@
 first 100 documents and then contructed a histogram of the counts. We
-obtain the figure below:
-
-    \begin{figure}
-        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_72_0.png}\end{center}
-        \caption{}
-        \label{}
+obtain the figure \ref{fig7}:
+
+    \begin{figure}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_73_0.png}\end{center}
+        \caption{Distribution of the 100 most referenced documents belonging to each year}
+        \label{fig7}
     \end{figure}
@@
     The top 10 of the most influencial and most important referenced papers
-are the following:
-
-    \begin{figure}
-        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_75_0.png}\end{center}
-        \caption{}
-        \label{}
+are represented in table \ref{indegree}:
+
+    \begin{figure}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_76_0.png}\end{center}
+        \caption{In-degree count for each document}
+        \label{indegree}
     \end{figure}
@@
 likely to cited together the more it is probable that both documents are
-about the same subject From the table below we can also notice that some
-papers cites like to cite the same authors together, which is logic in a
-sense, because if some authors always treat about the same subjects then
-they are experts in that field and a lot of their publications are
+about the same subject From the table \ref{fig8} we can also notice that
+some papers cites like to cite the same authors together, which is logic
+in a sense, because if some authors always treat about the same subjects
+then they are experts in that field and a lot of their publications are
 relevant and can be cited together.
@@
     \begin{figure}
-        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_77_0.png}\end{center}
-        \caption{}
-        \label{}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_78_0.png}\end{center}
+        \caption{Count of documents cited together}
+        \label{fig8}
     \end{figure}
@@
 papers cited together. As we explained before, we run strongly connected
-algorithm to check if some cited documents are more likely to cited
+algorithm to check if some cited documents are more likely to be cited
 together, and this will give us clusters of cited documents that are
@@
     \begin{figure}
-        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_80_0.png}\end{center}
-        \caption{}
-        \label{}
-    \end{figure}
-
-\begin{Verbatim}[commandchars=\\\{\}]
-{\color{outcolor}Out[{\color{outcolor}185}]:} <IPython.core.display.HTML object>
-\end{Verbatim}
-
-    \begin{figure}
-        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_82_0.png}\end{center}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_81_0.png}\end{center}
+        \caption{Table of the documents belonging to the same clusters}
+        \label{fig9}
+    \end{figure}
+
+    \begin{figure}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_83_0.png}\end{center}
         \caption{}
@@
 
-\begin{Verbatim}[commandchars=\\\{\}]
-{\color{outcolor}Out[{\color{outcolor}236}]:} <IPython.core.display.HTML object>
-\end{Verbatim}
-
-    In the table below are the documents of the giant connected component
-represented in the interactive graph above.
-
-    \begin{figure}
-        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_86_0.png}\end{center}
-        \caption{}
-        \label{}
+    In the table \ref{fig10} below are the documents of the giant connected
+component represented in the interactive graph \ref{fig11}.
+
+    \begin{figure}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_87_0.png}\end{center}
+        \caption{Giant component graph}
+        \label{fig12}
+    \end{figure}
+
+    \begin{figure}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_88_0.png}\end{center}
+        \caption{Documents belonging to the giant component}
+        \label{fig10}
     \end{figure}
@@
 So if more than 4 documents are referenced by two distinct documents
-than the latter are more likely to be about the same subect.
-
-    \begin{figure}
-        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_88_0.png}\end{center}
-        \caption{}
-        \label{}
+than the latter are more likely to be about the same subect. In the
+table \ref{fig11} we can find some of the papers that belong to the same
+clusters.
+
+    \begin{figure}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_90_0.png}\end{center}
+        \caption{Documents in conferences belonging to the same clusters}
+        \label{fig11}
     \end{figure}

### 2019-01-10 Report/paper.tex
push change

@@
 \renewcommand{\figurename}{Figure}
-\captionsetup{labelformat=simple}\title{Bibliometric Analysis of ICLS and CSCL research}
-\author{\IEEEauthorblockN{Léonore Valentine Guillain, Nour Ghalia Abassi}\par
-    \IEEEauthorblockA{EPFL}
+\captionsetup{labelformat=simple}\title{   }
+\author{
 }
@@
 \item
-  the institutions and countries dominant in the conferences
-\item
-  the differences between ICLS and CSCL with respect to citations,
+  The institutions and countries dominant in the conferences
+\item
+  The differences between ICLS and CSCL with respect to citations,
   contributors and publications
 \item
-  first insight into changes of the years with respect to citations,
+  First insight into changes of the years with respect to citations,
   contributors and publications
 \item
-  collaboration network patterns with respect to countries, institutions
+  Collaboration network patterns with respect to countries, institutions
   and authors
 \item
-  the migration of participants across institutions
-\item
-  trends of keywords over the years
-\item
-  trends of citations and evolution of the number of documents from 1977
+  The migration of participants across institutions
+\item
+  Trends of keywords over the years
+\item
+  Trends of citations and evolution of the number of documents from 1977
   until 2018
 \item
-  clusters of the cited documents
-\item
-  clusters of the papers written within the conferences
+  Clusters of the cited documents
+\item
+  Clusters of the papers written within the conferences
 \end{itemize}

### 2019-01-11 Report/paper.tex
push change

@@
 
-    \documentclass[journal,twocolumn]{IEEEtran}
+    \documentclass[article,twocolumn]{IEEEtran}
 \usepackage[noadjust]{cite}
@@
 participants and of the research being conducted within the community.
-After describing how to extract data from the original dataset we derive
+After describing how to extract data from the base dataset we derive
 insights into the community using network analysis, natural language
@@
 with each other. At the time of writing the dataset contains 4 years of
-the proceedings, staring from 2015 to 2018. While ICLS covers the entire
-field of the learning sciences, CSCL focuses on learning through
-collaboration with the help of communication technologies \cite{ICLS}.
-To understand the community formed by the participants of the
-conferences as well as to understand the research being conducted within
-the community, we explore methods to bring insight into the following
-aspects:
+the proceedings, from 2015 to 2018. While ICLS covers the entire field
+of the learning sciences, CSCL focuses on learning through collaboration
+with the help of communication technologies \cite{ICLS}. To understand
+the community formed by the participants of the conferences as well as
+to understand the research being conducted within the community, we
+explore methods to bring insight into the following aspects:
 
@@
   The differences between ICLS and CSCL with respect to citations,
-  contributors and publications
-\item
-  First insight into changes of the years with respect to citations,
-  contributors and publications
+  research conducted and contributors
 \item
@@
 \item
+  First insight into changes over the years with respect to contributors
+  and collaboration patterns
+\item
   The migration of participants across institutions
 \item
-  Trends of keywords over the years
-\item
-  Trends of citations and evolution of the number of documents from 1977
-  until 2018
-\item
-  Clusters of the cited documents
-\item
-  Clusters of the papers written within the conferences
+  Popularity of keywords over the years
+\item
+  Trends inregards to citated papers and the evolution of their
+  prevalence from 1977 until 2018
+\item
+  Discovering clusters of the cited documents
+\item
+  Discovering clusters of the papers written within the conferences
 \end{itemize}
@@
 well as associated metadata in \emph{xml} format. To extract information
-from the dataset we first convert the data to a format that is more
+from the dataset we first converted the data to a format that is more
 adapt to the task of data analysis and more compatible with a variety of
-external libraries. We store all the resulting data in \emph{csv}
+external libraries. We stored all the resulting data in \emph{csv}
 format, as csv is a human readable format and can easily be processed by
@@
 
-We extract the metadata from the xml files using the \emph{lxmltree}
-python library. We associate the contents of each xml tag to a column in
-csv file. As the xml files do not exactly follow the xml standard, we
-handle errors by iteratively parsing the xml tree. For some files, the
-section containing the keywords is malformed which can not be handled by
-the parser. This is remedied by using regular expressions to match the
-section contains the keywords. To each file we associate the name of the
-source file and the order in which an author name occurs in the xml
-file. Each author is associated one line in the XML file. From the
-associated citation string we add to the first part of the citation
-containing the author names, year and title. which we use to identify
-references in other papers to that paper. Then we add a shortened
-version of author names (i.e.~West, R.) by considering the author order.
-Note that the short name extracted from the citation and the
-corresponding long name (Robert West) in the metadata do at times not
-match up. Thus the author order listed in the citation string does not
-always correspond to the author order listed in the metadata. After
-extraction, we clean the data by unifying names, as slight spelling
-differences exist within the same author name (i.e.~Robert West, Robert
-A. West). When unifying the names we need to make sure to not overmerge
-by labeling to different authors as having the same name. First, we use
-a strict condition to catch small differences in names, such as an extra
-middle name. This is done by splitting up names into substrings based on
-whitespace and commas. For two names in the dataset we check whether the
-intersection of their sets of substrings contains at least 2 names of
-length at least 3. If the condition is met we consider these two names
-to be identical, and add the mapping from one name to the other to a
-dictionary. Once all tuples of names (s.t. the first name appears before
-the second one in order) are checked and added to the dictionary we
-unify the names. Using this method we reduce the number of authors in
-the dataset from 1951 down to 1879. Further, to merge names with
-misspellings or people that use nicknames (Christian vs Chris) and avoid
-over-merging we consider only names of authors that have similar
-collaboration patterns. To do this we build the graph of co-authors and
-check names of authors that are in the same neighborhood of a node on
-the graph (see methodology for further details). Then we use the
+We extracted the metadata from the xml files using the \emph{lxmltree}
+python library. We associated the contents of each xml tag to a column
+in a csv file. As the xml files do not exactly follow the xml standard,
+we handled errors by iteratively parsing the xml tree. For some files,
+the section containing the keywords is malformed and can not be
+extracted by the parser. This was remedied using regular expressions to
+match the section containing the keywords. To each file we associated
+the name of the source file and the order in which an author name occurs
+in the xml file. Each author is associated to one line in the xml file.
+From the associated citation string we add to the first part of the
+citation containing the author names, year and title. This is later used
+to identify the paper when it is referenced in an other paper. Then we
+add a shortened version of author names (i.e.~West, R.) by considering
+the author order. Note that it happens that the short name extracted
+from the citation and the corresponding long name (Robert West) in the
+metadata do not match up. Thus the author order listed in the citation
+string does not always correspond to the author order listed in the
+metadata. After extraction, we cleaned the data by unifying names, as
+slight spelling differences exist within the same author name
+(i.e.~Robert West, Robert A. West). When unifying the names we needed to
+make sure not to overmerge by labeling two different authors as having
+the same name. First, we used a strict condition to catch small
+differences in names, such as an extra middle name. This is done by
+splitting up names into substrings based on whitespaces and commas. For
+two names in the dataset we checked whether the intersection of their
+sets of substrings contained at least 2 names of length at least 3. If
+the condition was met we considered these two names to be identical, and
+added the mapping from one name to the other to a dictionary. Once all
+tuples of names (s.t. the first name appears before the second one in
+order) were checked and added to the dictionary we unified the names.
+Using this method we reduced the number of authors in the dataset from
+1951 down to 1879. Further, to merge names with misspellings or people
+who use nicknames (Christian vs Chris) and to avoid overmerging we
+considered only names of authors that have similar collaboration
+patterns. To do this we built a graph based on co-authors relations and
+checked names of authors that were in the same neighborhood of a node on
+the graph (see methodology for further details). Then, we used the
 \emph{difflib} library to check for similarity of two strings and
-consider a name to belong to the same person if they reach the threshold
-of 0.8. Again names considered to belong to the same person are added to
-the mapping dictionary which is then applied to all names. This method
-again reduces the number of authors in the dataset from 1879 to 1951.
+considered a name to belong to the same person if the similarity measure
+reached the threshold of 0.8. Again names considered to belong to the
+same person were added to the mapping dictionary which was then applied
+to all names. This method again reduced the number of authors in the
+dataset from 1879 to 1951.
 
@@
 
-To extract information from the papers themselves we need to first
+To extract information from the papers themselves we needed first to
 extract the text from the pdfs. Various parsers performing this task
-exist. However, parsers such as pdfminer, PyPDF2 that claim to be able
+exist. However, parsers such as pdfminer or PyPDF2 that claim to be able
 to extract the text as well as metadata from papers have not been kept
@@
 contained in the pdfs to \emph{txt} format. All methods describing how
-to extract data from the papers work on the extracted \emph{txt} files.
-The characters contained in the \emph{txt} files are not all encoded
-uniformly, which means that characters that look the same to humans may
-be encoded in different way . Hence, for many applications we need to
-unify the formating. This is done using the \emph{unicodedata} module
-and setting converting all characters to `Normal Form Composed' form .
+to extract data from the papers worked on the extracted \emph{txt}
+files. The characters contained in the \emph{txt} files were not all
+encoded uniformly, which means that characters that look the same to
+humans may be encoded in different ways. Hence, for many converting all
+characters to `Normal Form Composed' form.
 
 A convenient property of papers is that they are structured fairly
-regularly. The ISLS Author Guidelines \cite{guidelines} give us guidance
-on how the papers in our dataset should be structured. We use this to
+regularly. The ISLS Author Guidelines \cite{guidelines} gave us guidance
+on how the papers in our dataset should be structured. We used this to
 our advantage when extracting information from the paper text. While the
 vast majority of papers in the dataset follow these guidelines,
-exceptions do exist. We thus make sure to handle deviations from the
+exceptions do exist. We thus made sure to handle deviations from the
 structure.
@@
 
-We know that each valid paper contains a reference section at the end
-listing all the references cited in the paper. While tools are being
-developed to extract the reference section directly from pdfs, notably
-Scholarcy \cite{scholarcy}, they did not produce satisfactory results.
-That is they had issues splitting the references correctly and
-categorizing parts of the reference accurately. This may occur because
-they are trained to extract any reference format, and thus can not make
-many assumptions on the structure. But in our dataset papers following
-the guidelines should list their references in APA format. Hence using
-regular expressions and background on how APA references gives us better
-results than out of the box methods.
+Each valid paper contains a reference section at the end listing all the
+references cited in the paper. While tools are being developed to
+extract the reference section directly from pdfs, notably Scholarcy
+\cite{scholarcy}, they did not produce satisfactory results. That is,
+they did not split the references correctly and categorized parts of the
+reference inaccurately. This may occur because they are trained to
+extract any reference format, and thus can not make many assumptions on
+the structure. But in our dataset papers following the guidelines should
+list their references in APA format. Hence using regular expressions and
+background on APA referencing gave us better results than out of the box
+methods.
 
 \textbf{Regular expressions in python:} Python has two modules that
-implement regular expressions \emph{re} and \emph{regex}. We used regex
+implement regular expressions, \emph{re} and \emph{regex}. We used regex
 as --unlike the re module-- this module allows to handle strings with
 non-ascii characters by having unicode expressions. As many authors have
-names with non-ascii characters this is an important capability.
-
-\textbf{To get the reference section for of a paper} we use a regular
+names containing non-ascii characters this is an important capability.
+
+\textbf{To get the reference section for of a paper} we used a regular
 expressions to find the reference header and determine the sections end
-by checking for acknowledgement or appendix sections in the text file
+by checking for acknowledgements or appendix sections in the text file
 previously extracted using poppler. Then, to extract individual
 references we split the section into a list of substrings at each new
-line character and glue substrings back together if they satisfy a set
-of conditions. We found this method to be robust as it makes sure that
-all properly formatted references are separated.
-
-\textbf{To unify substrings} we exploit the fact that that APA
-references all have the same initial structure: \emph{Lastname F.M.
-(when published) Title which may contain colons and other non-alphabetic
-chars. Where published. Who published} \cite{apaformat}. We thus check
+line character and concatenated substrings back together if they
+satisfied a set of conditions. We found this method to be robust as it
+makes sure that all properly formatted references are separated.
+
+\textbf{To unify substrings} we exploited the fact that APA references
+all have the same initial structure: \emph{Lastname F.M. (when
+published) Title which may contain colons and other non-alphabetic
+chars. Where published. Who published} \cite{apaformat}. We thus checked
 that the beginning of each reference contains ``Lastname F.M. (when
@@
 does not contain such a section, then it must be part of an other
-reference, which is lies before in the list of reference substrings.
-Note that this beginning is also what is added to the metadata as
-identifying string. We found that in practical application it is
-important to first merge lines if they were clearly cut off, as papers
-with many authors may have the beginning on multiple lines. We can find
-split up lines by checking for lines starting with non-alphabetic
-characters or starting in a sentence. We merge these with the line
-above. We can identify lines by their ending as being split up, such as
-if they end in a comma, colon or only contain author names. We merge
-these lines with the lines below them. Only then can we check whether a
-line contains a valid citation start. If it does not we merge it with
-the line above it. After this merging process we validate the returned
-reference split by looking at the overall length and the initials, as
-well as checking that a random sample returns satisfactory splitting
-accuracy. We find that the above method of extracting the references
-produces good results for proper APA citations and on APA citations
-indeed outperforms Scolarcy when it comes to splitting up the lines.
-\emph{To then get the subcomponents of a reference} is rather trivial,
-as we can again use the structure of APA citations. The string before
-the first parenthesis contains the authors names, inside the parentheses
-we find the year or some other reference to publication time, after
-which the title follows until the first dot. Then a reference to the
-publishing venue follows.
-
-    \begin{figure}
-        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_10_0.png}\end{center}
-        \caption{Different formats used to reference institution}
-        \label{figA}
-    \end{figure}
-
-    \begin{figure}
-        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_11_0.png}\end{center}
-        \caption{Different formats used to reference institution}
-        \label{figB}
-    \end{figure}
+reference, which lies before in the list of reference substrings. Note
+that this beginning is also what is added to the metadata as identifying
+string. We found that in practical application it is important to first
+merge lines if they were clearly cut off, as papers with many authors
+may have the beginning on multiple lines. We could find split up lines
+by checking for lines starting with non-alphabetic characters or
+starting in a sentence. We merged these with the line above. We could
+identify lines by their ending as being split up, such as if they end in
+a comma, colon or only contain author names. We merged these lines with
+the lines below them. Only then could we check whether a line contained
+a valid citation start. If it did not we merged it with the line above
+it. After this merging process we validated the returned reference split
+by looking at the overall length and the initials, as well as by
+checking that a random sample returned satisfactory splitting accuracy.
+We found that the above method of extracting the references produced
+good results for proper APA citations and on APA citations indeed
+outperformed Scolarcy when it came to splitting up the lines.
+
+\textbf{To then get the subcomponents of a reference} was rather
+trivial, as we could again use the structure of APA citations. The
+string before the first parenthesis contains the authors names, inside
+the parentheses we find the year or some other reference to publication
+time, after which the title follows until the first dot. Then a
+reference to the publishing venue follows.
 
@@
 Now we consider the section before the abstract, which contains the
-authors names, their email and the institution they are affiliated with.
-Affiliation with institution can give us a lot of insight where people
-are working and gives use a way estimate where they are from. To go from
-this section to an exact affiliation with an institution a multifaceted
-approach was used.
+authors names, their email addresses and the institutions they are
+affiliated with. Affiliation with institution can give us a lot of
+insight where people are working and gives use a way estimate where they
+are from. To extract the exact affiliation of an authors with an
+institution two approaches were used.
 
@@
 The most robust way to get a persons institution affiliation is to use
-their email. Emails can easily be extracted from the header section
-using a regular expression and given a domain-university mapping
-\cite{mapping} give us an onto mapping from domain to institution. The
-additional advantage of this method is that using the additional
+their email address. Email addresses can easily be extracted from the
+header section using a regular expression. Then we used a
+domain-university mapping \cite{mapping} to map domains to institutions.
+The additional advantage of this method is that using the additional
 metadata associated to each university in the mapping, we also access
@@
 
+    \begin{figure}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_11_0.png}\end{center}
+        \caption{Different formats used to reference institution}
+        \label{figA}
+    \end{figure}
+
+    \begin{figure}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_12_0.png}\end{center}
+        \caption{Different formats used to reference institution}
+        \label{figB}
+    \end{figure}
+
     \hypertarget{approach-2}{%
@@
 The header section itself contains information on the institution, but
-as different was to list authors are accepted, notably two ways as can
-be seen in Figure \ref{figA} and Figure \ref{figB}. Hence, we first
-detect the structure of the header section before extracting the
-association. We tag the substring present in this section using a
+different ways to list authors are accepted, notably two ways as can be
+seen in Figure \ref{figA} and Figure \ref{figB}. Hence, we first
+detected the structure of the header section before extracting the
+association. We tagged the substring present in this section using a
 combination of \emph{named entity detection}, using the implementation
@@
 to detect where in the header the email is. Then, taking the tagged
-section, we detect which subsections correspond to which
-author-affiliation listing type, and extract the author email -
+section, we detected which subsections corresponded to which
+author-affiliation listing type, and extracted the author email -
 institution mapping accordingly.
@@
 companies will be in the mapping-- and many participants use gmail and
-similar providers as their official correspondence email. However,
-Approach 2 may contain differences in spelling in the institution name,
-which need to be merged. Thus we combine both approaches, and use the
-corresponding institutions in Approach 1 to unify the institutions
-obtained in Approach 2. Furthermore, we later merge names by considering
-the location of the institutions.
-
-But first as with Approach 2 institution affiliation does not allow us
-to automatically associate a country to the institution, we need to get
-this through other means. A first step is to use the top level domains
+similar providers as their official email. However, Approach 2 may
+contain differences in spelling in the institution name, which needed to
+be merged. Thus we combined both approaches, and used the corresponding
+institutions in Approach 1 to unify the institutions obtained in
+Approach 2. Furthermore, we later merged names by considering the
+location of the institutions.
+
+But first as with Approach 2 institution affiliation did not allow us to
+automatically associate a country to the institution, we needed to get
+this through other means. A first step was to use the top level domains
 present in the emails to associate a country of origin to the
 participants and their associated institutions. Then, to plot the
-community we augment the dataset with geolocation information. As a
-further benefit, having this information we can then easily associate a
-country to the institution for the emails that do not have a top level
-domain indicating location and merge the names of institutions where
-necessary based on location.
+community we augmented the dataset with geolocation information. As a
+further benefit, having this information we could then easily associate
+a country to the institution for the emails that do not have a top level
+domain indicating location and further merge the names of institutions
+based on location.
 
@@
 institutions, even well known ones such as Tokyo University, have their
-coordinates listed on their Wikipedia. To get the remaining locations we
-use the geopy, which is a client for geocoding web services. These
-results however are more error prone and will always return a result. It
-is thus recommended to verify the correctness of the results. To get the
-country we can then again use geopy. The resulting data containing paper
+coordinates listed on Wikipedia. To get the remaining locations we used
+the geopy, which is a client for geocoding web services. These results
+however are more error prone and will always return a result. It is thus
+recommended to verify the correctness of the results. To get the country
+we then again used geopy. The resulting data containing paper
 identifier, the authors email, its associated domain, order in which the
-author was cited, the institution, country, Longitude and Latitude are
-saved to a csv file. We use the paper identifier and author order to
+author was cited, the institution, country, Longitude and Latitude were
+saved to a csv file. We used the paper identifier and author order to
 associate this data with the metadata to link information about authors
@@
 
-\textbf{\emph{How it works}} : * It splits the text into sentences and
-generates some words as candidates.\\
-* Various punctuation signs will be treated as sentence boundaries. *
+\textbf{\emph{How it works}} :
+
+\begin{itemize}
+\tightlist
+\item
+  It splits the text into sentences and generates some words as
+  candidates.\\
+\item
+  Various punctuation signs will be treated as sentence boundaries.
+\item
   All words listed in the stopwords file will be treated as phrase
@@
   part of the phrase. For example, `new' is listed in RAKE's stopword
-list. This means that neither `New York' nor `New Zealand' can be ever a
-keyword. * For each keyword candidate generated, the algorithm computes
-the score of the pretended keyword, which is the sum of the scores for
-each of its words (if it's a composed word). The words are scored
-according to their frequency and the typical length of a candidate
-phrase in which they appear. * The last step is ranking the scores ansd
-selecting the ones with the highest score
+  list. This means that neither `New York' nor `New Zealand' can be ever
+  a keyword.
+\item
+  For each keyword candidate generated, the algorithm computes the score
+  of the pretended keyword, which is the sum of the scores for each of
+  its words (if it's a composed word). The words are scored according to
+  their frequency and the typical length of a candidate phrase in which
+  they appear.
+\item
+  The last step is ranking the scores ansd selecting the ones with the
+  highest score
+\end{itemize}
 
@@
     \begin{figure}
-        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_26_0.png}\end{center}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_27_0.png}\end{center}
         \caption{Trends of keywords over the years}
@@
     We wanted then to know what are the trends of words for each specific
-year, so we select distinct words for each year, it means that we select
-for each year the words that were present for that year and never for
-the others. We get the figure below. As we can see from the graph
-\ref{fig2}, the most used word in the papers, more than 10\% of 2015
-papers uses the word `peer', more than 6\% of the papers uses the words
-`building', `embodied' in 2016. In 2017 the most frequent keyword on is
-`reponsive' and in 2018 `tools' is present with more than 6\%.
-
-    \begin{figure}
-        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_28_0.png}\end{center}
+year, so we select distinct words for each year. On other words it means
+that we select for each year the words that were only present for this
+specific year and never appeared in the others. We get the figure below.
+As we can see from the graph \ref{fig2}, the most used word in the
+papers, more than 10\% of 2015 papers uses the word `peer', more than
+6\% of the papers uses the words `building', `embodied' in 2016. In 2017
+the most frequent keyword on is `reponsive' and in 2018 `tools' is
+present with more than 6\%.
+
+    \begin{figure}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_29_0.png}\end{center}
         \caption{Distinct keywords over the years}
@@
 ordered by term frequency across the corpus. On this word representation
-we will run K-means.
+we run K-means.
 
@@
     \begin{figure}
-        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_31_0.png}\end{center}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_32_0.png}\end{center}
         \caption{Baseline model document clusters}
@@
     \begin{figure}
-        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_33_0.png}\end{center}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_34_0.png}\end{center}
         \caption{Cluster using Average of GloVe vectors combined with K-means }
@@
     \begin{figure}
-        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_35_0.png}\end{center}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_36_0.png}\end{center}
         \caption{Cluster using Weighted average of TF-IDF + GloVe  combined with K-means }
@@
     \begin{figure}
-        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_41_0.png}\end{center}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_42_0.png}\end{center}
         \caption{Intersection between references graph}
@@
 together in the 5 distinct documents, then the weight of the edge would
-be of 5. We obtain a graph of 10845 nodes and 148594 edges represented
-in this figure \ref{fig6}
-
-    \begin{figure}
-        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_45_0.png}\end{center}
-        \caption{}
-        \label{}
+be of 5. We obtain a graph of 10845 nodes and 148594 edges but we
+filtered the edges that have a weight higher than 4 and we get the graph
+below represented in this figure \ref{fig6}
+
+    \begin{figure}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_46_0.png}\end{center}
+        \caption{Relations between references filtered}
+        \label{fig6}
     \end{figure}
@@
 
-To get insight into collaborations within the community we build graphs
+To get insight into collaborations within the community we built graphs
 based on co-authorship of papers. To build the graph structure and
@@
 First, we built a co-authorship graph based on individual authors. Each
-node represents an author, and two nodes are connected if the authors
+node represented an author, and two nodes were connected if the authors
 collaborated on a paper. Other works \cite{cheong2009social},
@@
 link from the first author of the paper to all other authors. However,
-as we are more interested in collaboration patterns and less in finding
-the most influential first author, we build an undirected graph with
-edges between all co-authors. On the downside, this yields a very dense
-graph. Hence, we prune the initial graph by removing nodes that do not
+as we were more interested in collaboration patterns and less in finding
+the most influential first author, we built an undirected graph with
+edges between all co-authors. On the downside, it yielded a very dense
+graph. Hence, we pruned the initial graph by removing nodes that did not
 satisfy additional conditions. Intuitively it is clear that a singular
 collaboration on a paper does not necessarily indicate that two people
-even know each other. A first condition was to only link two nodes
-together if the authors corresponding to each node have appear as
-co-authors in more than one conference. The graph produced by this
-approach is much more sparse and contains much fewer authors.
-Additionally all connected components contain fewer than 50 authors,
-making it possible to consider each author individually. Such a
-component is shown in figure \ref{fig_plot}.
-
-    \begin{figure}
-        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_51_0.png}\end{center}
+even know each other. A first condition was to link two nodes together
+only if the authors corresponding to each node appeared as co-authors in
+more than one conference. The graph produced by this approach was much
+more sparse and contained much fewer authors. Additionally all connected
+components contained fewer than 50 authors, making it possible to
+consider each author individually. Such a component is shown in figure
+\ref{fig_plot}.
+
+    \begin{figure}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_52_0.png}\end{center}
         \caption{One of the connected components of the co-authorship graph}
@@
 the graph authors are only linked if they have written at least 2 papers
-together. This method yields a much larger component --containing 441
-authors-- as this second condition is weaker. To get an understanding of
-author to author relations in this component we need to further prune
-away parts of the graph that are not insightful. When we look at
-individual author within the community, we are interested well
-collaborative individuals. Hence we remove nodes that have collaborated
+together. This method yielded a much larger component --containing 441
+authors-- as this second condition was weaker. To get an understanding
+of author to author relations in this component we needed to further
+prune away parts of the graph that are not insightful. When we looked at
+individual author within the community, we were interested in
+collaborative individuals. Hence we removed nodes that had collaborated
 with fewer than 3 connections to other authors. The resulting graph can
@@
     \begin{figure}
-        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_53_0.png}\end{center}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_54_0.png}\end{center}
         \caption{Largest Component}
@@
 component with 1141 authors and 208 very small components with less than
-25 authors in them we focus on analyzing the structure of the main
-component of the graph. First we aim to detect sub-communities within
+25 authors in them we focused on analyzing the structure of the main
+component of the graph. First we aimed to detect sub-communities within
 the graph. Modularity is one measure used to find such communities. It
@@
 communities of median size 42.84. This is quite a large number of
-communities, so we consider an alternative way to yield bigger
+communities, so we considered an alternative way to yield bigger
 partitions. An alternate way to find subcommunities is to look at
@@
 With this method we are able to neatly separate the main component graph
-in three large communities. We note that the clusters found using method
-one are contained in the clusters found by method 2. See Figure
-\ref{Louvain} and Figure \ref{normalized}.
-
-    \begin{figure}
-        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_55_0.png}\end{center}
-        \caption{Subcommunities by Louvain}
-        \label{Louvain}
-    \end{figure}
-
-    \begin{figure}
-        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_56_0.png}\end{center}
-        \caption{Subcommunities via normalized cuts}
-        \label{normalized}
-    \end{figure}
-
-    To further analyze these subcommunities we look at the distribution of
+in three large communities. See figure \ref{normalized}
+
+    To further analyze these subcommunities we looked at the distribution of
 nationalities and institutions over the years. Additionally, to
-understand differences in the research being conducted, we analyze the
+understand differences in the research being conducted, we analyzed the
 frequency of keywords used for the papers that were writing within that.
@@
 To get a better overview of how co-authorship happens across countries
-and institutions, we built graphs where every node represents a country
-respectively an institution. Two countries or institutions are linked if
-two authors from these two institutions collaborated on a paper
-together. The country graph is simple enough that it does not have to be
-pruned. The institution graph on the other hand is again not
+and institutions, we built graphs where every node represented a
+country, respectively an institution. Two countries or institutions were
+linked if two authors from these two institutions collaborated on a
+paper together. The country graph is simple enough that it does not have
+to be pruned. The institution graph on the other hand is again not
 comprehensible without further processing. Thus, similar to the first
-approach on pruning presented, we only consider institutions who
+approach on pruning presented, we only considered institutions who
 collaborated in at least two conferences. This the main component of
@@
     \begin{figure}
-        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_58_0.png}\end{center}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_57_0.png}\end{center}
         \caption{Different formats used to reference institution}
@@
 degree centrality for graphs with few nodes and edges and betweenness
-centrality for larger graphs . Degree centrality measures the fraction
-of degrees (number of connections) a node has with respect to the total
+centrality for larger graphs. Degree centrality measures the fraction of
+degrees (number of connections) a node has with respect to the total
 number of connections in the graph. Betweenness centrality of a node is
 the sum of the fraction of all-pairs shortest paths that pass through
-it. Degree centrality is more adept for smaller graphs as their
+it. Degree centrality is more appropriate for smaller graphs as their
 structure is still easy to interpret. As by construction betweenness
@@
 
-To better understand and interact with the data we create interactive
+To better understand and interact with the data we created interactive
 graphs on top of the static graphs. Many libraries exist to allow for
@@
 allows to easily build interactive figures, while not being as heavy as
-booked and holoviews. Additionally, it is the most well maintained. D3
+bookeh and holoviews. Additionally, it is the most well maintained. D3
 requires a running server to be viewed and has a hard time dealing with
-large graphs. To plot figures we create them in networkx to grab the
-positioning of the nodes. Then we pass this positioning to plotly to
+large graphs. To plot figures we created them in networkx to grab the
+positioning of the nodes. Then we passed this positioning to plotly to
 plot.
@@
     \begin{figure}
-        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_65_0.png}\end{center}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_64_0.png}\end{center}
         \caption{Different formats used to reference institution}
@@
 
-*\textbf{International Collaboration:} The U.S. again stands out as a
+\textbf{International Collaboration:} The U.S. again stands out as a
 major player, with most collaborations happening between the U.S. and
@@
 collaborations. Out of these 153, 108 involved at least one U.S.
-participant. Excluding U.S. participation we find figure \ref{}. We
-noted that Finland is very collaborative, and that there exists a strong
-bond between Sweden and Israel. Additionally we observed that Asian
-nations seem to collaborate almost exclusively with each other or
-Canada.
-
-    \begin{figure}
-        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_67_0.png}\end{center}
+participant. Excluding U.S. participation we find figure
+\ref{figcollab}. We note that some countries, such as Japan, are not
+present in this graph. This means that all international collaboration
+of these countries, in this case japanese authors, also involves
+American authors. Additionally we observed that many asian nations seem
+to collaborate almost exclusively with each other or Canada.
+
+    \begin{figure}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_66_0.png}\end{center}
         \caption{Collaborative papers between countries}
@@
     \end{figure}
+
+    \textbf{Inter-institution collaboration}: In regards to collaboration
+between institutions, 318 out of the 815 papers were written in
+collaboration of authors from different institutions. The most
+collaborative university is the University of Indiana at Bloomington,
+followed by the University of Toronto. Considering the graph of
+university collaboration, we saw that none of the nodes is solitary -
+all institutions in the conference have collaborated with another
+institution at least once. There is a large main component and 6 other
+smaller clusters of universities. The cluster of main institutions
+collaborating in two conferences can be seen in figure \ref{unigraph}.
+We see that the topology of the cluster is rather odd, and that while
+some strong links exist, most links are weak.
+
+    \begin{figure}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_68_0.png}\end{center}
+        \caption{Subcommunities via normalized cuts}
+        \label{normalized}
+    \end{figure}
+
+    \begin{figure}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_69_0.png}\end{center}
+        \caption{Subcommunities by paricipation in CSCL. Blue: no participation in main compnents of CSCL. Red and Violate each mark participation in one of the two main components of CSCL}
+        \label{CSCL_components}
+    \end{figure}
+
+    \textbf{Author collaboration}: As the graph yielded by only considering
+repeat collaboration during different years is sparse, containing
+connected components of size at most 25, we deduce that repeat
+collaboration over the years is rather infrequent. As the graph
+conditioned on multiple collaboration is more dense (having a component
+of the size 400), we deduce that when multiple collaborations with the
+same authors happen, they yield work submitted at the same time.
+
+The fact that normalized graph cuts will split the community into three
+promted further investigation. As will be discussed in the next section,
+the graph of authors that participanted in CSCL yields two large
+connected components. By coloring the authors contained in the two CSCL
+components different colors, and authors in neither a third color, we
+find a similar partitioning of the graph, as can be observed in figure
+\ref{CSCL_components}. This is somewhat trivial, as the graph is built
+based on collaboration in these conferences. However, the analysis of
+nationalities present in the graph yield an interessting results. All
+Asian participants from nations other than Singapore are contained in
+the same cluster. We also note that one of the CSCL clusters ins closer
+to the group of ICLS only participants than the other. Additionaly,
+through normaized splits, we find that the section of the normalized cut
+containing ICLS only authors is overwhelmingmly american.
+
+Considering the wordclouds in figure \ref{c1}, \ref{c2}, \ref{c3} of the
+most common keywords in each of the large splits, we find a first
+indication that the splits also reflect some thematic differences in
+research.
+
+    \begin{figure}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_71_0.png}\end{center}
+        \caption{Keywords of the bottom community}
+        \label{c1}
+    \end{figure}
+
+    \begin{figure}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_72_0.png}\end{center}
+        \caption{Keywords of the middle community}
+        \label{c2}
+    \end{figure}
+
+    \begin{figure}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_73_0.png}\end{center}
+        \caption{Keywords of the top community}
+        \label{c3}
+    \end{figure}
+
+    \hypertarget{icls-and-cscl}{%
+\subsubsection{ICLS and CSCL}\label{icls-and-cscl}}
+
+In our analysis, we could find many structural differences between the
+two conferences. Firstly, ICLS is much larger and american dominated
+than CSCL. We also observed differences in the most cited papers and the
+average number of authors of a paper. By constructing the graph based on
+collaboration of authors in each conference, we find that while ICLS
+contains one giant component, CSCL contains two large main components.
+All these results are however to be taken with a grain of salt, as for
+each conference we only have data for two years, and the year 2018 is a
+marked outlier. Additionaly, we are unable to find a strong difference
+between the metrics of the graphs, that is diameter, density, clustering
+coefficient and average path length.
 
@@
     \begin{figure}
-        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_69_0.png}\end{center}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_76_0.png}\end{center}
         \caption{Movement of participants across institutions}
@@
     \end{figure}
+
+    \hypertarget{changes-over-the-years}{%
+\subsection{Changes over the years}\label{changes-over-the-years}}
+
+We can observe a growth of the number of participants over the years,
+and by building co-authorship graphs for each year of the conference, we
+observe that the density and clustering coefficient of the graph
+indicate a steady decrease, while the diameter and average shortest path
+length tend to increase. This hints that the community is attracting new
+member that do not collaborate with the established group of
+participants. But, as the years 2018 shows a massive increase of
+participation, in number of participants and number of institutions
+represented, as well as a large decrease in density of the graph --which
+is reduced by more than half from the previous ICLS conference-- it is
+impossible to draw any statisically significant conclusions.
 
@@
     \begin{figure}
-        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_71_0.png}\end{center}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_79_0.png}\end{center}
         \caption{Distribution of the number of referenced documents belonging to each year}
@@
     \begin{figure}
-        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_73_0.png}\end{center}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_81_0.png}\end{center}
         \caption{Distribution of the 100 most referenced documents belonging to each year}
@@
     \begin{figure}
-        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_76_0.png}\end{center}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_84_0.png}\end{center}
         \caption{In-degree count for each document}
@@
     \begin{figure}
-        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_78_0.png}\end{center}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_86_0.png}\end{center}
         \caption{Count of documents cited together}
@@
     \begin{figure}
-        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_81_0.png}\end{center}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_89_0.png}\end{center}
         \caption{Table of the documents belonging to the same clusters}
@@
     \begin{figure}
-        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_83_0.png}\end{center}
-        \caption{}
-        \label{}
-    \end{figure}
-
-    The largest strongly connected component is the composed of 8 nodes and
-56 edges. This documents are all cited together more than 4 times. You
-can investingate the edges and the weights in the interactive graph
-constructed above. We wanted all the documents to be linked to each
-others to be more precise, but if we only look to giant connected
-component, we will get a network of 27 referenced paper with 142 egdes.
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_91_0.png}\end{center}
+        \caption{Fully connected references graph}
+        \label{fig12}
+    \end{figure}
+
+    The largest fully connected component is the composed of 8 nodes and 56
+edges plotted in figure \ref{fig14}. This documents are all cited
+together more than 4 times. You can investingate the edges and the
+weights in the interactive graph constructed above. We wanted all the
+documents to be linked to each others to be more precise, but if we only
+look to giant connected component, we will get a network of 27
+referenced paper with 142 egdes.
 
@@
     \begin{figure}
-        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_87_0.png}\end{center}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_95_0.png}\end{center}
         \caption{Giant component graph}
@@
     \begin{figure}
-        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_88_0.png}\end{center}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_96_0.png}\end{center}
         \caption{Documents belonging to the giant component}
@@
     \begin{figure}
-        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_90_0.png}\end{center}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_98_0.png}\end{center}
         \caption{Documents in conferences belonging to the same clusters}
@@
 
-Lorem ipsum dolor sit amet, consectetur adipiscing elit, sed do eiusmod
-tempor incididunt ut labore et dolore magna aliqua. Ut enim ad minim
-veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea
-commodo consequat. Duis aute irure dolor in reprehenderit in voluptate
-velit esse cillum dolore eu fugiat nulla pariatur. Excepteur sint
-occaecat cupidatat non proident, sunt in culpa qui officia deserunt
-mollit anim id est laborum.
+In summary, we were able to extract how the dominant some institutions
+and countries are within the conference. Some initiall collaboration
+patterns between countries, instututions and authors were extracted.
+Subcommunities found within the network of co-authorship reflect the
+division between conferences and within the conference. Using the
+analysis of the affiliation over the years we followed the migration of
+participants accross institutions. Natural language preprocessing and
+metadata parsing enabled the extraction of trends of keywords over the
+years
+
+Overall, due to lack of data, we were often unable find non trivial
+results; This lack of data is exasperated by the fact that the
+conference of 2018 presents as an outlier in the dataset. Additionally,
+taking document clustering for instance as an example, network analysis
+of references were more accurate than(NLP) regarding documents and
+references clustering.
+
+We thus strongly recommend adding additional conferences to the dataset.
 \newpage

### 2019-01-11 Report/paper.tex
push paper

@@
 identifier, the authors email, its associated domain, order in which the
-author was cited, the institution, country, Longitude and Latitude were
+author was cited, the institution, country, longitude and latitude were
 saved to a csv file. We used the paper identifier and author order to
@@
 
-    \hypertarget{methodology-find-better-section-head..}{%
-\section{Methodology {[}find better section
-head..{]}}\label{methodology-find-better-section-head..}}
+    \hypertarget{methods-for-data-analysis}{%
+\section{Methods for Data Analysis}\label{methods-for-data-analysis}}
 

### 2019-01-11 Report/paper.tex
push my work
push report

@@
     From the pdf parser some of the documents were corrupted with some weird
-caracters such as , white space strings
+characters such as , white space strings
 
@@
 \item
-  We use \textbf{\emph{beautiful soup}} and \textbf{\emph{string}}
+  We used \textbf{\emph{beautiful soup}} and \textbf{\emph{string}}
   libraries to only keep the text that we needed without any special
@@
 \item
-  we apply \textbf{\emph{regular expression}} to remove numbers because
-  we thought that numbers were not that important.
+  we applied \textbf{\emph{regular expression}} to remove numbers
+  because we thought that numbers were not that important.
 \item
@@
 \item
-  We remove the words that were connecting parts of a sentence rather
-  than showing subjects, objects or intent. For us these words were not
-  that important and were only going to increase the bag of words length
+  We removed the words that were connecting parts of a sentence rather
+  than showing subjects, objects or intent (\textbf{\emph{stopwords}}).
+  For us these words were not that important and were only going to
+  increase the bag of words length
 \item
@@
 derived words to their word stem, base or root form---generally a
-written word form As the use of the stop words to reduce the BOW (bag of
-words size we also used lemmatization and stemming to be able to reduce
-the number of words without taking off any information)
+written word form.
+
+As the use of the stop words to reduce the BOW (bag of words size) we
+also used lemmatization and stemming to be able to reduce the number of
+words without taking off any valuable information.
 
@@
 \textbf{\emph{Stemming}} were only used with \textbf{\emph{TF-IDF}}
-while doing the Keywords extraction, otherwise we prefer keeping the
-words as they are because we are doing a mapping with a pretrained
-stanford word embedding and we do not want to loose interpretability.
-
-    For the Keywords extraction we use three methods :
-
-The first one whe is a trivial one is to search in the pdf itself for
+while doing the Keywords extraction, otherwise we prefered keeping the
+words as they were because we were doing a mapping with a pretrained
+stanford word embedding and sometimes root forms were not in the
+dictionnary of words of the pre-trained words-vectors.
+
+    For the Keywords extraction we used three methods :
+
+The first one is a trivial one is to search in the pdf itself for
 keywords and extract them, this method is the most accurate but we found
@@
   to adjust for the fact that some words appear more frequently in
-  general \cite{Tf-idf}
+  general \cite{Tf-idf}.
 \end{itemize}
@@
     With TF-IDF we sorted for each document the words with the highest score
-and then selected the the 7 first words for each document.
+and then selected the the 7 first words of each document.
 
@@
   boundaries. This helps generate candidates that consist of one or more
-  non-stopwords. However ,it won't work in cases where the stopword is
+  non-stopwords. However, it won't work in cases where the stopword is
   part of the phrase. For example, `new' is listed in RAKE's stopword
@@
 \item
-  The last step is ranking the scores ansd selecting the ones with the
+  The last step is ranking the scores and selecting the ones with the
   highest score
@@
     Once we have all the keywords from the three methods, we try to select
-the most accurate keywords. So we create a method that selects the
+the most accurate keywords. So we created a method that selects the
 intersection of TF-IDF keywords and the Rake keywords with the keywords
@@
 intersection is empty and we have the keywords in the text we only take
-the keywords of the text. If we don't have any keywords we take the
-intersection of the TF-IDF and the Rake. If again, the intersection is
-empty then we only take the TF-IDF keywords because they were closer to
-the text keywords than the Rake Keywords.
+the keywords of the text. If the paper does not have keywords, we take
+the intersection of the TF-IDF and the Rake. If again, the intersection
+is empty then we only take the TF-IDF keywords because they were closer
+to the text keywords than the Rake Keywords.
 
@@
 to scale over the years and use the percentage of appearence of a word.
-So after groupping the words by year and scaling them we found graph
-below \ref{fig1}
+So after groupping the words by year and scaling them we found the graph
+below \ref{fig1}.
 
@@
 
-With the natural langage processing, we start with a naive method which
-consists of clustering the documents using only TF-IDF. Each document
-has a vector representation with values for each word present in the
-document depending on the frequency of the word in this document
+With the natural langage processing, we started with a naive method
+which consists of clustering the documents using only TF-IDF. Each
+document has a vector representation with values for each word present
+in the document depending on the frequency of the word in this document
 regarding its frequency in all the other documents. So if a word is a
@@
 more important than the other words in the vector of the document. Once
-we have our vector representation, we select the max features parameter
-as 2500, it means that we will only consider the top max\_features
-ordered by term frequency across the corpus. On this word representation
-we run K-means.
+we obtained our vector representation, we selected the max features
+parameter as 2500, it means that we only considered the top
+max\_features ordered by term frequency across the corpus. On this word
+representation we run K-means.
 
@@
 
-This method does not give good results as we can see it in the graph
-below \ref{fig3} all the vectors are together there is no clear
+This method did not give good results as we can see it in the graph
+below \ref{fig3}. All the vectors are together there is no clear
 separation between the documents. So we decide to use other methods
-using word embeddings and properties of TF-IDF.
+using words embeddings and properties of TF-IDF.
 
@@
 interesting linear substructures of the word vector space. It is
-developed as an open-source project at Stanford.\cite{GloVe}
-
-We construct a dictionnary from the words embeddings mapping each word
-of a document to its vector representation, than we average all the
+developed as an open-source project at Stanford.\cite{GloVe} The goal of
+GloVe is to group words with similar meaning together in a new vector
+space.
+
+We constructed a dictionnary from the words embeddings mapping each word
+of a document to its vector representation, than we averaged all the
 vectors of each document. Since each words has its representation in
@@
 
-Once we get a document vector representation, we apply to it K-means.
-The results are better, but we have only two clusters. If we increase
-the number of clusters than there is no clear separation anymore
-separation. The plot below \ref{fig4} reprensents the documents
-belonging to each cluster.
+Once we obtained a document vector representation, we applied to it
+K-means. The results were slightly better, but we had only two clear
+separate clusters. If we increase the number of clusters than there is
+no clear separation anymore. The plot below \ref{fig4} reprensents the
+documents belonging to each cluster.
 
@@
 TF-IDF vector, we took all the vocabulary generated by all the documents
-and we created a method that sorts the document frequency vector, take
-the 500 first words and do a weighted average of the words embedding
-vectors with the TF-IDF score.
-
-Once we get the weighted average vector, and since we are using a words
-embedding of 50 dimentions. We decide to use feature reduction technique
-to reduce the number of dimensions and represent our vectors in an other
-vector space where all the features are orthogonal to each others.
+and we created a method that sorts the document frequency vector. We
+selected the 500 first words and did a weighted average of the words
+embedding vectors with the TF-IDF score.
+
+Once we get the weighted average vector, and since we were using a words
+embedding of 50 dimentions. We decided to use feature reduction
+technique to reduce the number of dimensions and represent our vectors
+in an other vector space where all the features are orthogonal to each
+others.
 
@@
 into a set of values of linearly uncorrelated variables called principal
-components. If there are \textbf{\emph{n}} observations with ****p****
-variables, then the number of distinct principal components is
-\textbf{\emph{min(n-1,p)}}. This transformation is defined in such a way
-that the first principal component has the largest possible variance
-(that is, accounts for as much of the variability in the data as
-possible), and each succeeding component in turn has the highest
-variance possible under the constraint that it is orthogonal to the
-preceding components. The resulting vectors (each being a linear
+components. If there are \textbf{\emph{n}} observations with
+\textbf{\emph{p}} variables, then the number of distinct principal
+components is \textbf{\emph{min(n-1,p)}}. This transformation is defined
+in such a way that the first principal component has the largest
+possible variance (that is, accounts for as much of the variability in
+the data as possible), and each succeeding component in turn has the
+highest variance possible under the constraint that it is orthogonal to
+the preceding components. The resulting vectors (each being a linear
 combination of the variables and containing n observations) are an
-uncorrelated orthogonal basis set. PCA is sensitive to the relative
-scaling of the original variables \cite{PCA}.
-
-Once we get our new vector representation, we apply K-means and we get
-the best separation, with a clear separation of 4 clusters as we can see
-it in the figure below \ref{fig5}.
+uncorrelated orthogonal basis set. \cite{PCA}.
+
+Once we get our new vector representation, we applied K-means and we
+obtained the best separation, with a clear separation of 4 clusters as
+we can see it in the figure below \ref{fig5}.
 
@@
 
-For the references graph we choose to construct 4 different graphs to be
+For the references graph we chose to construct 4 different graphs to be
 able to extract the more information we can. Our first purpose is to be
-able to cluster the documents that are about the same subject.
+able to cluster the documents that are about the same subject and to
+gain more insights about the most influencial papers, trends of
+citations\ldots{}
 
@@
 Our first graph is constructed using the references of each document. It
-is constructed as follow, for each two documents, if there is an
+is constructed as follows, for each two documents, if there is an
 intersection between the references of both documents then there is a
 link. The weights of the edges are the length of the intersection set.
-The intuition behind is that the more the weight is high, the more the
-documents are likely to be about the same subject since they are citing
-the same documents. From this graph, we create a subgraph of it, we
-filter the edges keeping only those who have a weight strictly higher
+The intuition behind it, is that the more the weight is high, the more
+the documents are likely to be about the same subject since they are
+citing the same documents. From this graph, we create a subgraph of it,
+we filter the edges keeping only those who have a weight strictly higher
 than 3. It means that, each node of the subgraph, is related to at least
@@
 link between the references of the document. We create a dictionnary of
-links, if the link is already in the dictionnary then we increase the
-weight of the link. So for instance, if two references are present
-together in the 5 distinct documents, then the weight of the edge would
-be of 5. We obtain a graph of 10845 nodes and 148594 edges but we
-filtered the edges that have a weight higher than 4 and we get the graph
-below represented in this figure \ref{fig6}
+links, for each new document, if two references of this latter have
+already a link in the dictionnary then we increase the weight of the
+link.
+
+So for instance, if two references are present together in the 5
+distinct documents, then the weight of the edge would be of 5. We obtain
+a graph of 10845 nodes and 148594 edges but we filtered the edges that
+have a weight higher than 4 and we get the graph below represented in
+this figure \ref{fig6}
 
@@
 \hypertarget{graph-construction}{%
-\subsubsection{Graph Construction:}\label{graph-construction}}
+\subsubsection{Graph Construction}\label{graph-construction}}
 
@@
 more sparse and contained much fewer authors. Additionally all connected
-components contained fewer than 50 authors, making it possible to
+components contained fewer than 35 authors, making it possible to
 consider each author individually. Such a component is shown in figure
@@
     A second alternative approach was to consider the strength of bounds. In
-the graph authors are only linked if they have written at least 2 papers
-together. This method yielded a much larger component --containing 441
-authors-- as this second condition was weaker. To get an understanding
-of author to author relations in this component we needed to further
-prune away parts of the graph that are not insightful. When we looked at
-individual author within the community, we were interested in
-collaborative individuals. Hence we removed nodes that had collaborated
-with fewer than 3 connections to other authors. The resulting graph can
-be seen in figure \ref{author_collab_large}. Details creating such a
-plot can be found in the section dedicated to this below.
+this graph authors are only linked if they have written at least 2
+papers together. This method yielded a much larger component
+--containing 441 authors-- as this second condition was weaker. To get
+an understanding of author to author relations in this component we
+needed to further prune away parts of the graph that are not insightful.
+When we looked at individual author within the community, we were
+interested in collaborative individuals. Hence we removed nodes that had
+fewer than 3 connections to other nodes. The resulting graph can be seen
+in figure \ref{author_collab_large}. Details creating such a plot can be
+found in the section dedicated to this below.
 
@@
 co-authorship graph. One should also consider the overall structure of
-the graph. As graph is not connected, and contains one large main
-component with 1141 authors and 208 very small components with less than
-25 authors in them we focused on analyzing the structure of the main
-component of the graph. First we aimed to detect sub-communities within
-the graph. Modularity is one measure used to find such communities. It
-measures the connection strength within a community relative to the
-strength of outgoing connections. Networks with high modularity have
-dense connections between the nodes within modules but sparse
-connections between nodes in different modules. A non-parametric
-algorithm for community detection is the Louvain Method
-\cite{blondel2008fast}. We used the implementation of Thomas Aynaud
-\cite{louvain}. This gives a good partitioning of the graph into 26
-communities of median size 42.84. This is quite a large number of
-communities, so we considered an alternative way to yield bigger
-partitions. An alternate way to find subcommunities is to look at
-normalized cuts, which partition the nodes into groups with many
-within-group connections and relatively few between-group connections.
-The advantage of this method is that we can choose how many cuts to
-make, and we are thus able to define the size of subcommunities. Finding
-normalized cuts in a graph can be done using \emph{sklearns} spectral
-clustering algorithm by passing it the adjacency matrix of the graph.
-With this method we are able to neatly separate the main component graph
-in three large communities. See figure \ref{normalized}
+the graph. As the co-authorship graph is not connected, and contains one
+large main component with 1141 authors and 208 very small components
+with less than 25 authors in them we focused on analyzing the structure
+of the main component of the graph. First we aimed to detect
+sub-communities within the graph. Modularity is one measure used to find
+such communities. It measures the connection strength within a community
+relative to the strength of outgoing connections. Networks with high
+modularity have dense connections between the nodes within the
+subcommunites but sparse connections between nodes in different
+subcommunites. A non-parametric algorithm for community detection is the
+Louvain Method \cite{blondel2008fast}. We used the implementation of
+Thomas Aynaud \cite{louvain}. This gives a good partitioning of the
+graph into 26 communities of median size 42.84. This is quite a large
+number of communities, so we considered an alternative way to yield
+bigger partitions. For this we looked at normalized cuts, which
+partition the nodes into groups with many within-group connections and
+relatively few between-group connections. The advantage of this method
+is that we can choose how many cuts to make, and we are thus able to
+define the size of subcommunities. Finding normalized cuts in a graph
+can be done using \emph{sklearns} spectral clustering algorithm by
+passing it the adjacency matrix of the graph. With this method we are
+able to neatly separate the main component graph in three large
+communities, as can be seen in figure \ref{normalized}
 
@@
 \subsubsection{Numerical analysis of
-graphs:}\label{numerical-analysis-of-graphs}}
+graphs}\label{numerical-analysis-of-graphs}}
 
@@
 \subsubsection{Plotting of co-authorship
-graphs:}\label{plotting-of-co-authorship-graphs}}
+graphs}\label{plotting-of-co-authorship-graphs}}
 
@@
 layouts of networkx. The force directed layout was used as it clusters
-together nodes with strong connections. Then the size of each node was
+together nodes with strong connections. As this layout is produced by
+iterations and based on random initial conditions, we set a fix random
+seed to be able to reproduce the positioning. The size of each node was
 changed based on the position of the node in the graph. Central nodes
@@
 number of connections in the graph. Betweenness centrality of a node is
-the sum of the fraction of all-pairs shortest paths that pass through
-it. Degree centrality is more appropriate for smaller graphs as their
-structure is still easy to interpret. As by construction betweenness
-takes into consideration the degrees of it neighboring nodes, it better
-structures the nodes large graphs into central and less central nodes.
+the sum of the fraction of all-pairs shortest paths that pass through it
+\ref{borgatti2014social}. We found that degree centrality is more
+appropriate for smaller graphs as their structure is still easy to
+interpret. As by construction betweenness takes into consideration the
+degrees of it neighboring nodes, it better structures the nodes large
+graphs into central and less central nodes.
 
@@
 
-We found that participants from 372 institutions participated over the
-last 4 years, with a median of 128 institutions per year. The number of
-institutions participating increased each year, with a noticeable peak
-in 2018, with participants from 261 institutions. This is a considerable
-increase from the last conference ICLS in 2016 which had 135
-participating institutions. Most participants are from the US, with a
-average of 50\% of all participants being from the US. We could also
-observe a trend of increase in US participants with only 35\% of US
-participants in 2015 and 51\% in 2017, followed by 64\% in 2018.
-Overall, participants from 41 nations have participated over the 4
-years, with an average of 28 nations represented at each conference.
-After the US, participants of Germany, Canada and Singapore make up the
-biggest proportion of participants \ref{fig_rep}.
+Participants from 372 institutions participated over the last 4 years,
+with a median of 128 institutions per year. The number of institutions
+participating increased each year, with a noticeable peak in 2018, with
+participants from 261 institutions. This is a considerable increase from
+the last conference ICLS in 2016 which had 135 participating
+institutions. Most participants are from the US, with a average of 50\%
+of all participants being from the US. We could also observe a trend of
+increase in US participants with only 35\% of US participants in 2015
+and 51\% in 2017, followed by 64\% in 2018. Overall, participants from
+41 nations have participated over the 4 years, with an average of 28
+nations represented at each conference. After the US, participants of
+Germany, Canada and Singapore make up the biggest proportion of
+participants \ref{figrep}.
 
@@
 collaborations. Out of these 153, 108 involved at least one U.S.
-participant. Excluding U.S. participation we find figure
-\ref{figcollab}. We note that some countries, such as Japan, are not
-present in this graph. This means that all international collaboration
-of these countries, in this case japanese authors, also involves
-American authors. Additionally we observed that many asian nations seem
-to collaborate almost exclusively with each other or Canada.
+participant. Excluding US participation we find the collaboration graph
+presented in figure \ref{figcollab}. We note that some countries, such
+as Japan, are not present in this graph. This means that all
+international collaboration of these countries, in this case japanese
+authors, also involves American authors. Additionally we observed that
+many Asian nations seem to collaborate almost exclusively with each
+other or Canada.
 
@@
         \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_66_0.png}\end{center}
-        \caption{Collaborative papers between countries}
+        \caption{Collaborative papers between countries excluding US}
         \label{figcollab}
@@
 repeat collaboration during different years is sparse, containing
-connected components of size at most 25, we deduce that repeat
+connected components of size at most 31, we deduce that repeat
 collaboration over the years is rather infrequent. As the graph
-conditioned on multiple collaboration is more dense (having a component
-of the size 400), we deduce that when multiple collaborations with the
-same authors happen, they yield work submitted at the same time.
+conditioned on multiple collaboration is more dense (having a connected
+component with more than 400 authors), we deduce that when multiple
+collaborations with the same authors happen, they yield work submitted
+at the same time.
 
@@
 based on collaboration in these conferences. However, the analysis of
-nationalities present in the graph yield an interessting results. All
+nationalities present in the graph yielded an interessting results. All
 Asian participants from nations other than Singapore are contained in
@@
 changed moved countries and 47 that have moved institutions. We can see
-that most movement occured within the US respectively Europe,
+that most movement occured within the US respectively Europe, see figure
 \ref{fig_move}.
@@
 Learning Sciences community is investigating more and more tools to
-facilitate learning over the years.
+facilitate the learning over the years.
 
@@
 citation graph that we constructed (graph3) before. We filtered the
-first 100 documents and then contructed a histogram of the counts. We
-obtain the figure \ref{fig7}:
+first 100 documents and then contructed a histogram of the counts by
+year. We obtain the figure \ref{fig7}:
 
@@
 we can say is that more than 50\% of the most cited documents are from
-2006 until 2016, we is 10 years. The other half is between 1977 until
+2006 until 2016, which is 10 years. The other half is between 1977 until
 2005 which represents more than 25 years. On top of that, 2016 is the
@@
 about the same subject From the table \ref{fig8} we can also notice that
-some papers cites like to cite the same authors together, which is logic
-in a sense, because if some authors always treat about the same subjects
-then they are experts in that field and a lot of their publications are
-relevant and can be cited together.
+some papers are more likely to cite distinct publications of the same
+author, which is logic in a sense, because if some authors always treat
+about the same subject then they are experts in that field and a lot of
+their publications are relevant and can be cited together.
 
@@
 more likely to be about the same subjects. We can visualise one cluster,
-the most important one.
+the most important one in figure \ref{fig12}.
 

### 2019-01-11 Report/paper.tex
push paper and figures

@@
 \begin{abstract}
-    In this report we explore ways to automatically analyze ICLS and CSCL
-papers to gain an understanding of the community formed by conference
-participants and of the research being conducted within the community.
-After describing how to extract data from the base dataset we derive
-insights into the community using network analysis, natural language
-processing and text mining. We discover patterns of collaboration
-between participants, their migration and the global spread of the
-community. We extract keywords and find clusters of referenced papers
-and documents within the conferences.
+    In this report we investigate ways to automatically analyze ICLS and
+CSCL papers to gain an understanding of the community formed by
+conference participants and of the research being conducted within the
+community. After describing how to extract data from the base dataset we
+derive insights into the community using network analysis, natural
+language processing and text mining. We discover patterns of
+collaboration between participants, their migration and the global
+spread of the community. We extract keywords and find clusters of
+referenced papers and documents within the conferences.
 \end{abstract}
@@
 \item
-  Trends inregards to citated papers and the evolution of their
+  Trends in regards to cited papers and the evolution of their
   prevalence from 1977 until 2018
 \item
-  Discovering clusters of the cited documents
-\item
-  Discovering clusters of the papers written within the conferences
+  Clusters of the cited documents
+\item
+  Clusters of the papers written within the conferences
 \end{itemize}
@@
 well as associated metadata in \emph{xml} format. To extract information
-from the dataset we first converted the data to a format that is more
-adapt to the task of data analysis and more compatible with a variety of
-external libraries. We stored all the resulting data in \emph{csv}
+from the dataset we first converted the data to a format that is better
+adapted to the task of data analysis and more compatible with a variety
+of external libraries. We stored all the resulting data in \emph{csv}
 format, as csv is a human readable format and can easily be processed by
@@
 in the xml file. Each author is associated to one line in the xml file.
-From the associated citation string we add to the first part of the
-citation containing the author names, year and title. This is later used
-to identify the paper when it is referenced in an other paper. Then we
-add a shortened version of author names (i.e.~West, R.) by considering
-the author order. Note that it happens that the short name extracted
-from the citation and the corresponding long name (Robert West) in the
-metadata do not match up. Thus the author order listed in the citation
-string does not always correspond to the author order listed in the
-metadata. After extraction, we cleaned the data by unifying names, as
-slight spelling differences exist within the same author name
-(i.e.~Robert West, Robert A. West). When unifying the names we needed to
-make sure not to overmerge by labeling two different authors as having
-the same name. First, we used a strict condition to catch small
-differences in names, such as an extra middle name. This is done by
-splitting up names into substrings based on whitespaces and commas. For
-two names in the dataset we checked whether the intersection of their
-sets of substrings contained at least 2 names of length at least 3. If
-the condition was met we considered these two names to be identical, and
-added the mapping from one name to the other to a dictionary. Once all
-tuples of names (s.t. the first name appears before the second one in
-order) were checked and added to the dictionary we unified the names.
-Using this method we reduced the number of authors in the dataset from
-1951 down to 1879. Further, to merge names with misspellings or people
-who use nicknames (Christian vs Chris) and to avoid overmerging we
-considered only names of authors that have similar collaboration
-patterns. To do this we built a graph based on co-authors relations and
-checked names of authors that were in the same neighborhood of a node on
-the graph (see methodology for further details). Then, we used the
-\emph{difflib} library to check for similarity of two strings and
-considered a name to belong to the same person if the similarity measure
-reached the threshold of 0.8. Again names considered to belong to the
-same person were added to the mapping dictionary which was then applied
-to all names. This method again reduced the number of authors in the
-dataset from 1879 to 1951.
+From the associated citation string we add the first part of the
+citation containing the author names, year, and title. This is later
+used to identify the paper when it is referenced in an other paper. Then
+we add a shortened version of author names (i.e.~West, R.) by
+considering the author order. Note that it happens that the short name
+extracted from the citation and the corresponding long name (Robert
+West) in the metadata do not match up. Thus the author order listed in
+the citation string does not always correspond to the author order
+listed in the metadata. After extraction, we cleaned the data by
+unifying names, as slight spelling differences exist within the same
+author name (i.e.~Robert West, Robert A. West). When unifying the names
+we needed to make sure not to overmerge by labeling two different
+authors as having the same name. First, we used a strict condition to
+catch small differences in names, such as an extra middle name. This is
+done by splitting up names into substrings based on whitespaces and
+commas. For two names in the dataset we checked whether the intersection
+of their sets of substrings contained at least 2 names of length at
+least 3. If the condition was met we considered these two names to be
+identical, and added the mapping from one name to the other to a
+dictionary. Once all tuples of names (s.t. the first name appears before
+the second one in order) were checked and added to the dictionary we
+unified the names. Using this method we reduced the number of authors in
+the dataset from 1951 down to 1879. Further, to merge names with
+misspellings or people who use nicknames (Christian vs Chris) and to
+avoid overmerging we considered only names of authors that have similar
+collaboration patterns. To do this we built a graph based on
+co-authorship relations and checked names of authors that were in the
+same neighborhood of a node on the graph (see methodology for further
+details). Then, we used the \emph{difflib} library to check the
+similarity of two strings and considered a name to belong to the same
+person if the similarity measure reached the threshold of 0.8. Again,
+names considered to belong to the same person were added to the mapping
+dictionary which was then applied to all names. This method again
+reduced the number of authors in the dataset from 1879 to 1851.
 
@@
 contained in the pdfs to \emph{txt} format. All methods describing how
-to extract data from the papers worked on the extracted \emph{txt}
-files. The characters contained in the \emph{txt} files were not all
-encoded uniformly, which means that characters that look the same to
-humans may be encoded in different ways. Hence, for many converting all
+to extract data from the papers worked on the extracted txt files. The
+characters contained in the txt files were not all encoded uniformly,
+which means that characters that look the same to humans may be encoded
+in different ways. Hence, for many applications we converted all
 characters to `Normal Form Composed' form.
@@
 as --unlike the re module-- this module allows to handle strings with
-non-ascii characters by having unicode expressions. As many authors have
-names containing non-ascii characters this is an important capability.
+non-ascii characters by allowing the use of unicode regular expressions.
+As many authors have names containing non-ascii characters this is an
+important capability.
 
 \textbf{To get the reference section for of a paper} we used a regular
-expressions to find the reference header and determine the sections end
-by checking for acknowledgements or appendix sections in the text file
-previously extracted using poppler. Then, to extract individual
-references we split the section into a list of substrings at each new
-line character and concatenated substrings back together if they
-satisfied a set of conditions. We found this method to be robust as it
-makes sure that all properly formatted references are separated.
+expressions to find the reference header and determine the end of the
+section by checking for acknowledgements or appendix sections in the
+text file previously extracted using poppler. Then, to extract
+individual references we split the section into a list of substrings at
+each new line character and concatenated substrings back together if
+they satisfied a set of conditions. We found this method to be robust as
+it makes sure that all properly formatted references are separated.
 
 \textbf{To unify substrings} we exploited the fact that APA references
-all have the same initial structure: \emph{Lastname F.M. (when
+all have the same underlying structure: \emph{Lastname F.M. (when
 published) Title which may contain colons and other non-alphabetic
@@
 the lines below them. Only then could we check whether a line contained
-a valid citation start. If it did not we merged it with the line above
+a valid citation start. If it did not, we merged it with the line above
 it. After this merging process we validated the returned reference split
@@
 their email address. Email addresses can easily be extracted from the
-header section using a regular expression. Then we used a
-domain-university mapping \cite{mapping} to map domains to institutions.
-The additional advantage of this method is that using the additional
-metadata associated to each university in the mapping, we also access
-information about the country of the university.
+header section using a regular expression. Then, the part of the email
+containing the university domain can be extracted using an other regular
+expression. After this we used a domain-university mapping
+\cite{mapping} to map domains to institutions. The additional advantage
+of this method is that using the additional metadata associated to each
+university in the mapping, we also access information about the country
+of the university.
 
@@
 association. We tagged the substring present in this section using a
-combination of \emph{named entity detection}, using the implementation
-provided by \emph{spacy}, simple string comparison matching of the names
-of authors and institutions we extracted from the metadata respectively
-from Approach 1 and tagging sections containing ``emails'' using regex ,
-to detect where in the header the email is. Then, taking the tagged
-section, we detected which subsections corresponded to which
-author-affiliation listing type, and extracted the author email -
-institution mapping accordingly.
+combination of \emph{named entity detection}, which automatically
+classifies strings as belonging to some pre-defined category, using the
+implementation provided by \emph{spacy}\cite{spacy2}, and simple string
+comparison matching of the names of authors and institutions we
+extracted from the metadata respectively from Approach 1 and tagging
+sections containing ``emails'' using regex , to detect where in the
+header the email is. Then, taking the tagged section, we detected which
+subsections corresponded to which author-affiliation listing type, and
+extracted the author email - institution mapping accordingly.
 
 Approach 2 allows to match many more institutions to authors than
-Approach 1 as not every institution is present in the mapping --no
-companies will be in the mapping-- and many participants use gmail and
-similar providers as their official email. However, Approach 2 may
-contain differences in spelling in the institution name, which needed to
-be merged. Thus we combined both approaches, and used the corresponding
-institutions in Approach 1 to unify the institutions obtained in
-Approach 2. Furthermore, we later merged names by considering the
-location of the institutions.
-
-But first as with Approach 2 institution affiliation did not allow us to
-automatically associate a country to the institution, we needed to get
-this through other means. A first step was to use the top level domains
-present in the emails to associate a country of origin to the
-participants and their associated institutions. Then, to plot the
+Approach 1 as not every institution is present in the mapping and many
+participants use gmail and similar providers as their official email.
+However, Approach 2 may contain differences in spelling in the
+institution name, which needed to be unified. Thus we combined both
+approaches, and used the corresponding institutions in Approach 1 to
+unify the institutions obtained in Approach 2. Furthermore, we later
+merged names by considering the location of the institutions.
+
+But first, as with Approach 2 institution affiliation did not allow us
+to automatically associate a country to the institution, we needed to
+get this information through other means. A first step was to use the
+top level domains present in the emails to associate a country of origin
+to the participants and their associated institutions. Then, to plot the
 community we augmented the dataset with geolocation information. As a
 further benefit, having this information we could then easily associate
-a country to the institution for the emails that do not have a top level
-domain indicating location and further merge the names of institutions
-based on location.
+a country to the institution for the emails that ido not have a top
+level domain indicating location and further merge the names of
+institutions based on location.
 
@@
 using the API is due to the website redirecting to the relevant article
-on the institution even when misspellings are present. Requests were
-sent using \emph{urllib3} and \emph{beautifulsoup} was used to parse
-them get the coordinates present in the article. Regretfully not all
-institutions, even well known ones such as Tokyo University, have their
-coordinates listed on Wikipedia. To get the remaining locations we used
-the geopy, which is a client for geocoding web services. These results
-however are more error prone and will always return a result. It is thus
-recommended to verify the correctness of the results. To get the country
-we then again used geopy. The resulting data containing paper
-identifier, the authors email, its associated domain, order in which the
-author was cited, the institution, country, longitude and latitude were
-saved to a csv file. We used the paper identifier and author order to
-associate this data with the metadata to link information about authors
-with the papers they authored.
-
-    \hypertarget{keywords-extraction}{%
-\subsection{Keywords extraction}\label{keywords-extraction}}
+on the institution even when misspellings are present or multiple ways
+to spell the university exist. Requests were sent using \emph{urllib3},
+and \emph{beautifulsoup} was used to parse them get the coordinates
+present in the article. Regretfully not all institutions, even well
+known ones such as Tokyo University, have their coordinates listed on
+Wikipedia. To get the remaining locations we used geopy, which is a
+python client for geocoding web services. These results however are more
+error prone as geopy will always return a result. It is thus recommended
+to verify the correctness of the results. To get the country we then
+again used geopy. The resulting data containing paper identifier, the
+authors email, its associated domain, order in which the author was
+cited, the institution, country, longitude and latitude were saved to a
+csv file. We used the paper identifier and author order to associate
+this data with the metadata to link information about authors with the
+papers they authored.
+
+    \hypertarget{keyword-extraction}{%
+\subsection{Keyword extraction}\label{keyword-extraction}}
 
@@
 
-    From the pdf parser some of the documents were corrupted with some weird
-characters such as , white space strings
+    The pdf parser returns txt files that are encoded using a variety of
+conventions, thus when extracting the strings from the text files, we
+were met with non-ascii characters, which had to be dealt with. We
+preprocessed the text by applying the following steps to it:
 
@@
 \item
-  We used \textbf{\emph{beautiful soup}} and \textbf{\emph{string}}
-  libraries to only keep the text that we needed without any special
-  character.
-\item
-  we applied \textbf{\emph{regular expression}} to remove numbers
-  because we thought that numbers were not that important.
-\item
-  We put all the words to lower cases
-\item
-  We removed the words that were connecting parts of a sentence rather
-  than showing subjects, objects or intent (\textbf{\emph{stopwords}}).
-  For us these words were not that important and were only going to
-  increase the bag of words length
-\item
-  In some methods we use \textbf{\emph{Lemmatization}} and
-  \textbf{\emph{stemming}} and in other methods we don't because we
-  wanted to do a mapping with \textbf{\emph{GloVe}} vocabulary which we
-  will explain later on.
+  We used \emph{beautiful soup} and \emph{string} libraries to only keep
+  sections of the text that we needed and remove special characters.
+\item
+  We applied \textbf{\emph{regular expression}} to remove numbers
+  because numbers were not important for our analysis.
+\item
+  We put all words to lower case
+\item
+  We removed words that were connecting parts of a sentence rather than
+  showing subjects, objects or intent (\textbf{\emph{stopwords}}). For
+  the purpose of this task these words were not important and were only
+  going to increase the bag of words length
+\item
+  In some methods we applied \textbf{\emph{lemmatization}} and
+  \textbf{\emph{stemming}} to the words. In other methods we did not
+  because we implement a mapping with \textbf{\emph{GloVe}} vocabulary
+  instead, which we will explain later on.
 \end{itemize}
@@
 derived words to their word stem, base or root form---generally a
-written word form.
-
-As the use of the stop words to reduce the BOW (bag of words size) we
-also used lemmatization and stemming to be able to reduce the number of
-words without taking off any valuable information.
-
-    \textbf{\emph{Lemmatization}} and different form of
+written word form. As the use of the stop words to reduce the BOW (bag
+of words) size we also used lemmatization and stemming to be able to
+reduce the number of words without taking off any valuable information.
+
+\textbf{\emph{Lemmatization}} and different forms of
 \textbf{\emph{Stemming}} were only used with \textbf{\emph{TF-IDF}}
@@
 words as they were because we were doing a mapping with a pretrained
-stanford word embedding and sometimes root forms were not in the
-dictionnary of words of the pre-trained words-vectors.
-
-    For the Keywords extraction we used three methods :
-
-The first one is a trivial one is to search in the pdf itself for
+Stanford Word Embedding \cite{GloVe_web} and sometimes root forms were
+not in the dictionnary of words of the pre-trained words-vectors.
+
+For the Keywords extraction we used three methods : The first one is a
+trivial approach that consists of searching in the pdf itself for
 keywords and extract them, this method is the most accurate but we found
 out that for 492 papers we had no keywords included. So we deciced to
-use two methods for keywords extraction. The first one is
-\textbf{\emph{TF-IDF}} and the second one is \textbf{\emph{Rake}}.
-
-    \begin{itemize}
-\tightlist
-\item
-  \textbf{\emph{TF-IDF}}: Tf--idf is one of the most popular
-  term-weighting schemes today, in information retrieval, tf--idf or
-  TFIDF, short for term frequency--inverse document frequency, is a
-  numerical statistic that is intended to reflect how important a word
-  is to a document in a collection or corpus. It is often used as a
-  weighting factor in searches of information retrieval, text mining,
-  and user modeling. The tf--idf value increases proportionally to the
-  number of times a word appears in the document and is offset by the
-  number of documents in the corpus that contain the word, which helps
-  to adjust for the fact that some words appear more frequently in
-  general \cite{Tf-idf}.
-\end{itemize}
-
-    With TF-IDF we sorted for each document the words with the highest score
-and then selected the the 7 first words of each document.
-
-    \begin{itemize}
-\tightlist
-\item
+use other two methods for keywords extraction, namely one based on
+\textbf{\emph{TF-IDF}} and a second one based on \textbf{\emph{Rake}}.
+\textbf{\emph{TF-IDF}} is one of the most popular term-weighting schemes
+today, in information retrieval, tf--idf or TFIDF, short for term
+frequency--inverse document frequency, is a numerical statistic that is
+intended to reflect how important a word is to a document in a
+collection or corpus. It is often used as a weighting factor in searches
+of information retrieval, text mining, and user modeling. The tf--idf
+value increases proportionally to the number of times a word appears in
+the document and is offset by the number of documents in the corpus that
+contain the word, which helps to adjust for the fact that some words
+appear more frequently in general \cite{Tf-idf}. With TF-IDF we sorted
+for each document the words with the highest score and then selected the
+7 first words of each document.
+
     \textbf{\emph{Rake}}: Rake stands for Rapid Automatic Keyword
@@
 toolkit for the score calculations.
-\end{itemize}
-
-\textbf{\emph{How it works}} :
+
+\textbf{\emph{How the method works}} :
 
@@
 
-    Once we have all the keywords from the three methods, we try to select
-the most accurate keywords. So we created a method that selects the
+Once we have all the keywords from the three methods, we tried to select
+the most accurate keywords. So we created a method that selected the
 intersection of TF-IDF keywords and the Rake keywords with the keywords
@@
 intersection is empty and we have the keywords in the text we only take
-the keywords of the text. If the paper does not have keywords, we take
-the intersection of the TF-IDF and the Rake. If again, the intersection
-is empty then we only take the TF-IDF keywords because they were closer
-to the text keywords than the Rake Keywords.
+the keywords of the text. If the paper does not contain any keywords, we
+take the intersection of the TF-IDF and the Rake outputs. If again, the
+intersection is empty then we only take the TF-IDF keywords because they
+were closer to the text keywords than the Rake Keywords.
 
@@
     \begin{figure}
-        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_27_0.png}\end{center}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_21_0.png}\end{center}
         \caption{Trends of keywords over the years}
@@
     We wanted then to know what are the trends of words for each specific
-year, so we select distinct words for each year. On other words it means
-that we select for each year the words that were only present for this
-specific year and never appeared in the others. We get the figure below.
-As we can see from the graph \ref{fig2}, the most used word in the
-papers, more than 10\% of 2015 papers uses the word `peer', more than
-6\% of the papers uses the words `building', `embodied' in 2016. In 2017
-the most frequent keyword on is `reponsive' and in 2018 `tools' is
-present with more than 6\%.
-
-    \begin{figure}
-        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_29_0.png}\end{center}
+year, so we selected distinct words for each year. In other words it
+means that we selected for each year the words that were only present
+for this specific year and never appeared in the others. We get the
+figure below. As we can see from the graph \ref{fig2}, the most used
+word in the papers, more than 10\% of 2015 papers used the word `peer',
+more than 6\% of the papers used the words `building', `embodied' in
+2016. In 2017 the most frequent keyword is `reponsive' and in 2018
+`tools' is present with more than 6\%.
+
+    \begin{figure}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_23_0.png}\end{center}
         \caption{Distinct keywords over the years}
@@
 To cluster the documents we decided to use two different approaches. The
-first one is Natural Langage Processing (NLP) and the second one is a
-network analysis. The most accurate one is the network clustering using
-the references graph.
+first one is based on Natural Langage Processing (NLP) and the second
+one is rooted in network analysis. We fin that network clustering using
+the references graph is most accurate.
 
@@
 
-\hypertarget{baseline-tf-idf-combined-with-k-means}{%
-\paragraph{Baseline : TF-IDF combined with
-K-means}\label{baseline-tf-idf-combined-with-k-means}}
+\hypertarget{baseline---tf-idf-combined-with-k-means}{%
+\paragraph{Baseline - TF-IDF combined with
+K-means}\label{baseline---tf-idf-combined-with-k-means}}
 
 With the natural langage processing, we started with a naive method
-which consists of clustering the documents using only TF-IDF. Each
+which consisted of clustering the documents using only TF-IDF. Each
 document has a vector representation with values for each word present
@@
 a set of observations into a number of clusters (k), resulting in the
-partitioning of the data into Voronoi cells. It can be considered a
+partitioning of the data into Voronoi cells. It can be considered as a
 method of finding out which group a certain object really belongs to.
@@
 separation between the documents. So we decide to use other methods
-using words embeddings and properties of TF-IDF.
-
-    \begin{figure}
-        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_32_0.png}\end{center}
+using words embeddings combined with properties of TF-IDF.
+
+    \begin{figure}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_26_0.png}\end{center}
         \caption{Baseline model document clusters}
@@
 The second method was to use pre-trained words embeddings. We decided to
-use \textbf{\emph{GloVe}} library pre-trained on Wikipedia dataset.
+use \emph{GloVe} library pre-trained on Wikipedia dataset.
 
@@
 We constructed a dictionnary from the words embeddings mapping each word
-of a document to its vector representation, than we averaged all the
-vectors of each document. Since each words has its representation in
+of a document to its vector representation, then we averaged all the
+vectors of each document. Since each words has its own representation in
 space, the average of all the words for each document will lead to a
@@
 
-Once we obtained a document vector representation, we applied to it
-K-means. The results were slightly better, but we had only two clear
-separate clusters. If we increase the number of clusters than there is
-no clear separation anymore. The plot below \ref{fig4} reprensents the
-documents belonging to each cluster.
-
-    \begin{figure}
-        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_34_0.png}\end{center}
+Once we obtained a document vector representation, we applied K-means to
+it. The results were slightly better, but we had only two clear
+separated clusters. If we increase the number of clusters, then there is
+no clear separation between clusters visible anymore. The plot in figure
+\ref{fig4} reprensents the documents belonging to each cluster.
+
+    \begin{figure}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_28_0.png}\end{center}
         \caption{Cluster using Average of GloVe vectors combined with K-means }
@@
 and we created a method that sorts the document frequency vector. We
-selected the 500 first words and did a weighted average of the words
-embedding vectors with the TF-IDF score.
-
-Once we get the weighted average vector, and since we were using a words
-embedding of 50 dimentions. We decided to use feature reduction
+selected the 500 first words and computed a weighted average of the
+every word embedding vector with the its respectively TF-IDF score.
+
+Once we get the weighted average vector, since we were using a words
+embedding of 50 dimentions, we decided to use feature reduction
 technique to reduce the number of dimensions and represent our vectors
@@
 
-To apply the feature reduction to our vectors we used
+To apply feature reduction to our vectors we used
 \textbf{\emph{Principal Component Analysis (PCA)}} algorithm.
@@
 obtained the best separation, with a clear separation of 4 clusters as
-we can see it in the figure below \ref{fig5}.
-
-    \begin{figure}
-        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_36_0.png}\end{center}
+we can see it in figure \ref{fig5}.
+
+    \begin{figure}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_30_0.png}\end{center}
         \caption{Cluster using Weighted average of TF-IDF + GloVe  combined with K-means }
-        \label{fig}
+        \label{fig5}
     \end{figure}
@@
 For the references graph we chose to construct 4 different graphs to be
-able to extract the more information we can. Our first purpose is to be
-able to cluster the documents that are about the same subject and to
-gain more insights about the most influencial papers, trends of
-citations\ldots{}
+able to extract as much information as possible. Firstly, to be able to
+cluster the documents that are about the same subject and secondly to
+gain more insights about the most influencial papers and trends of
+citations.
 
@@
 Our first graph is constructed using the references of each document. It
-is constructed as follows, for each two documents, if there is an
-intersection between the references of both documents then there is a
-link. The weights of the edges are the length of the intersection set.
-The intuition behind it, is that the more the weight is high, the more
-the documents are likely to be about the same subject since they are
-citing the same documents. From this graph, we create a subgraph of it,
-we filter the edges keeping only those who have a weight strictly higher
-than 3. It means that, each node of the subgraph, is related to at least
-one other node with 4 same documents referenced.
-
-    The resulted graph is plotted in this figure \ref{intersection}, is an
-undirected graph with 805 nodes and 6699 edges. On this graph we extract
-two main information : * Strongly connected components to be able to
-detect clusters and related documents. * In\_degree in order to check if
-there are documents that are related to a lot of documents and those
-documents would be more general than others, and won't necessarly belong
-to one specific cluster.
-
-    \begin{figure}
-        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_42_0.png}\end{center}
+is constructed as follows: for each two documents, if there is an
+intersection between the references of both documents, then there is a
+link conneting the two documents. The weights of the edges are the
+length of the intersection set. The intuition behind it is that the
+higher the weight, the more the documents are likely to be about the
+same subject, since they are citing the same documents. From this graph,
+we create a subgraph of it. We filter the edges keeping only those who
+have a weight strictly higher than 3. This means that, each node of the
+subgraph, is related to at least one other node with 4 same documents
+referenced.
+
+    The resulting graph, plotted in figure \ref{intersection}, is an
+undirected graph with 805 nodes and 6699 edges. On this graph we
+extracted two main features:
+
+\begin{itemize}
+\tightlist
+\item
+  Strongly connected components to be able to detect clusters and
+  related documents.
+\item
+  The in-degree in order to check if there are documents that are
+  related to a lot of documents and if those documents are more general
+  than others, and will not necessarly belong to one specific cluster.
+\end{itemize}
+
+    \begin{figure}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_36_0.png}\end{center}
         \caption{Intersection between references graph}
@@
 
-The second graph is more about the referenced documents and not about
-the documents themselves. The aim of this graph is to see if there are
-documents that are more likely to cited together. If it is the case,
-then these documents are likely to be about the same subject. It is a
-weighted graph constructed as follow: for each document, we create a
+The second graph relates more to the referenced documents and is not
+about the documents themselves. The aim of this graph is to see if there
+are documents that are more likely to be cited together. If this is the
+case, then these documents are likely to be about the same subject. This
+weighted graph is constructed as follows: for each document, we create a
 link between the references of the document. We create a dictionnary of
-links, for each new document, if two references of this latter have
+links, for each new document, if two references of the latter have
 already a link in the dictionnary then we increase the weight of the
-link.
-
-So for instance, if two references are present together in the 5
-distinct documents, then the weight of the edge would be of 5. We obtain
-a graph of 10845 nodes and 148594 edges but we filtered the edges that
-have a weight higher than 4 and we get the graph below represented in
-this figure \ref{fig6}
-
-    \begin{figure}
-        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_46_0.png}\end{center}
+link. For instance, if two references are present together in the 5
+distinct documents, then the weight of the edge would be of 5. We
+obtained a graph of 10845 nodes and 148594 edges but we filtered the
+edges that have a weight higher than 4 and we get the graph below
+represented in this figure \ref{fig6}
+
+    \begin{figure}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_40_0.png}\end{center}
         \caption{Relations between references filtered}
@@
 
-    We can directly select from the interactive graph the nodes with degree
-higher than 100, these nodes represent the more cited documents, but we
-will construct a subgraph to specificly tackle these important
+    We can directly select from the interactive graph, which can be found in
+the jupyter notebook corresponding to this report, the nodes with degree
+higher than 100. These nodes represent the most cited documents, but we
+will construct a subgraph to specificly tackle the most important
 referenced documents. On this graph, to be able to detect similar
-documents we also run Strongly connected components algorithm. On top of
-it, we inspected the documents with higher weights, we will explain more
-about what we extracted from this graph in the result section.
+documents we also run the Strongly connected components algorithm. On
+top of this, we inspected the documents with higher weights. We will
+explain more about what we extracted from this graph in the result
+section.
 
     \hypertarget{third-graph-exploratory-references-graph}{%
-\paragraph{Third graph: exploratory references
+\paragraph{Third graph: Exploratory references
 graph}\label{third-graph-exploratory-references-graph}}
 
-With this graph we aim to find what are the most cited documents, what
-are the documents that are the most influencial and how citations evolve
-over time.
-
-This is a directed graph constructed in this way. For each document, if
-the document cites another document than there is a link between the
+With this graph we aimed to find the most cited documents, the documents
+that are the most influencial and how citations evolve over time. This
+is a directed graph constructed in the following way: for each document,
+if the document cites another document, then there is a link between the
 document and the cited one. We get a graph of 11650 nodes and 13243
-egdes. We also construct a subgraph of this graph, which is a
-co-citations in conferences, but because a lack of data, we find only
-three documents that cites other documents.
+egdes. We also constructed a subgraph of this graph, which is a
+co-citations in conferences, but do to a lack of data, we found only
+three documents that were cited by other documents.
 
@@
 
-\textbf{PageRank (PR)}* is an algorithm used by Google Search to rank
-web pages in their search engine results. In our case, It measure
-PageRank is a way of measuring the importance of referenced papers.
-Compared to the in-degree analysis we get almost the same results since
-we have no out degree for almost every node.
+\textbf{PageRank (PR)}* is an algorithm originally used by Google Search
+to rank web pages in their search engine results. In our case, PageRank
+is a way of measuring the importance of referenced papers. Compared to
+the in-degree analysis we get almost the same results. This is because
+almost all nodes have a zero out degree.
 
@@
 name and institution of the author that is represented by a node-- to
-the nodes and edges of the graph.
+the nodes and edges of the graph. We also associate the number of
+collaborations between different parties to the graphs as the weight of
+the edge.
 
@@
 more than one conference. The graph produced by this approach was much
-more sparse and contained much fewer authors. Additionally all connected
-components contained fewer than 35 authors, making it possible to
-consider each author individually. Such a component is shown in figure
-\ref{fig_plot}.
-
-    \begin{figure}
-        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_52_0.png}\end{center}
+more sparse and contained much fewer authors. Additionally, all
+connected components contained fewer than 35 authors, making it possible
+to consider each author individually. Such a component is shown in
+figure \ref{fig_plot}.
+
+    \begin{figure}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_46_0.png}\end{center}
         \caption{One of the connected components of the co-authorship graph}
@@
 an understanding of author to author relations in this component we
-needed to further prune away parts of the graph that are not insightful.
-When we looked at individual author within the community, we were
-interested in collaborative individuals. Hence we removed nodes that had
-fewer than 3 connections to other nodes. The resulting graph can be seen
-in figure \ref{author_collab_large}. Details creating such a plot can be
-found in the section dedicated to this below.
-
-    \begin{figure}
-        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_54_0.png}\end{center}
+needed to further prune away parts of the graph that were not
+insightful. When we looked at individual author within the community, we
+were interested in collaborative individuals. Hence we removed nodes
+that had fewer than 3 connections to other nodes. The resulting graph
+can be seen in figure \ref{author_collab_large}. Details creating such a
+plot can be found in the section dedicated to this below.
+
+    \begin{figure}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_48_0.png}\end{center}
         \caption{Largest Component}
@@
     \begin{figure}
-        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_57_0.png}\end{center}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_51_0.png}\end{center}
         \caption{Different formats used to reference institution}
@@
 \item
-  Average clustering coefficient: Measure of how much the nodes in a
+  Average clustering coefficient: measure of how much the nodes in a
   graph tend to cluster together. Average over all clustering
@@
 the sum of the fraction of all-pairs shortest paths that pass through it
-\ref{borgatti2014social}. We found that degree centrality is more
+\cite{borgatti2014social}. We found that degree centrality is more
 appropriate for smaller graphs as their structure is still easy to
@@
 degrees of it neighboring nodes, it better structures the nodes large
-graphs into central and less central nodes.
+graphs into central and less central nodes. The width of the edge is
+based on the weight of the edge, which in turn reflects the number of
+collaboration between two nodes.
 
@@
 implementing a custom visualization using \emph{D3} was also
-contemplated. However, functions provided by plotly is most general and
-allows to easily build interactive figures, while not being as heavy as
-bookeh and holoviews. Additionally, it is the most well maintained. D3
-requires a running server to be viewed and has a hard time dealing with
-large graphs. To plot figures we created them in networkx to grab the
-positioning of the nodes. Then we passed this positioning to plotly to
-plot.
+contemplated. However, functionality provided by plotly is most general
+and allows to easily build interactive figures, while not being as heavy
+as bookeh and holoviews. Additionally, it is the most well maintained.
+D3 requires a running server to be viewed and has a hard time dealing
+with large graphs. To plot figures we created them in networkx to grab
+the positioning of the nodes. Then we passed this positioning to plotly
+to plot.
 
@@
 Bibliographic analysis.
+
+    \begin{figure}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_57_0.png}\end{center}
+        \caption{Global spread of community. Size of dot represent number of participants from each institution}
+        \label{global_com}
+    \end{figure}
 
@@
     \begin{figure}
-        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_64_0.png}\end{center}
-        \caption{Different formats used to reference institution}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_59_0.png}\end{center}
+        \caption{Number of Contributiors by coutry, excluding the US}
         \label{figrep}
@@
     \begin{figure}
-        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_66_0.png}\end{center}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_61_0.png}\end{center}
         \caption{Collaborative papers between countries excluding US}
@@
     \begin{figure}
-        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_68_0.png}\end{center}
-        \caption{Subcommunities via normalized cuts}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_63_0.png}\end{center}
+        \caption{Subcommunities via normalized cuts in largest component of co-authorship graph}
         \label{normalized}
@@
     \begin{figure}
-        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_69_0.png}\end{center}
-        \caption{Subcommunities by paricipation in CSCL. Blue: no participation in main compnents of CSCL. Red and Violate each mark participation in one of the two main components of CSCL}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_64_0.png}\end{center}
+        \caption{Subcommunities by paricipation in CSCL. Blue: no participation in main compnents of CSCL. Red and orange each mark participation in one of the two main components of CSCL}
         \label{CSCL_components}
@@
 based on collaboration in these conferences. However, the analysis of
-nationalities present in the graph yielded an interessting results. All
+nationalities present in the graph yielded an interesting results. All
 Asian participants from nations other than Singapore are contained in
-the same cluster. We also note that one of the CSCL clusters ins closer
-to the group of ICLS only participants than the other. Additionaly,
-through normaized splits, we find that the section of the normalized cut
-containing ICLS only authors is overwhelmingmly american.
+the same cluster. We also note that one of the CSCL clusters is closer
+to the group of ICLS-only participants than the other. Additionaly,
+through normalized splits, we find that the section of the normalized
+cut containing ICLS only authors is overwhelmingly american.
 
@@
     \begin{figure}
-        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_71_0.png}\end{center}
-        \caption{Keywords of the bottom community}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_66_0.png}\end{center}
+        \caption{Keywords of the blue Community}
         \label{c1}
@@
     \begin{figure}
-        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_72_0.png}\end{center}
-        \caption{Keywords of the middle community}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_67_0.png}\end{center}
+        \caption{Keywords of the red community}
         \label{c2}
@@
     \begin{figure}
-        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_73_0.png}\end{center}
-        \caption{Keywords of the top community}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_68_0.png}\end{center}
+        \caption{Keywords of the orange community}
         \label{c3}
@@
 years. Over the years of recording we find 14 participants that have
-changed moved countries and 47 that have moved institutions. We can see
-that most movement occured within the US respectively Europe, see figure
+changed countries and 47 that have moved institutions. We can see that
+most movement occured within the US respectively Europe, see figure
 \ref{fig_move}.
@@
     \begin{figure}
-        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_76_0.png}\end{center}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_71_0.png}\end{center}
         \caption{Movement of participants across institutions}
@@
 notice that throughouts the year each pick is higher than the older one,
-which can be explained by the fact that The International Society of the
+which can be explained by the fact that the International Society of the
 Learning Sciences community is investigating more and more tools to
@@
     \begin{figure}
-        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_79_0.png}\end{center}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_74_0.png}\end{center}
         \caption{Distribution of the number of referenced documents belonging to each year}
@@
 published is increasing too. Using Pagerank algorithm and the In-degree
-of each nodes to get the most influancial documents referenced of the
-citation graph that we constructed (graph3) before. We filtered the
+of each nodes to get the most influencial documents referenced of the
+exploratory citations graph that we constructed before. We filtered the
 first 100 documents and then contructed a histogram of the counts by
@@
     \begin{figure}
-        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_81_0.png}\end{center}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_76_0.png}\end{center}
         \caption{Distribution of the 100 most referenced documents belonging to each year}
@@
     \begin{figure}
-        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_84_0.png}\end{center}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_79_0.png}\end{center}
         \caption{In-degree count for each document}
@@
 likely to cited together. We can say that the more two documents are
-likely to cited together the more it is probable that both documents are
-about the same subject From the table \ref{fig8} we can also notice that
-some papers are more likely to cite distinct publications of the same
-author, which is logic in a sense, because if some authors always treat
-about the same subject then they are experts in that field and a lot of
-their publications are relevant and can be cited together.
-
-    \begin{figure}
-        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_86_0.png}\end{center}
+likely to be cited together the more it is probable that both documents
+are about the same subject. From the table \ref{fig8} we can also notice
+that some papers are more likely to cite distinct publications of the
+same author, which is logic in a sense, because if some authors always
+treat about the same subject then they are experts in that field and a
+lot of their publications are relevant and can be cited together.
+
+    \begin{figure}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_81_0.png}\end{center}
         \caption{Count of documents cited together}
@@
     \begin{figure}
-        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_89_0.png}\end{center}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_83_0.png}\end{center}
         \caption{Table of the documents belonging to the same clusters}
@@
     \begin{figure}
-        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_91_0.png}\end{center}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_85_0.png}\end{center}
         \caption{Fully connected references graph}
@@
     The largest fully connected component is the composed of 8 nodes and 56
-edges plotted in figure \ref{fig14}. This documents are all cited
-together more than 4 times. You can investingate the edges and the
+edges plotted in figure \ref{fig12}. These documents are all cited
+together more than 4 times. You can investigate the edges and the
 weights in the interactive graph constructed above. We wanted all the
@@
 look to giant connected component, we will get a network of 27
-referenced paper with 142 egdes.
-
-    In the table \ref{fig10} below are the documents of the giant connected
-component represented in the interactive graph \ref{fig11}.
-
-    \begin{figure}
-        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_95_0.png}\end{center}
+referenced paper with 142 egdes represented in this graph \ref{fig15}.
+
+    In the table \ref{fig10} below are the documents contained in the giant
+connected component represented in the interactive graph \ref{fig15}.
+
+    \begin{figure}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_89_0.png}\end{center}
         \caption{Giant component graph}
-        \label{fig12}
-    \end{figure}
-
-    \begin{figure}
-        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_96_0.png}\end{center}
+        \label{fig15}
+    \end{figure}
+
+    \begin{figure}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_90_0.png}\end{center}
         \caption{Documents belonging to the giant component}
@@
 
-    Now we want to apply the same logic with the papers in-conferences. So
-we will focus on the analysis of the first graph that uses the
-intersection between the referenced documents of each two by two papers.
-The length of the intersection set had to be more than 4.
+    We wanted to apply the same logic with the papers in-conferences. So we
+focused on the analysis of the first graph that uses the intersection
+between the referenced documents of each two by two papers. The length
+of the intersection set had to be more than 4.
 
@@
     \begin{figure}
-        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_98_0.png}\end{center}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_92_0.png}\end{center}
         \caption{Documents in conferences belonging to the same clusters}
@@
 
-    When applying this kind of clustering we find that most of the clusters
+    When applying this kind of clustering we found that most of the clusters
 contains almost the same authors with different papers, which is logic

### 2019-01-11 Report/paper.tex
push paper and figures

@@
 derive insights into the community using network analysis, natural
-language processing and text mining. We discover patterns of
+language processing and text mining. We discovered patterns of
 collaboration between participants, their migration and the global
-spread of the community. We extract keywords and find clusters of
+spread of the community. We extracted keywords and found clusters of
 referenced papers and documents within the conferences.
@@
 to understand the research being conducted within the community, we
-explore methods to bring insight into the following aspects:
+explored methods to bring insight into the following aspects:
 
@@
 format, as csv is a human readable format and can easily be processed by
-all the data analysis tools we employ.
+all the data analysis tools we used.
 
@@
 in the xml file. Each author is associated to one line in the xml file.
-From the associated citation string we add the first part of the
+From the associated citation string we added the first part of the
 citation containing the author names, year, and title. This is later
 used to identify the paper when it is referenced in an other paper. Then
-we add a shortened version of author names (i.e.~West, R.) by
+we added a shortened version of author names (i.e.~West, R.) by
 considering the author order. Note that it happens that the short name
@@
 insight where people are working and gives use a way estimate where they
-are from. To extract the exact affiliation of an authors with an
+are from. To extract the exact affiliation of an author with an
 institution two approaches were used.
@@
 
-The most robust way to get a persons institution affiliation is to use
+The most robust way to get a person's institution affiliation is to use
 their email address. Email addresses can easily be extracted from the
 header section using a regular expression. Then, the part of the email
-containing the university domain can be extracted using an other regular
-expression. After this we used a domain-university mapping
+address containing the university domain can be extracted using an other
+regular expression. After this we used a domain-university mapping
 \cite{mapping} to map domains to institutions. The additional advantage
@@
         \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_11_0.png}\end{center}
-        \caption{Different formats used to reference institution}
+        \caption{First format used to refernce institution}
         \label{figA}
@@
         \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_12_0.png}\end{center}
-        \caption{Different formats used to reference institution}
+        \caption{Second format used to refernce institution}
         \label{figB}
@@
 detected the structure of the header section before extracting the
-association. We tagged the substring present in this section using a
-combination of \emph{named entity detection}, which automatically
+association.
+
+We tagged the substring present in this section using a combination of
+two methods. Firstly, \emph{named entity detection}, which automatically
 classifies strings as belonging to some pre-defined category, using the
-implementation provided by \emph{spacy}\cite{spacy2}, and simple string
-comparison matching of the names of authors and institutions we
-extracted from the metadata respectively from Approach 1 and tagging
-sections containing ``emails'' using regex , to detect where in the
-header the email is. Then, taking the tagged section, we detected which
-subsections corresponded to which author-affiliation listing type, and
-extracted the author email - institution mapping accordingly.
+implementation provided by \emph{spacy}\cite{spacy2}. This taggs
+categorized strings as organisation or a person. Secondly, we used
+simple string comparison matching of the names of authors and
+institutions to determine if a string is an author name (person) or an
+institution (organization). We extracted the data needed for this from
+the metadata respectively from Approach 1. To detect sections that are
+email adresses, we used regular expression. We assigned these strings
+the caregory ``Email''. Then, taking the tagged section, we detected
+which subsections corresponded to which author-affiliation listing type,
+and extracted the authors email address - institution mapping
+accordingly.
 
@@
 
-As there are a variety of way in which the name of an institution could
-be written --consider EPFL, EPF Lausanne-- crawling the english, french
-and german version of Wikipedia (not using the API, or the API wrapper,
-as this does not give access to the desired information) was a quick and
+As there are a variety of way in which the name of an institution can be
+written --consider EPFL, EPF Lausanne-- crawling the english, french and
+german version of Wikipedia (not using the API, or the API wrapper, as
+this does not give access to the desired information) was a quick and
 accurate way to get the location. The advantage of sending requests over
@@
 to spell the university exist. Requests were sent using \emph{urllib3},
-and \emph{beautifulsoup} was used to parse them get the coordinates
+and \emph{beautifulsoup} was used to parse them and get the coordinates
 present in the article. Regretfully not all institutions, even well
@@
 visualize it the python package \emph{networkx} was used. When
-constructing the graph, we associate qualitative features --such as the
+constructing the graph, we associated qualitative features --such as the
 name and institution of the author that is represented by a node-- to
-the nodes and edges of the graph. We also associate the number of
+the nodes and edges of the graph. We also associated the number of
 collaborations between different parties to the graphs as the weight of
@@
         \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_46_0.png}\end{center}
-        \caption{One of the connected components of the co-authorship graph}
+        \caption{One of the connected components of the multi-year co-authorship graph}
         \label{fig_plot}
@@
         \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_48_0.png}\end{center}
-        \caption{Largest Component}
+        \caption{Largest Component of the multiple collaboration co-authorship graph}
         \label{author_collab_large}
@@
 can be done using \emph{sklearns} spectral clustering algorithm by
-passing it the adjacency matrix of the graph. With this method we are
+passing it the adjacency matrix of the graph. With this method we were
 able to neatly separate the main component graph in three large
@@
 approach on pruning presented, we only considered institutions who
-collaborated in at least two conferences. This the main component of
-this graph is shown in figure \ref{unigraph}.
+collaborated in at least two conferences. The main component of this
+graph is shown in figure \ref{unigraph}.
 
@@
 appropriate for smaller graphs as their structure is still easy to
-interpret. As by construction betweenness takes into consideration the
-degrees of it neighboring nodes, it better structures the nodes large
-graphs into central and less central nodes. The width of the edge is
-based on the weight of the edge, which in turn reflects the number of
+interpret. As by definition betweenness centrality takes into
+consideration the degrees of a nodes neighboring nodes, it better
+structures the nodes large graphs into central and less central nodes.
+To decide which nodes to label, we use the same mesures by selecting the
+nodes with the largest centrality, only plotting nodes who's cenrality
+is in the 90th percentile of the graph. The width of the edge is based
+on the weight of the edge, which in turn reflects the number of
 collaboration between two nodes.
@@
         \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_59_0.png}\end{center}
-        \caption{Number of Contributiors by coutry, excluding the US}
+        \caption{Number of Contributiors by country, excluding the US}
         \label{figrep}
@@
 collaborations. Out of these 153, 108 involved at least one U.S.
-participant. Excluding US participation we find the collaboration graph
+participant. Excluding US participation we found the collaboration graph
 presented in figure \ref{figcollab}. We note that some countries, such
@@
         \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_61_0.png}\end{center}
-        \caption{Collaborative papers between countries excluding US}
+        \caption{Collaboration between countries excluding the US}
         \label{figcollab}
@@
         \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_64_0.png}\end{center}
-        \caption{Subcommunities by paricipation in CSCL. Blue: no participation in main compnents of CSCL. Red and orange each mark participation in one of the two main components of CSCL}
+        \caption{Subcommunities by participation in CSCL. Blue: no participation in main components of CSCL. Red and orange each mark participation in one of the two main components of CSCL}
         \label{CSCL_components}
@@
 The fact that normalized graph cuts will split the community into three
-promted further investigation. As will be discussed in the next section,
-the graph of authors that participanted in CSCL yields two large
-connected components. By coloring the authors contained in the two CSCL
-components different colors, and authors in neither a third color, we
-find a similar partitioning of the graph, as can be observed in figure
-\ref{CSCL_components}. This is somewhat trivial, as the graph is built
-based on collaboration in these conferences. However, the analysis of
-nationalities present in the graph yielded an interesting results. All
-Asian participants from nations other than Singapore are contained in
-the same cluster. We also note that one of the CSCL clusters is closer
-to the group of ICLS-only participants than the other. Additionaly,
-through normalized splits, we find that the section of the normalized
-cut containing ICLS only authors is overwhelmingly american.
+prompted further investigation. As will be discussed in the next
+section, the graph of authors that participanted in CSCL yields two
+large connected components. By coloring the authors contained in the two
+CSCL components with different colors, and authors in neither with a
+third color, we found a similar partitioning of the graph, as can be
+observed in figure \ref{CSCL_components}. This is somewhat trivial, as
+the graph is built based on collaboration in these conferences. However,
+the analysis of nationalities present in the graph yielded an
+interesting results. All Asian participants from nations other than
+Singapore are contained in the same cluster. We also observed that one
+of the CSCL clusters is closer to the group of ICLS-only participants
+than the other. Additionaly, through normalized splits, we found that
+the section of the normalized cut containing ICLS only authors is
+overwhelmingly American.
 
 Considering the wordclouds in figure \ref{c1}, \ref{c2}, \ref{c3} of the
-most common keywords in each of the large splits, we find a first
+most common keywords in each of the large splits, we found a first
 indication that the splits also reflect some thematic differences in
@@
         \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_66_0.png}\end{center}
-        \caption{Keywords of the blue Community}
+        \caption{Keywords of the blue community}
         \label{c1}
@@
 average number of authors of a paper. By constructing the graph based on
-collaboration of authors in each conference, we find that while ICLS
+collaboration of authors in each conference, we found that while ICLS
 contains one giant component, CSCL contains two large main components.
@@
 
-Using the data we have of participants over the years, and knowing their
-affiliation, we can now find members that change institutions over the
-years. Over the years of recording we find 14 participants that have
-changed countries and 47 that have moved institutions. We can see that
-most movement occured within the US respectively Europe, see figure
+Knowing the affiliation of participants to an institution in a given
+year, we can now find members that change institutions over the years.
+Over the years of recording we found 14 participants that have changed
+countries and 47 that have moved institutions. We can see that most
+movement occured within the US respectively Europe, see figure
 \ref{fig_move}.
@@
 
-We can observe a growth of the number of participants over the years,
-and by building co-authorship graphs for each year of the conference, we
-observe that the density and clustering coefficient of the graph
+We observe a growth of the number of participants over the years, and by
+building co-authorship graphs for each year of the conference, we
+observed that the density and clustering coefficient of the graph
 indicate a steady decrease, while the diameter and average shortest path
@@
 is reduced by more than half from the previous ICLS conference-- it is
-impossible to draw any statisically significant conclusions.
+impossible to draw any statisically significant conclusion.
 
@@
 wanted to investigate more if the relevance of all the documents
-published is increasing too. Using Pagerank algorithm and the In-degree
-of each nodes to get the most influencial documents referenced of the
-exploratory citations graph that we constructed before. We filtered the
-first 100 documents and then contructed a histogram of the counts by
-year. We obtain the figure \ref{fig7}:
+published is increasing aswell. Using the Pagerank algorithm and the
+In-degree of each nodes to get the most influencial documents referenced
+of the exploratory citations graph that we constructed before. We
+filtered the first 100 documents and then contructed a histogram of the
+counts by year. We obtained the figure \ref{fig7}:
 
@@
     We also noticed from the first graph that some documents were more
-likely to cited together. We can say that the more two documents are
+likely to be cited together. We can say that the more two documents are
 likely to be cited together the more it is probable that both documents
@@
 
-    Using this graph, we also want to extract if there are some clusters of
-papers cited together. As we explained before, we run strongly connected
-algorithm to check if some cited documents are more likely to be cited
-together, and this will give us clusters of cited documents that are
-more likely to be about the same subjects. We can visualise one cluster,
-the most important one in figure \ref{fig12}.
+    Using this graph, we also wanted to extract if there are some clusters
+of papers cited together. As we explained before, we run strongly
+connected algorithm to check if some cited documents are more likely to
+be cited together, and this will give us clusters of cited documents
+that are more likely to be about the same subjects. We can visualise one
+cluster, the most important one in figure \ref{fig12}.
 
@@
 
-In summary, we were able to extract how the dominant some institutions
-and countries are within the conference. Some initiall collaboration
-patterns between countries, instututions and authors were extracted.
+In summary, we were able to show how the dominant some institutions and
+countries are within the conference. Collaboration patterns between
+countries, instututions and authors were extracted and analyzed.
 Subcommunities found within the network of co-authorship reflect the
@@
 
-Overall, due to lack of data, we were often unable find non trivial
-results; This lack of data is exasperated by the fact that the
-conference of 2018 presents as an outlier in the dataset. Additionally,
-taking document clustering for instance as an example, network analysis
-of references were more accurate than(NLP) regarding documents and
-references clustering.
+Overall, due to lack of data, we were often unable to find non trivial
+results; this lack of data is aggravated by the fact that the conference
+of 2018 presents as an outlier in the dataset. Additionally, taking
+document clustering as an example, network analysis of references were
+more accurate than NLP regarding documents and references clustering.
 

### 2019-01-11 Report/paper.tex
push interactive report noteboo and final report

@@
 \item
-  We put all words to lower case
+  We put all words to lower case.
 \item
@@
   the purpose of this task these words were not important and were only
-  going to increase the bag of words length
+  going to increase the bag of words length.
 \item
@@
 keywords and extract them, this method is the most accurate but we found
-out that for 492 papers we had no keywords included. So we deciced to
-use other two methods for keywords extraction, namely one based on
+out that 492 papers had no keywords included. So we deciced to use two
+other methods for keywords extraction, namely one based on
 \textbf{\emph{TF-IDF}} and a second one based on \textbf{\emph{Rake}}.
+
 \textbf{\emph{TF-IDF}} is one of the most popular term-weighting schemes
@@
         \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_48_0.png}\end{center}
-        \caption{Largest Component of the multiple collaboration co-authorship graph}
+        \caption{Largest component of the multiple collaboration co-authorship graph}
         \label{author_collab_large}
@@
     \begin{figure}
-        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_51_0.png}\end{center}
-        \caption{Different formats used to reference institution}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_52_0.png}\end{center}
+        \caption{Main component of institution collaboration graph}
         \label{unigraph}
@@
     \begin{figure}
-        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_57_0.png}\end{center}
-        \caption{Global spread of community. Size of dot represent number of participants from each institution}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_58_0.png}\end{center}
+        \caption{Global spread of community. Size of dot represents the number of participants from each institution}
         \label{global_com}
@@
     \begin{figure}
-        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_59_0.png}\end{center}
-        \caption{Number of Contributiors by country, excluding the US}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_60_0.png}\end{center}
+        \caption{Number of participants by country, excluding the US}
         \label{figrep}
@@
     \begin{figure}
-        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_61_0.png}\end{center}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_62_0.png}\end{center}
         \caption{Collaboration between countries excluding the US}
@@
     \begin{figure}
-        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_63_0.png}\end{center}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_64_0.png}\end{center}
         \caption{Subcommunities via normalized cuts in largest component of co-authorship graph}
@@
     \begin{figure}
-        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_64_0.png}\end{center}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_66_0.png}\end{center}
         \caption{Subcommunities by participation in CSCL. Blue: no participation in main components of CSCL. Red and orange each mark participation in one of the two main components of CSCL}
@@
 Singapore are contained in the same cluster. We also observed that one
-of the CSCL clusters is closer to the group of ICLS-only participants
-than the other. Additionaly, through normalized splits, we found that
-the section of the normalized cut containing ICLS only authors is
-overwhelmingly American.
+of the CSCL clusters (orange in \ref{CSCL_components}) is closer to the
+group of ICLS-only participants than the other (red component).
+Additionaly, through normalized splits, we found that the section of the
+normalized cut containing mostly ICLS only authors (blue in
+\ref{normalized}) is overwhelmingly American.
 
@@
     \begin{figure}
-        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_66_0.png}\end{center}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_68_0.png}\end{center}
         \caption{Keywords of the blue community}
@@
     \begin{figure}
-        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_67_0.png}\end{center}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_69_0.png}\end{center}
+        \caption{Keywords of the orange community}
+        \label{c2}
+    \end{figure}
+
+    \begin{figure}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_70_0.png}\end{center}
         \caption{Keywords of the red community}
-        \label{c2}
-    \end{figure}
-
-    \begin{figure}
-        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_68_0.png}\end{center}
-        \caption{Keywords of the orange community}
         \label{c3}
@@
     \begin{figure}
-        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_71_0.png}\end{center}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_73_0.png}\end{center}
         \caption{Movement of participants across institutions}
@@
 indicate a steady decrease, while the diameter and average shortest path
-length tend to increase. This hints that the community is attracting new
-member that do not collaborate with the established group of
+length tend to increase. This suggests that the community is attracting
+new members that do not collaborate with the established group of
 participants. But, as the years 2018 shows a massive increase of
@@
     \begin{figure}
-        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_74_0.png}\end{center}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_76_0.png}\end{center}
         \caption{Distribution of the number of referenced documents belonging to each year}
@@
     \begin{figure}
-        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_76_0.png}\end{center}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_78_0.png}\end{center}
         \caption{Distribution of the 100 most referenced documents belonging to each year}
@@
     \begin{figure}
-        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_79_0.png}\end{center}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_81_0.png}\end{center}
         \caption{In-degree count for each document}
@@
     \begin{figure}
-        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_81_0.png}\end{center}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_83_0.png}\end{center}
         \caption{Count of documents cited together}
@@
     \begin{figure}
-        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_83_0.png}\end{center}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_85_0.png}\end{center}
         \caption{Table of the documents belonging to the same clusters}
@@
     \begin{figure}
-        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_85_0.png}\end{center}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_87_0.png}\end{center}
         \caption{Fully connected references graph}
@@
     \begin{figure}
-        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_89_0.png}\end{center}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_91_0.png}\end{center}
         \caption{Giant component graph}
@@
     \begin{figure}
-        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_90_0.png}\end{center}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_92_0.png}\end{center}
         \caption{Documents belonging to the giant component}
@@
     \begin{figure}
-        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_92_0.png}\end{center}
+        \begin{center}\adjustimage{max size={\linewidth}{0.4\paperheight}}{paper_files/paper_94_0.png}\end{center}
         \caption{Documents in conferences belonging to the same clusters}
